---
title: "calculating_comm_div_metrics_benthic"
author: "CEB"
date: '2023-05-10'
output: html_document
---

#load packages
```{r}
library(tidyverse) #for everything
library(vegan) # for diversity and community analyses


library(corrplot)


```


#START WITH VIDEO DATA-----------

#load raw data
```{r}

#raw video data----
tet_video_raw<-read.csv("../raw_data/Summary_sheet_benthic_video_tetiaroa_Nov21_RW.csv", stringsAsFactors = TRUE)
str(tet_video_raw)

#change transect number to factor
tet_video_raw<-
  tet_video_raw%>%
  mutate(Transect = as.factor(Transect))
tet_video_raw

##also load site metadata:----
tet_site_meta<-read.csv("../../metadata/TARP_Nov2021_site_metadata_version2.csv", stringsAsFactors = TRUE)
str(tet_site_meta)

#also load transect metadata:-----


#create new columns to match metadata, and remove capitalization of motu----
tet_video_raw<-
  tet_video_raw%>%
  rename_with(tolower)%>%
  mutate(motu = str_to_lower(motu),
         transect_name = str_to_lower(transect_name),
         protection = str_to_lower(exposure))%>%
  relocate(protection, .after = exposure)
 
tet_video_raw

#combine with site metadata----
tet_video_raw_meta<-left_join(
  select(tet_video_raw,-c(rat_treatment, exposure, longitude_start, latitude_start, longitude_end, latitude_end)),
                              tet_site_meta, by = c("motu", "protection"))%>%
  relocate(site.name:rat.eradication.status, .after = motu)
tet_video_raw_meta

```

##aggregate - one for broad groupings, one for coral-focused bc can use genus for these:
```{r}

#broad groupings: hard coral, other inverts (sea_cucumber, tridacna_giant_clam, corallimorpharia), pavement, dead_coral, fish, rubble (rubble, sand_rubble), sand, cca, turf (turf_algae, turf_rubble), macroalgae
#transect_tape

#NEW broad groupings: hard coral, other inverts (sea_cucumber, tridacna_giant_clam, corallimorpharia), pavement.turf (pavement, turf_algae), dead_coral, fish, rubble (rubble, sand_rubble, turf_rubble), sand, cca, macroalgae
#transect_tape

colnames(tet_video_raw_meta)

tet_video_raw_meta_broad<-
  tet_video_raw_meta%>%
  mutate(hard_coral = rowSums(across(c(acropora_arborescent:porites_submassive))))%>%
  mutate(other_fish_inverts = rowSums(across(c(sea_cucumber, tridacna_giant_clam, fish, corallimorpharia ))))%>%
  mutate(pavement = rowSums(across(c(turf_algae, pavement))))%>%
  mutate(rubble = rowSums(across(c(rubble, sand_rubble, turf_rubble))))%>%
  select(motu, site.name, wind.exposure, rat.eradication.status, protection, transect, 
         hard_coral, other_fish_inverts, sand, dead_coral, pavement, rubble, cca, macroalgae,
         transect_tape)%>%
  mutate(total = rowSums(across(c(hard_coral:transect_tape))))

tet_video_raw_meta_broad
#looks good, rowsums to 100, but can ignore transect tape. 

#coral only: 
tet_video_raw_meta_coral<-
  tet_video_raw_meta%>%
  select(motu:porites_submassive)

tet_video_raw_meta_coral


```

#calculate diversity (only makes sense for corals?)
```{r}

#make species only table and env only table: ----
tet_video_raw_meta_coral_sp<-
  tet_video_raw_meta_coral%>%
  ungroup()%>%
  select(acropora_arborescent:porites_submassive)
tet_video_raw_meta_coral_sp

tet_video_raw_meta_broad_sp<-
  tet_video_raw_meta_broad%>%
  ungroup()%>%
  select(hard_coral:macroalgae)
tet_video_raw_meta_broad_sp


tet_video_raw_env<-
  tet_video_raw_meta_broad%>%
  ungroup()%>%
  select(motu:transect)
tet_video_raw_env


###calculate diversity for corals----
observed<-specnumber(tet_video_raw_meta_coral_sp)
shannon<-diversity(tet_video_raw_meta_coral_sp, "shannon")
evenness<-diversity(tet_video_raw_meta_coral_sp)/log(specnumber(tet_video_raw_meta_coral_sp)) #J = H/log(specnumber(BCI))

tet_video_coral_diversity<-
tet_video_raw_env %>%
  cbind(observed, shannon, evenness)

tet_video_coral_diversity


#quick plots----
tet_video_coral_diversity%>%
  ggplot(aes(x = motu, y = observed, color = wind.exposure, fill = wind.exposure))+
  geom_boxplot(outlier.size=0, outlier.stroke=0,outlier.shape=NA, alpha = 0.1) +
  geom_point(size = 3, pch=21, alpha= .6, position=position_jitterdodge())+
  theme_bw()

tet_video_coral_diversity%>%
  ggplot(aes(x = motu, y = shannon, color = wind.exposure, fill = wind.exposure))+
  geom_boxplot(outlier.size=0, outlier.stroke=0,outlier.shape=NA, alpha = 0.1) +
  geom_point(size = 3, pch=21, alpha= .6, position=position_jitterdodge())+
  theme_bw()


tet_video_coral_diversity%>%
  ggplot(aes(x = motu, y = evenness, color = wind.exposure, fill = wind.exposure))+
  geom_boxplot(outlier.size=0, outlier.stroke=0,outlier.shape=NA, alpha = 0.1) +
  geom_point(size = 3, pch=21, alpha= .6, position=position_jitterdodge())+
  theme_bw()




```


###run nmds (broad groupings)-----
```{r}
#run nmds----
nmds_video<-metaMDS(tet_video_raw_meta_broad_sp, distance = "bray", trymax=200, k=2, autotransform = FALSE)
nmds_video
#2 axes stress = 0.06125085, so all good

plot(nmds_video)
scores(nmds_video, display="species")


#look at plot and centroids, for now just motu and exposure (so sitename). will need to add explanatory variables
plot(nmds_video)
ord.fit<-envfit(nmds_video~site.name, data = tet_video_raw_meta_broad, na.rm=TRUE)
ord.fit #looks like some differences among motu
plot(ord.fit)
#draw polygons
ordihull(nmds_video, tet_video_raw_meta_broad$site.name, pty=3)


#PERMANOVA
#anosim more influenced by dispersion, so use adonis
#run analysis
ad_video1<-adonis2(tet_video_raw_meta_broad_sp ~ site.name, data = tet_video_raw_meta_broad, method="euclidean")
ad_video1
#site explains ~38% of variance


ad_video2<-adonis2(tet_video_raw_meta_broad_sp ~ motu*wind.exposure, data = tet_video_raw_meta_broad, method="euclidean")
ad_video2
#motu only significant - explains 31%


#test dispersion using PERMDISP
mod_video <- betadisper(vegdist(tet_video_raw_meta_broad_sp, method = "bray"), tet_video_raw_meta_broad$site.name)
mod_video
#test for overall differences
anova(mod_video)
#not different

#extract distance to centroid - use TukeyHSD.betadisper from ?betadisper
dist_cent_video <-betadisper(d = vegdist(tet_video_raw_meta_broad_sp, method = "bray"),
                           group = tet_video_raw_meta_broad$site.name,
                           type = "centroid", sqrt.dist = FALSE)
dist_cent_video
TukeyHSD(dist_cent_video,conf.level = .95) #okay this shows CI's for contrasts. note that conf.level affects intervals, but not p-values. 

dist_cent_videodf<-
  cbind(tet_video_raw_env, dist_cent_video$distances) %>%
  rename(Distance_to_centroid = "dist_cent_video$distances")
dist_cent_videodf



##SIMPER analysis to test effects of species----
#by site:
sim_video<-simper(tet_video_raw_meta_broad_sp, tet_video_raw_meta_broad$site.name, permutations = 999)
summary(sim_video)

#by motu:
sim_video_motu<-simper(tet_video_raw_meta_broad_sp, tet_video_raw_meta_broad$motu, permutations = 999)
summary(sim_video_motu)

#by exposure:
sim_video_exp<-simper(tet_video_raw_meta_broad_sp, tet_video_raw_meta_broad$wind.exposure, permutations = 999)
summary(sim_video_exp)



##extract site/transect scores----
video_spp.sc <- as.data.frame(scores(nmds_video, "species"))  #Using the scores function from vegan to extract the species scores and convert to a data.frame
video_spp.sc<-
  video_spp.sc%>%
  rownames_to_column(var="Species") # create a column of species, from the rownames of species.scores


video_site.sc <- scores(nmds_video, display = "sites", shrink = FALSE) 
video_site.sc

#merge site.sc with metadata and dispersion
nmds_video_site_scores<-
  bind_cols(dist_cent_videodf,
                    as_tibble(video_site.sc))
nmds_video_site_scores


#plot just to see----

#get hull data:
site.A1 <- nmds_video_site_scores[nmds_video_site_scores$site.name == "A1", ][chull(nmds_video_site_scores[nmds_video_site_scores$site.name == 
    "A1", c("NMDS1", "NMDS2")]), ]

site.A2 <- nmds_video_site_scores[nmds_video_site_scores$site.name == "A2", ][chull(nmds_video_site_scores[nmds_video_site_scores$site.name == 
    "A2", c("NMDS1", "NMDS2")]), ]  

site.Re1 <- nmds_video_site_scores[nmds_video_site_scores$site.name == "Re1", ][chull(nmds_video_site_scores[nmds_video_site_scores$site.name == 
    "Re1", c("NMDS1", "NMDS2")]), ]

site.Re2<- nmds_video_site_scores[nmds_video_site_scores$site.name == "Re2", ][chull(nmds_video_site_scores[nmds_video_site_scores$site.name == 
    "Re2", c("NMDS1", "NMDS2")]), ]  

site.Rm1 <- nmds_video_site_scores[nmds_video_site_scores$site.name == "Rm1", ][chull(nmds_video_site_scores[nmds_video_site_scores$site.name == 
    "Rm1", c("NMDS1", "NMDS2")]), ]

site.Rm2<- nmds_video_site_scores[nmds_video_site_scores$site.name == "Rm2", ][chull(nmds_video_site_scores[nmds_video_site_scores$site.name == 
    "Rm2", c("NMDS1", "NMDS2")]), ]  

hull.data <- rbind(site.A1, site.A2, site.Re1, site.Re2, site.Rm1, site.Rm2)  #combine
hull.data

ggplot() + 
  geom_text(data=video_spp.sc,aes(x=NMDS1,y=NMDS2,label=Species), alpha = .2) +  # add the species labels - 
  geom_point(data=nmds_video_site_scores,aes(x=NMDS1,y=NMDS2,colour=site.name, fill = site.name, pch = site.name), stat="identity", size=5, alpha = .9) +
  geom_polygon(data=hull.data,aes(x=NMDS1,y=NMDS2,fill=site.name,group=site.name),alpha=0.30) + # add the convex hulls
  theme_bw() + 
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(), #remove gray boxes
        text = element_text(size=20))
        #legend.title = element_blank()) #remove legend title
        #legend.box.background = element_rect(colour = "black", fill='white', linetype='solid', size=1), 
       # legend.justification=c(1,.9), legend.position=c(1,.9))  #  fix legend



```

##combine transect data and save----
```{r}
str(nmds_video_site_scores) #BROAD GROUPS
str(tet_video_coral_diversity) #CORALS
str(tet_video_raw_meta_broad) #broad groups - % cover

#rename:
tet_video_coral_diversity_rn<-
  tet_video_coral_diversity%>%
  rename(coral_observed = observed,
         coral_shannon = shannon, 
         coral_evenness= evenness)
tet_video_coral_diversity_rn


tet_video_div_comm_dat<-
  left_join(tet_video_coral_diversity_rn, nmds_video_site_scores,
            by = c("motu", "site.name", "wind.exposure", "rat.eradication.status", "protection", "transect"))
tet_video_div_comm_dat


tet_video_div_comm_dat_w_cover<-
  left_join(tet_video_div_comm_dat, tet_video_raw_meta_broad,
            by = c("motu", "site.name", "wind.exposure", "rat.eradication.status", "protection", "transect"))

tet_video_div_comm_dat_w_cover
#round % cover data, and make it clear what it is....
tet_video_div_comm_dat_w_cover<-
  tet_video_div_comm_dat_w_cover%>%
  mutate(across(c(hard_coral:transect_tape), round, 2))%>%
  rename_with(.fn = ~ paste0(.x, "_percent_cover"), .cols = c("hard_coral":"total"))
tet_video_div_comm_dat_w_cover

#write.csv(tet_video_div_comm_dat_w_cover, "../output/data/tet_video_div_comm_dat.csv")

```



#####NOW DO IN SITU---------

#load raw data
```{r}

#raw in situ data----
tet_insitu_raw<-read.csv("../raw_data/Tetiaroa_benthic_uvc_focal_Nov21_in_situ.csv", stringsAsFactors = TRUE)
str(tet_insitu_raw)

#change transect number to factor
tet_insitu_raw<-
  tet_insitu_raw%>%
  mutate(Transect = as.factor(Transect))
levels(tet_insitu_raw$Transect)

##also load site metadata:----
tet_site_meta<-read.csv("../../metadata/TARP_Nov2021_site_metadata_version2.csv", stringsAsFactors = TRUE)
str(tet_site_meta)

#also load transect metadata:-----


#create new columns to match metadata, and remove capitalization of motu----
tet_insitu_raw<-
  tet_insitu_raw%>%
  rename_with(tolower)%>%
  mutate(motu = str_to_lower(motu),
         protection = str_to_lower(site))%>%
  relocate(protection, .after = motu)
 
tet_insitu_raw

#combine with site metadata----
tet_insitu_raw_meta<-left_join(
  select(tet_insitu_raw,-c(site)),
                              tet_site_meta, by = c("motu", "protection"))%>%
  relocate(site.name:rat.eradication.status, .after = motu)
tet_insitu_raw_meta

```

##check broad categories match groupings
```{r}
levels(tet_insitu_raw_meta$category)
levels(tet_insitu_raw_meta$benthos)

tet_insitu_raw_meta%>%
  filter(benthos=="coral")%>%
  droplevels()%>%
  group_by(category)%>%
  summarize(n_category=length(category))

tet_insitu_raw_meta%>%
  filter(benthos=="turf")%>%
  droplevels()%>%
  group_by(category)%>%
  summarize(n_category=length(category))

tet_insitu_raw_meta%>%
  filter(benthos=="sand")%>%
  droplevels()%>%
  group_by(category)%>%
  summarize(n_category=length(category))

tet_insitu_raw_meta%>%
  filter(benthos=="cyano")%>%
  droplevels()%>%
  group_by(category)%>%
  summarize(n_category=length(category))

tet_insitu_raw_meta%>%
  filter(benthos=="macroalgae")%>%
  droplevels()%>%
  group_by(category)%>%
  summarize(n_category=length(category))

tet_insitu_raw_meta%>%
  filter(benthos=="pavement")%>%
  droplevels()%>%
  group_by(category)%>%
  summarize(n_category=length(category))

tet_insitu_raw_meta%>%
  filter(benthos=="rubble")%>%
  droplevels()%>%
  group_by(category)%>%
  summarize(n_category=length(category))


##combine some categories-----

#clam + sea cucumber to other invert
tet_insitu_raw_meta<-
  tet_insitu_raw_meta%>%
  mutate(category = case_when(benthos == "clam" ~ "other_invert",
                           benthos == "sea cucumber" ~ "other_invert",
                           TRUE ~ as.character(category)))%>%
  mutate(category = as.factor(category))

tet_insitu_raw_meta

#pavement + turf (because some observer differences - I called more turf, but only did Rimatuu Exposed and Reiono Protected. Rosie called pavement. Also includes pavement/sand)
tet_insitu_raw_meta<-
  tet_insitu_raw_meta%>%
  mutate(category = case_when(benthos == "turf" ~ "pavement",
                              benthos == "pavement/sand" ~ "pavement",
                           TRUE ~ as.character(category)))%>%
  mutate(category = as.factor(category))

tet_insitu_raw_meta
levels(tet_insitu_raw_meta$category)



```

##aggregate - one for broad groupings, one for coral-focused bc can use genus for these:
```{r}

#first sum by transect and make wide----
#by specific groups:
tet_insitu_raw_meta_benthos_wide<-
tet_insitu_raw_meta%>%
  mutate(count = 1)%>%
  group_by(motu, site.name, wind.exposure, rat.eradication.status, transect, benthos)%>%
  summarize(sum_transect = sum(count),
            prop_transect = sum_transect/60) %>% #60 points per transect
   pivot_wider(id_cols = c(motu, site.name, wind.exposure, rat.eradication.status, transect), 
              values_from = prop_transect, names_from = benthos, values_fill = 0)%>%
  ungroup()
tet_insitu_raw_meta_benthos_wide


#by broad category:
tet_insitu_raw_meta_cat_wide<-
tet_insitu_raw_meta%>%
  mutate(count = 1)%>%
  group_by(motu, site.name, wind.exposure, rat.eradication.status, transect, category)%>%
  summarize(sum_transect = sum(count),
            prop_transect = sum_transect/60) %>% #60 points per transect
   pivot_wider(id_cols = c(motu, site.name, wind.exposure, rat.eradication.status, transect), 
              values_from = prop_transect, names_from = category, values_fill = 0)%>%
  ungroup()
tet_insitu_raw_meta_cat_wide



#coral only: ----
tet_insitu_raw_meta_coral_wide<-
  tet_insitu_raw_meta_benthos_wide%>%
  select(c(motu, site.name, wind.exposure, rat.eradication.status, transect,
           porites, acropora, montipora, pavona, leptoseris, fungia, "porites rus"))%>%
    mutate(porites = rowSums(across(c(porites, "porites rus")))) %>% #combine porites + porites rus
  select(-c("porites rus"))
tet_insitu_raw_meta_coral_wide


```


#calculate diversity (only makes sense for corals?)
```{r}

#make species only table and env only table: ----
tet_insitu_raw_meta_coral_sp<-
  tet_insitu_raw_meta_coral_wide%>%
  ungroup()%>%
  select(porites:fungia)
tet_insitu_raw_meta_coral_sp

tet_insitu_raw_meta_broad_sp<-
  tet_insitu_raw_meta_cat_wide%>%
  ungroup()%>%
  select(coral:cyano)
tet_insitu_raw_meta_broad_sp


tet_insitu_raw_env<-
  tet_insitu_raw_meta_cat_wide%>%
  ungroup()%>%
  select(motu:transect)
tet_insitu_raw_env


###calculate diversity for corals----
observed<-specnumber(tet_insitu_raw_meta_coral_sp)
shannon<-diversity(tet_insitu_raw_meta_coral_sp, "shannon")
evenness<-diversity(tet_insitu_raw_meta_coral_sp)/log(specnumber(tet_insitu_raw_meta_coral_sp)) #J = H/log(specnumber(BCI))

tet_insitu_coral_diversity<-
tet_insitu_raw_env %>%
  cbind(observed, shannon, evenness)

tet_insitu_coral_diversity


#quick plots----
tet_insitu_coral_diversity%>%
  ggplot(aes(x = motu, y = observed, color = wind.exposure, fill = wind.exposure))+
  geom_boxplot(outlier.size=0, outlier.stroke=0,outlier.shape=NA, alpha = 0.1) +
  geom_point(size = 3, pch=21, alpha= .6, position=position_jitterdodge())+
  theme_bw()

tet_insitu_coral_diversity%>%
  ggplot(aes(x = motu, y = shannon, color = wind.exposure, fill = wind.exposure))+
  geom_boxplot(outlier.size=0, outlier.stroke=0,outlier.shape=NA, alpha = 0.1) +
  geom_point(size = 3, pch=21, alpha= .6, position=position_jitterdodge())+
  theme_bw()


tet_insitu_coral_diversity%>%
  ggplot(aes(x = motu, y = evenness, color = wind.exposure, fill = wind.exposure))+
  geom_boxplot(outlier.size=0, outlier.stroke=0,outlier.shape=NA, alpha = 0.1) +
  geom_point(size = 3, pch=21, alpha= .6, position=position_jitterdodge())+
  theme_bw()


#all between 1-3 coral genera, not showing much....

```


###run nmds (broad groupings)-----
```{r}
#run nmds----
nmds_insitu<-metaMDS(tet_insitu_raw_meta_broad_sp, distance = "bray", trymax=200, k=2, autotransform = FALSE)
nmds_insitu
#2 axes stress = 0.06666792, so all good

plot(nmds_insitu)
scores(nmds_insitu, display="species")


#look at plot and centroids, for now just motu and exposure (so sitename). will need to add explanatory variables
plot(nmds_insitu)
ord.fit<-envfit(nmds_insitu~site.name, data = tet_insitu_raw_meta_cat_wide, na.rm=TRUE)
ord.fit #looks like some differences among motu
plot(ord.fit)
#draw polygons
ordihull(nmds_insitu, tet_insitu_raw_meta_cat_wide$site.name, pty=3)


#PERMANOVA
#anosim more influenced by dispersion, so use adonis
#run analysis
ad_insitu1<-adonis2(tet_insitu_raw_meta_broad_sp ~ site.name, data = tet_insitu_raw_meta_cat_wide, method="euclidean")
ad_insitu1
#site explains ~55% of variance


ad_insitu2<-adonis2(tet_insitu_raw_meta_broad_sp ~ motu*wind.exposure, data = tet_insitu_raw_meta_cat_wide, method="euclidean")
ad_insitu2
#motu and motu*exposure significant - 36% and 18% r^2, respectively


#test dispersion using PERMDISP
mod_insitu <- betadisper(vegdist(tet_insitu_raw_meta_broad_sp, method = "bray"), tet_insitu_raw_meta_cat_wide$site.name)
mod_insitu
#test for overall differences
anova(mod_insitu)
#not different

#extract distance to centroid - use TukeyHSD.betadisper from ?betadisper
dist_cent_insitu <-betadisper(d = vegdist(tet_insitu_raw_meta_broad_sp, method = "bray"),
                           group = tet_insitu_raw_meta_cat_wide$site.name,
                           type = "centroid", sqrt.dist = FALSE)
dist_cent_insitu
TukeyHSD(dist_cent_insitu,conf.level = .95) #okay this shows CI's for contrasts. note that conf.level affects intervals, but not p-values. 

dist_cent_insitudf<-
  cbind(tet_insitu_raw_env, dist_cent_insitu$distances) %>%
  rename(Distance_to_centroid = "dist_cent_insitu$distances")
dist_cent_insitudf



##SIMPER analysis to test effects of species----
#by site:
sim_insitu<-simper(tet_insitu_raw_meta_broad_sp, tet_insitu_raw_meta_cat_wide$site.name, permutations = 999)
summary(sim_insitu)

#by motu:
sim_insitu_motu<-simper(tet_insitu_raw_meta_broad_sp, tet_insitu_raw_meta_cat_wide$motu, permutations = 999)
summary(sim_insitu_motu)

#by exposure:
sim_insitu_exp<-simper(tet_insitu_raw_meta_broad_sp, tet_insitu_raw_meta_cat_wide$wind.exposure, permutations = 999)
summary(sim_insitu_exp)



##extract site/transect scores----
insitu_spp.sc <- as.data.frame(scores(nmds_insitu, "species"))  #Using the scores function from vegan to extract the species scores and convert to a data.frame
insitu_spp.sc<-
  insitu_spp.sc%>%
  rownames_to_column(var="Species") # create a column of species, from the rownames of species.scores


insitu_site.sc <- scores(nmds_insitu, display = "sites", shrink = FALSE) 
insitu_site.sc

#merge site.sc with metadata and dispersion
nmds_insitu_site_scores<-
  bind_cols(dist_cent_insitudf,
                    as_tibble(insitu_site.sc))
nmds_insitu_site_scores


#plot just to see----

#get hull data:
site.A1 <- nmds_insitu_site_scores[nmds_insitu_site_scores$site.name == "A1", ][chull(nmds_insitu_site_scores[nmds_insitu_site_scores$site.name == 
    "A1", c("NMDS1", "NMDS2")]), ]

site.A2 <- nmds_insitu_site_scores[nmds_insitu_site_scores$site.name == "A2", ][chull(nmds_insitu_site_scores[nmds_insitu_site_scores$site.name == 
    "A2", c("NMDS1", "NMDS2")]), ]  

site.Re1 <- nmds_insitu_site_scores[nmds_insitu_site_scores$site.name == "Re1", ][chull(nmds_insitu_site_scores[nmds_insitu_site_scores$site.name == 
    "Re1", c("NMDS1", "NMDS2")]), ]

site.Re2<- nmds_insitu_site_scores[nmds_insitu_site_scores$site.name == "Re2", ][chull(nmds_insitu_site_scores[nmds_insitu_site_scores$site.name == 
    "Re2", c("NMDS1", "NMDS2")]), ]  

site.Rm1 <- nmds_insitu_site_scores[nmds_insitu_site_scores$site.name == "Rm1", ][chull(nmds_insitu_site_scores[nmds_insitu_site_scores$site.name == 
    "Rm1", c("NMDS1", "NMDS2")]), ]

site.Rm2<- nmds_insitu_site_scores[nmds_insitu_site_scores$site.name == "Rm2", ][chull(nmds_insitu_site_scores[nmds_insitu_site_scores$site.name == 
    "Rm2", c("NMDS1", "NMDS2")]), ]  

hull.data <- rbind(site.A1, site.A2, site.Re1, site.Re2, site.Rm1, site.Rm2)  #combine
hull.data

ggplot() + 
  geom_text(data=insitu_spp.sc,aes(x=NMDS1,y=NMDS2,label=Species), alpha = .2) +  # add the species labels - 
  geom_point(data=nmds_insitu_site_scores,aes(x=NMDS1,y=NMDS2,colour=site.name, fill = site.name, pch = site.name), stat="identity", size=5, alpha = .9) +
  geom_polygon(data=hull.data,aes(x=NMDS1,y=NMDS2,fill=site.name,group=site.name),alpha=0.30) + # add the convex hulls
  theme_bw() + 
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(), #remove gray boxes
        text = element_text(size=20))
        #legend.title = element_blank()) #remove legend title
        #legend.box.background = element_rect(colour = "black", fill='white', linetype='solid', size=1), 
       # legend.justification=c(1,.9), legend.position=c(1,.9))  #  fix legend



```


##combine transect data and save----
```{r}
str(nmds_insitu_site_scores) #BROAD GROUPS
str(tet_insitu_coral_diversity) #CORALS
str(tet_insitu_raw_meta_cat_wide) #% cover data

#rename:
tet_insitu_coral_diversity_rn<-
  tet_insitu_coral_diversity%>%
  rename(coral_observed = observed,
         coral_shannon = shannon, 
         coral_evenness= evenness)
tet_insitu_coral_diversity_rn


tet_insitu_div_comm_dat<-
  left_join(tet_insitu_coral_diversity_rn, nmds_insitu_site_scores,
            by = c("motu", "site.name", "wind.exposure", "rat.eradication.status", "transect"))
tet_insitu_div_comm_dat

#write.csv(tet_insitu_div_comm_dat, "../output/data/tet_insitu_div_comm_dat.csv")

##keep % cover data, too: 
tet_insitu_div_comm_dat_w_cover<-
  left_join(tet_insitu_div_comm_dat, tet_insitu_raw_meta_cat_wide,
            by = c("motu", "site.name", "wind.exposure", "rat.eradication.status", "transect"))

tet_insitu_div_comm_dat_w_cover

#round % cover data, and make it clear what it is....
tet_insitu_div_comm_dat_w_cover<-
  tet_insitu_div_comm_dat_w_cover%>%
  mutate(across(c(coral:cyano), round, 2))%>%
  rename_with(.fn = ~ paste0(.x, "_prop_cover"), .cols = c("coral":"cyano"))
tet_insitu_div_comm_dat_w_cover


#write.csv(tet_insitu_div_comm_dat_w_cover, "../output/data/tet_insitu_div_comm_dat.csv")


```



#check corrs bewtween in situ and video % cover:
```{r}

#hard coral
cor.test(tet_insitu_div_comm_dat_w_cover$coral_prop_cover, tet_video_div_comm_dat_w_cover$hard_coral_percent_cover)
#0.7463035 


#macroalgae
cor.test(tet_insitu_div_comm_dat_w_cover$macroalgae_prop_cover, tet_video_div_comm_dat_w_cover$macroalgae_percent_cover)
#0.7884377


#pavement
cor.test(tet_insitu_div_comm_dat_w_cover$pavement_prop_cover, tet_video_div_comm_dat_w_cover$pavement_percent_cover)
#0.3124796


#rubble
cor.test(tet_insitu_div_comm_dat_w_cover$rubble_prop_cover, tet_video_div_comm_dat_w_cover$rubble_percent_cover)
#0.4638508


#sand
cor.test(tet_insitu_div_comm_dat_w_cover$sand_prop_cover, tet_video_div_comm_dat_w_cover$sand_percent_cover)
#0.8228589

#other inverts
cor.test(tet_insitu_div_comm_dat_w_cover$other_invert_prop_cover, tet_video_div_comm_dat_w_cover$other_fish_inverts_percent_cover)
#0.1873515


#for largest groups (corals, macroalgae, sand) - very strongly correlated
#only issue is with turf/pavement...

```


##check corrs - re-group:
```{r}
tet_video_raw_meta_broad<-
  tet_video_raw_meta%>%
  mutate(total_hard_coral = rowSums(across(c(acropora_arborescent:porites_submassive))))%>%
  mutate(other_fish_inverts = rowSums(across(c(sea_cucumber, tridacna_giant_clam, fish, corallimorpharia ))))%>%
  mutate(turf = rowSums(across(c(turf_algae, turf_rubble))))%>%
  mutate(rubble = rowSums(across(c(rubble, sand_rubble))))%>%
  select(motu, site.name, wind.exposure, rat.eradication.status, protection, transect, 
         total_hard_coral, other_fish_inverts, sand, dead_coral, pavement, rubble, turf, cca, macroalgae,
         transect_tape)%>%
  mutate(total = rowSums(across(c(total_hard_coral:transect_tape))))


str(tet_insitu_raw_meta_benthos_wide)
str(tet_video_raw_meta)


tet_benthos_wide_for_corr<-
  full_join(tet_insitu_raw_meta_benthos_wide, tet_video_raw_meta, by = 
              c("motu",  "site.name", "transect", "rat.eradication.status"), suffix = c("_insitu", "_video"))

tet_benthos_wide_for_corr

cor.test(tet_benthos_wide_for_corr$turf, tet_benthos_wide_for_corr$turf_algae) #-0.1389805 


cor.test((tet_benthos_wide_for_corr$turf+tet_benthos_wide_for_corr$pavement_insitu), #in situ
         (tet_benthos_wide_for_corr$turf_algae + tet_benthos_wide_for_corr$pavement_video)) #video
#0.04224298 

cor.test((tet_benthos_wide_for_corr$turf+tet_benthos_wide_for_corr$pavement_insitu), #in situ
         (tet_benthos_wide_for_corr$turf_algae + tet_benthos_wide_for_corr$pavement_video + tet_benthos_wide_for_corr$turf_rubble)) 
#0.02968842

tet_benthos_wide_for_corr<-
  tet_benthos_wide_for_corr%>%
  rename("pavement.sand" = "pavement/sand")

cor.test((tet_benthos_wide_for_corr$turf+tet_benthos_wide_for_corr$pavement_insitu + tet_benthos_wide_for_corr$pavement.sand), #in situ
         (tet_benthos_wide_for_corr$turf_algae + tet_benthos_wide_for_corr$pavement_video)) #video
#0.411273 **BEST AND SIGNIFICANT*** can make sense because pavement/sand implies lots of turf trapping sediment** 


cor.test((tet_benthos_wide_for_corr$turf+tet_benthos_wide_for_corr$pavement_insitu + tet_benthos_wide_for_corr$pavement.sand), #in situ
         (tet_benthos_wide_for_corr$turf_algae + tet_benthos_wide_for_corr$pavement_video + tet_benthos_wide_for_corr$turf_rubble))
#0.4056352 - also fine, but probably keep turf/rubble with rubble because otherwise confusing with pavement...


#try including cca, because not counted in situ
cor.test((tet_benthos_wide_for_corr$turf+tet_benthos_wide_for_corr$pavement_insitu + tet_benthos_wide_for_corr$pavement.sand), #in situ
         (tet_benthos_wide_for_corr$turf_algae + tet_benthos_wide_for_corr$pavement_video + tet_benthos_wide_for_corr$cca))
#0.4222163 - technically best, but weird to not keep cca seperate....


#check cca - none in situ, but always <1% in video**
ggplot(tet_benthos_wide_for_corr, aes(x = motu, y = cca))+
         geom_point(alpha = .2)
       
       #check for rubble:
       cor.test((tet_benthos_wide_for_corr$rubble_insitu), #in situ
                (tet_benthos_wide_for_corr$rubble_video))
       #0.06882663 
       
       
       
       cor.test((tet_benthos_wide_for_corr$rubble_insitu), #in situ
                (tet_benthos_wide_for_corr$rubble_video + tet_benthos_wide_for_corr$sand_rubble))
       #0.4549847
       
       
       cor.test((tet_benthos_wide_for_corr$rubble_insitu), #in situ
                (tet_benthos_wide_for_corr$rubble_video + tet_benthos_wide_for_corr$sand_rubble+tet_benthos_wide_for_corr$turf_rubble))
       #0.453607
       
```

##combine in situ and video, and create corr-plots
```{r}
tet_video_div_comm_dat_w_cover #video
tet_insitu_div_comm_dat_w_cover 

tet_video_div_comm_dat_w_cover_for_cor<-
  tet_video_div_comm_dat_w_cover%>%
  rename_with(~paste0(.,"_video"), -c(motu, site.name, wind.exposure, rat.eradication.status, 
                                      protection, transect))

tet_video_div_comm_dat_w_cover_for_cor


tet_insitu_div_comm_dat_w_cover_for_cor<-
  tet_insitu_div_comm_dat_w_cover%>%
  rename_with(~paste0(.,"_insitu"), -c(motu, site.name, wind.exposure, rat.eradication.status, 
                                       transect))

tet_insitu_div_comm_dat_w_cover_for_cor

tet_benthic_all_for_cor<-full_join(tet_video_div_comm_dat_w_cover_for_cor,
                                   tet_insitu_div_comm_dat_w_cover_for_cor, 
                                   by = c("motu", "site.name", "wind.exposure", "rat.eradication.status", "transect"))

tet_benthic_all_for_cor


#now do correlations:
tet_benthic_all_for_cor_mat<-as.data.frame(tet_benthic_all_for_cor[,7:35])


cor.mtest(tet_benthic_all_for_cor_mat)
correlation.matrix <- cor(tet_benthic_all_for_cor_mat, use = "pairwise.complete.obs")
write.csv(correlation.matrix, "../output/benthic_video_vs_in_situ_corrmatrix.csv")


corrplot(cor(tet_benthic_all_for_cor_mat, use = "pairwise.complete.obs"), type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5, title = "Benthic Video- In situ")

pdf(file = "../output/benthic_video_vs_in_situ_corrplot.pdf")

corrplot(cor(tet_benthic_all_for_cor_mat, use = "pairwise.complete.obs"), type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5, title = "Benthic Video- In situ")

dev.off()

#actually for things we expect to be correlated, looks pretty good....



##re-do corrplot and only comapre things we expect to be correlated----
#not working easily:
tet_benthic_all_for_cor_mat<-as.data.frame(tet_benthic_all_for_cor[,7:35])
tet_benthic_all_for_cor_mat.r<-as.data.frame(tet_benthic_all_for_cor[,c(13:20,29:35)])
correlation.matrix.r1<-cor(tet_benthic_all_for_cor[,13:22], tet_benthic_all_for_cor[,29:35], use = "pairwise.complete.obs")
correlation.matrix.r1

correlation_df_sig<-cor.mtest(tet_benthic_all_for_cor_mat.r, conf.level = 0.95, method = "spearman")
correlation_df_sig

corrplot(corr=cor(tet_benthic_all_for_cor_mat.r, use = "pairwise.complete.obs"),
       #  p.mat=correlation_df_sig$p, sig.level=0.05, 
         type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5, title = "Benthic Video- In situ")

corrplot(corr=correlation.matrix.r1,
       #  p.mat=correlation_df_sig$p, sig.level=0.05, 
         type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5, title = "Benthic Video- In situ")

c_df <- Hmisc::rcorr(cor(tet_benthic_all_for_cor_mat.r), type='spearman')
corrplot(corr=c_df$r[1:11,10:16],  sig.level=0.05, 
         method='color', diag=FALSE, addCoef.col=1, type='upper', insig='blank',
         number.cex=.8)

#SO: just copied and pasted from corrmatrix:
corrs_reduced<-read.csv("../output/benthic_video_vs_in_situ_corrmatix_extracted.csv", stringsAsFactors = TRUE)
corrs_reduced

ggplot(data = corrs_reduced, aes(x = group, y = corr, size = corr, colour = corr))+
  geom_point()+
    scale_size_continuous(range = c(5, 10), limits = c(0,1))+
  #scale_fill_continuous(type = "viridis")+
scale_color_gradient2(low="red", mid="white", high="blue", 
                        limits = c(-1, 1), oob = scales::squish)  +
  theme_bw()+
  ylim(c(0,1))

```




#save all as .Rdata
```{r}
tet_video_div_comm_dat_w_cover #video
tet_insitu_div_comm_dat_w_cover #in situ


#save(tet_video_div_comm_dat_w_cover, tet_insitu_div_comm_dat_w_cover, file = "../output/data/benthic_community_data.Rdata")


```

