---
title: "n15_vs_microbes"
author: "HEE"
date: "2024-06-04"
output: html_document
---

#Load the libraries
```{r}
library(tidyverse)
library(plyr)
library(jtools)
library(multcompView)
library(multcomp)
library(MASS) #for glmms
library(glmmTMB) #for glmms with a beta distribution
library(nlme) #for linear mixed effects models
library(lme4) #for linear mixed effects models
library(emmeans) #for multiple comparisons
library(car) #for qqplots
library(vcd) #for distplots of non-gaussian distributions
library(sjPlot)
library(mgcv) #for running beta distributions
 
```

#Load the data
```{r}
#Bring in Microbes and seabird data
seabirds <- read.csv("../output/n15_seabirds_combined_no_iti.csv", strip.white = T, header = T)
microbes <- read.csv("../../microbiome_analyses/downstream_analyses/integration/output/nov2021_microbiome_metrics.csv")

#recode the site.name category so we can combine with seabird data

microbes$site.name[microbes$site.name == "A1"] <- "Aie_Protected"
microbes$site.name[microbes$site.name == "A2"] <- "Aie_Exposed"
microbes$site.name[microbes$site.name == "Re1"] <- "Reiono_Protected"
microbes$site.name[microbes$site.name == "Re2"] <- "Reiono_Exposed"
microbes$site.name[microbes$site.name == "Rm1"] <- "Rimatuu_Protected"
microbes$site.name[microbes$site.name == "Rm2"] <- "Rimatuu_Exposed"

microbes$site.name <- as.factor(microbes$site.name)
levels(microbes$site.name)


#Combine with seabird data:
microbes.seabirds <- merge(microbes, seabirds, by = "site.name", all = TRUE, no.dups = TRUE)
head(microbes.seabirds)

#Add a seabird level category
microbes.seabirds <-
  microbes.seabirds%>%
  mutate(seabird_level = case_when(breeding_biomass_kgha_side<10 ~"low",
                                   breeding_biomass_kgha_side>10&breeding_biomass_kgha_side <200 ~"mid",
                                   breeding_biomass_kgha_side>200 ~"high"))%>%
  mutate(seabird_level = as.factor(seabird_level))%>%
  mutate(seabird_level = fct_relevel(seabird_level, "low", "mid", "high"))

str(microbes.seabirds$distance.along.transect)
microbes.seabirds$Distance_to_shore <- as.factor(microbes.seabirds$distance.along.transect)

str(microbes.seabirds$seabird_level)

```

#Split into water and coral
```{r}
coral.microbes.seabirds <- microbes.seabirds %>% filter(sample.type == "coral")
water.microbes.seabirds <- microbes.seabirds %>% filter(sample.type ==  "water")

```

*Coral First*

Our predictor variable is algal N15 to reflect nutrient loading in the system
#1. Alpha metrics: Observed
```{r}
hist(coral.microbes.seabirds$Observed) #not normal
qqPlot(coral.microbes.seabirds$Observed) #terrible fit

#Check poisson and nbinomial because these are count data
distplot(coral.microbes.seabirds$Observed, type="poisson") #looks pretty good!

#Predictor variable is algae N15
#Fixed Effects with an interaction = exposure (distance from shore is incorporated in the n15 values, especially when paired here)
#Random effect = site name 

cor.rich.glm <- glmer(Observed~algae.N15*Exposure + (1|site.name), family = "poisson", data = coral.microbes.seabirds)
plot(cor.rich.glm)

hist(resid(cor.rich.glm))
qqnorm(resid(cor.rich.glm)) #not perfect but so much better

summary(cor.rich.glm) #yes significant!
Anova(cor.rich.glm)
#Response: Observed
#                     Chisq Df Pr(>Chisq)    
#algae.N15          73.4964  1    < 2e-16 ***
#Exposure            1.4389  1    0.23031    
#algae.N15:Exposure  3.5884  1    0.05819 .  

##okay, actually looks like no (or marginal) interactions, just mean n15 significant***

test(emtrends(cor.rich.glm, ~ Exposure, var = "algae.N15", adjust = "fdr"))

 #Exposure  algae.N15.trend     SE  df z.ratio p.value
 #Exposed             0.103 0.0243 Inf   4.244  <.0001
 #Protected           0.164 0.0213 Inf   7.695  <.0001

#looks like exposure is significant??

test(emtrends(cor.rich.glm, pairwise~ Exposure, var = "algae.N15", adjust = "fdr"))
 #contrast            estimate     SE  df z.ratio p.value
 #Exposed - Protected  -0.0612 0.0323 Inf  -1.894  0.0582

#but the contrast is no significant effect of exposure. 

#to get effect size, exponentiate (log-link in Poisson):
exp(0.103) #1.108491
exp(0.164) #1.178214


```

#Plot
```{r}
range(coral.microbes.seabirds$algae.N15, na.rm = T)

rich_plot_dat <- emmip(cor.rich.glm,  ~ algae.N15|Exposure, at = list(algae.N15 = seq(2.73, 10.66, 0.1)), CIs = TRUE, plotit=FALSE, type = "response")

range(coral.microbes.seabirds[coral.microbes.seabirds$Exposure == "Protected",]$algae.N15, na.rm = T) #2.73, 10.66
range(coral.microbes.seabirds[coral.microbes.seabirds$Exposure == "Exposed",]$algae.N15, na.rm = T) #4.64, 8.45

rich_plot_dat.protected<-
  rich_plot_dat%>%
  filter(Exposure == "Protected")%>%
  filter(algae.N15>=2.73&algae.N15<=10.66)

rich_plot_dat.exposed<-
  rich_plot_dat%>%
  filter(Exposure == "Exposed")%>%
  filter(algae.N15>=4.64&algae.N15<=8.45)

my_colors <- RColorBrewer::brewer.pal(3, "Dark2")[c(1,2)]
##Plot the richness according to N15 & exposure
p.cor.rich <- ggplot(coral.microbes.seabirds, aes(x = algae.N15, y = Observed, color = Exposure, 
                      fill = Exposure, group = Exposure))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(shape = Exposure))+
  geom_line(data = rich_plot_dat.protected, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = rich_plot_dat.protected, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL, fill = Exposure, color = Exposure), alpha = .2, lwd=0)+
    geom_line(data = rich_plot_dat.exposed, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = rich_plot_dat.exposed, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL, fill = Exposure, color = Exposure), alpha = .2, lwd=0)+
  ylab("Microbial ASV richness \n(Coral Microbiome)") +
  xlab(expression(italic(delta)^15*N))+
  scale_fill_manual(values = my_colors, labels = c('windward', 'leeward'))+
  scale_color_manual(values = my_colors, labels = c('windward', 'leeward')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = "None") +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))

p.cor.rich
#ggsave("../output/seabird-microbes/clean_output/1_coral_micro-richness_model_HE_w_exp.jpg", plot = last_plot(), width = 7, height = 5)

rich_plot_dat_no_exp <- emmip(cor.rich.glm,  ~ algae.N15, at = list(algae.N15 = seq(2.73, 10.66, .1)), CIs = TRUE, plotit=FALSE, type = "response")

##Plot the richness according to N15 & exposure (combined effect line)--=--
ggplot(coral.microbes.seabirds, aes(x = algae.N15, y = Observed))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(fill = Exposure, colour = Exposure, shape = Exposure))+
  geom_line(data = rich_plot_dat_no_exp, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = rich_plot_dat_no_exp, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
  ylab("Observed ASV richness \n(Coral Microbiome)") +
  xlab(expression(italic(delta)^15*N))+
   scale_fill_manual(values = my_colors, labels = c('windward', 'leeward'))+
  scale_color_manual(values = my_colors, labels = c('windward', 'leeward')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = c(0.85, 0.85)) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))



#ggsave("../output/seabird-microbes/clean_output/1_coral_micro-richness_model_HE.jpg", plot = last_plot(), width = 7, height = 5)


```



#Shannon
```{r}
hist(log(coral.microbes.seabirds$Shannon))
qqPlot(log(coral.microbes.seabirds$Shannon))  #log seems better, but not perfect

shannon.lmer<-lmerTest::lmer(log(Shannon) ~ algae.N15*Exposure + (1|site.name), data=coral.microbes.seabirds)
plot(resid(shannon.lmer))
summary(shannon.lmer)
#Fixed effects:
#                            Estimate Std. Error       df t value Pr(>|t|)
#(Intercept)                 -0.30608    0.63850 53.60609  -0.479    0.634
#algae.N15                    0.14783    0.09828 58.00000   1.504    0.138
#ExposureProtected            0.55479    0.74742 36.80599   0.742    0.463
#algae.N15:ExposureProtected -0.11019    0.11504 48.88265  -0.958    0.343

anova(shannon.lmer)
Anova(shannon.lmer)

#Response: log(Shannon)
#                    Chisq Df Pr(>Chisq)
#algae.N15          1.7414  1     0.1870
#Exposure           0.2836  1     0.5944
#algae.N15:Exposure 0.9175  1     0.3381

test(emtrends(shannon.lmer, ~ Exposure, var = "algae.N15", adjust = "fdr", lmer.df = "asymptotic"))

 #Exposure  algae.N15.trend     SE  df z.ratio p.value
 #Exposed            0.1478 0.0983 Inf   1.504  0.2651
 #Protected          0.0376 0.0598 Inf   0.630  0.5290

#No significant interaction or effect of exposure on shannon div

test(emtrends(shannon.lmer, pairwise~ Exposure, var = "algae.N15", adjust = "fdr", lmer.df = "asymptotic"))

#contrasts
# contrasts
 #contrast            estimate    SE  df z.ratio p.value
 #Exposed - Protected     0.11 0.115 Inf   0.958  0.3381

#Same non-significant results when NOT using an asymptotic 
```

#Plot
```{r}
range(coral.microbes.seabirds$algae.N15, na.rm = T)

sh_plot_dat <- emmip(shannon.lmer,  ~ algae.N15|Exposure, at = list(algae.N15 = seq(2.73, 10.66, 0.1)), CIs = TRUE, plotit=FALSE, type = "response")

range(coral.microbes.seabirds[coral.microbes.seabirds$Exposure == "Protected",]$algae.N15, na.rm = T) #2.73, 10.66
range(coral.microbes.seabirds[coral.microbes.seabirds$Exposure == "Exposed",]$algae.N15, na.rm = T) #4.64, 8.45

sh_plot_dat.protected<-
  sh_plot_dat%>%
  filter(Exposure == "Protected")%>%
  filter(algae.N15>=2.73&algae.N15<=10.66)

sh_plot_dat.exposed<-
  sh_plot_dat%>%
  filter(Exposure == "Exposed")%>%
  filter(algae.N15>=4.64&algae.N15<=8.45)


my_colors <- RColorBrewer::brewer.pal(3, "Dark2")[c(1,2)]

p.cor.sh <- ggplot(coral.microbes.seabirds, aes(x = algae.N15, y = log(Shannon), color = Exposure, 
                      fill = Exposure, group = Exposure))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(shape = Exposure))+
  geom_line(data = sh_plot_dat.protected, aes(x = algae.N15, y = log(yvar)))+
   geom_ribbon(data = sh_plot_dat.protected, aes(x = algae.N15, y = log(yvar), ymin = log(LCL), ymax=log(UCL), fill = Exposure, color = Exposure), alpha = .2, lwd=0)+
    geom_line(data = sh_plot_dat.exposed, aes(x = algae.N15, y = log(yvar)))+
   geom_ribbon(data = sh_plot_dat.exposed, aes(x = algae.N15, y = log(yvar), ymin = log(LCL), ymax=log(UCL), fill = Exposure, color = Exposure), alpha = .2, lwd=0)+
  ylab("Microbial Shannon Diversity \n (Coral Microbiome)") +
  xlab(expression(italic(delta)^15*N))+
  scale_fill_manual(values = my_colors, labels = c('windward', 'leeward'))+
  scale_color_manual(values = my_colors, labels = c('windward', 'leeward')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = "None") +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))
p.cor.sh

##without exposure 
sh_plot_dat_no_exp <- emmip(shannon.lmer,  ~ algae.N15, at = list(algae.N15 = seq(2.73, 10.66, .1)), CIs = TRUE, plotit=FALSE, type = "response")

##Plot the richness according to N15 & exposure (combined effect line)--=--
ggplot(coral.microbes.seabirds, aes(x = algae.N15, y = Shannon))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(fill = Exposure, colour = Exposure, shape = Exposure))+
  geom_line(data = sh_plot_dat_no_exp, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = sh_plot_dat_no_exp, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
  ylab("log(Microbial Shannon Diversity) \n") +
  xlab(expression(italic(delta)^15*N))+
   scale_fill_manual(values = my_colors, labels = c('windward', 'leeward'))+
  scale_color_manual(values = my_colors, labels = c('windward', 'leeward')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = "None") +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))



#ggsave("../output/seabird-microbes/clean_output/2_coral_micro-shannon_model_HE.jpg", plot = last_plot(), width = 7, height = 5)

```

#Evenness

```{r}
hist((coral.microbes.seabirds$Evenness)) #not bad
qqPlot((coral.microbes.seabirds$Evenness))
#gaussian

cor.even.lmer<-lmerTest::lmer(Evenness ~ algae.N15* Exposure + (1|site.name), data=coral.microbes.seabirds)
plot(resid(cor.even.lmer)) #very nice residuals

summary(cor.even.lmer)
Anova(cor.even.lmer)
#Analysis of Deviance Table (Type II Wald chisquare tests)

#Response: Evenness
#                    Chisq Df Pr(>Chisq)   
#algae.N15          1.4192  1   0.233529   
#Exposure           0.0315  1   0.859161   
#algae.N15:Exposure 6.8847  1   0.008694 **

#yes evennes has an interaction effect (perhaps unsurprising)


anova(cor.even.lmer)
#Type III Analysis of Variance Table with Satterthwaite's method
##                    Sum Sq Mean Sq NumDF DenDF F value   Pr(>F)   
#algae.N15          0.20637 0.20637     1    58  7.1627 0.009661 **
#Exposure           0.19628 0.19628     1    58  6.8124 0.011500 * 
#algae.N15:Exposure 0.19836 0.19836     1    58  6.8847 0.011092 * 

test(emtrends(cor.even.lmer, ~ Exposure, var = "algae.N15", adjust = "fdr", lmer.df = "asymptotic"))

 #Exposure  algae.N15.trend     SE  df z.ratio p.value
 #Exposed          0.096572 0.0335 Inf   2.881  0.0079*
 #Protected        0.000956 0.0143 Inf   0.067  0.9467

test(emtrends(cor.even.lmer, pairwise~ Exposure, var = "algae.N15", adjust = "fdr", lmer.df = "asymptotic"))
#contrasts
#  contrast            estimate     SE  df z.ratio p.value
 #Exposed - Protected   0.0956 0.0364 Inf   2.624  0.0087

#Significant contrast! And stays significant if using non-asymptotic df 

```

#Plot
```{r}

ev_plot_dat <- emmip(cor.even.lmer,  ~ algae.N15|Exposure, at = list(algae.N15 = seq(2.73, 10.66, 0.1)), CIs = TRUE, plotit=FALSE, type = "response")
ev_plot_dat.protected<-
  ev_plot_dat%>%
  filter(Exposure == "Protected")%>%
  filter(algae.N15>=2.73&algae.N15<=10.66)

ev_plot_dat.exposed<-
  ev_plot_dat%>%
  filter(Exposure == "Exposed")%>%
  filter(algae.N15>=4.64&algae.N15<=8.45)


my_colors <- RColorBrewer::brewer.pal(3, "Dark2")[c(1,2)]

p.cor.even <- ggplot(coral.microbes.seabirds, aes(x = algae.N15, y = Evenness, color = Exposure, 
                      fill = Exposure, group = Exposure))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(shape = Exposure))+
  geom_line(data = ev_plot_dat.protected, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = ev_plot_dat.protected, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL, fill = Exposure, color = Exposure), alpha = .2, lwd=0)+
    geom_line(data = ev_plot_dat.exposed, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = ev_plot_dat.exposed, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL, fill = Exposure, color = Exposure), alpha = .2, lwd=0)+
  ylab("Microbial Evennness \n(Coral Microbiome)") +
  xlab(expression(italic(delta)^15*N))+
  scale_fill_manual(values = my_colors, labels = c('windward', 'leeward'))+
  scale_color_manual(values = my_colors, labels = c('windward', 'leeward')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = c(0.85, 0.15),
        legend.backgroun = element_rect(fill = "transparent")) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))

p.cor.even
#WEIRD

#ggsave("../output/seabird-microbes/clean_output/3_coral_micro-evenness_model_HE.jpg", plot = last_plot(), width = 7, height = 5)


```

#Plot
```{r}
library(cowplot)

#1) p.cor.sh
#2) p.cor.even

coral_microbe_supp_plots<-cowplot::plot_grid(p.cor.sh, p.cor.even, labels = "auto", label_fontface = "plain")
coral_microbe_supp_plots

ggsave("../output/seabird-microbes/coral_microbe_supp_divplots.jpg", plot = coral_microbe_supp_plots, width = 10, height = 4)
ggsave("../output/seabird-microbes/coral_microbe_supp_divplots.pdf", plot = coral_microbe_supp_plots, width = 10, height = 4)
```


#Faith's Phylogenetic Diversity

```{r}
hist(log(coral.microbes.seabirds$FaithPD))
plot(log(FaithPD) ~ algae.N15, coral.microbes.seabirds)
qqPlot(log(coral.microbes.seabirds$FaithPD)) #not bad, not great

cor.fpd.lmer<-lmerTest::lmer(FaithPD~ algae.N15*Exposure + (1|site.name), data=coral.microbes.seabirds)
plot(resid(cor.fpd.lmer)) #resids look good

summary(cor.fpd.lmer)
#Fixed effects:
#                            Estimate Std. Error      df t value Pr(>|t|)
#(Intercept)                   5.2001    11.4092 52.8892   0.456    0.650
#algae.N15                     0.9380     1.7683 57.7601   0.530    0.598
#ExposureProtected            -5.1655    13.1897 35.3462  -0.392    0.698
#algae.N15:ExposureProtected   0.2961     2.0459 45.3883   0.145    0.886
Anova(cor.fpd.lmer)
#Response: FaithPD
#                    Chisq Df Pr(>Chisq)
#algae.N15          1.6990  1     0.1924
#Exposure           0.7677  1     0.3809
#algae.N15:Exposure 0.0209  1     0.8849
anova(cor.fpd.lmer)
#Type III Analysis of Variance Table with Satterthwaite's method
#                   Sum Sq Mean Sq NumDF  DenDF F value Pr(>F)
#algae.N15          77.805  77.805     1 45.388  1.1271 0.2940
#Exposure           10.587  10.587     1 35.346  0.1534 0.6977
#algae.N15:Exposure  1.446   1.446     1 45.388  0.0209 0.8856

test(emtrends(cor.fpd.lmer, ~ Exposure, var = "algae.N15", adjust = "fdr", lmer.df = "asymptotic"))
#Exposure  algae.N15.trend     SE  df z.ratio p.value
# Exposed             0.938 1.77 Inf   0.530  0.5958
# Protected           1.234 1.03 Inf   1.199  0.4608
test(emtrends(cor.fpd.lmer, pairwise~ Exposure, var = "algae.N15", adjust = "fdr", lmer.df = "asymptotic"))
#contrasts
# contrast            estimate     SE  df z.ratio p.value
# Exposed - Protected   -0.296 2.05 Inf  -0.145  0.8849

#Yup, nothing significant

#try not asymptotic
test(emtrends(cor.fpd.lmer, pairwise~ Exposure, var = "algae.N15", adjust = "fdr"))
#Same as above.

```

#Plot
```{r}
range(coral.microbes.seabirds$algae.N15, na.rm = T)

fpd_plot_dat <- emmip(cor.fpd.lmer,  ~ algae.N15|Exposure, at = list(algae.N15 = seq(2.73, 10.66, 0.1)), CIs = TRUE, plotit=FALSE, type = "response")

range(coral.microbes.seabirds[coral.microbes.seabirds$Exposure == "Protected",]$algae.N15, na.rm = T) #2.73, 10.66
range(coral.microbes.seabirds[coral.microbes.seabirds$Exposure == "Exposed",]$algae.N15, na.rm = T) #4.64, 8.45

fpd_plot_dat.protected<-
  fpd_plot_dat%>%
  filter(Exposure == "Protected")%>%
  filter(algae.N15>=2.73&algae.N15<=10.66)

fpd_plot_dat.exposed<-
  fpd_plot_dat%>%
  filter(Exposure == "Exposed")%>%
  filter(algae.N15>=4.64&algae.N15<=8.45)


my_colors <- RColorBrewer::brewer.pal(3, "Dark2")[c(1,2)]

ggplot(coral.microbes.seabirds, aes(x = algae.N15, y = FaithPD, color = Exposure, 
                      fill = Exposure, group = Exposure))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(shape = Exposure))+
  geom_line(data = fpd_plot_dat.protected, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = fpd_plot_dat.protected, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL, fill = Exposure, color = Exposure), alpha = .2, lwd=0)+
    geom_line(data = fpd_plot_dat.exposed, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = fpd_plot_dat.exposed, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL, fill = Exposure, color = Exposure), alpha = .2, lwd=0)+
  ylab("Microbial Shannon Diveristy \n") +
  xlab(expression(italic(delta)^15*N))+
  scale_fill_manual(values = my_colors, labels = c('windward', 'leeward'))+
  scale_color_manual(values = my_colors, labels = c('windward', 'leeward')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = c(0.85, 0.82)) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))


##without exposure 
fpd_plot_dat_no_exp <- emmip(cor.fpd.lmer,  ~ algae.N15, at = list(algae.N15 = seq(2.73, 10.66, .1)), CIs = TRUE, plotit=FALSE, type = "response")

##Plot the richness according to N15 & exposure (combined effect line)--=--
ggplot(coral.microbes.seabirds, aes(x = algae.N15, y = FaithPD))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(fill = Exposure, colour = Exposure, shape = Exposure))+
  geom_line(data = fpd_plot_dat_no_exp, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = fpd_plot_dat_no_exp, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
  ylab("Microbial Faith's Phylogentic Diversity \n") +
  xlab(expression(italic(delta)^15*N))+
   scale_fill_manual(values = my_colors, labels = c('windward', 'leeward'))+
  scale_color_manual(values = my_colors, labels = c('windward', 'leeward')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = c(0.85, 0.75)) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))



ggsave("../output/seabird-microbes/clean_output/3_coral_micro-faithpd_model_HE.jpg", plot = last_plot(), width = 7, height = 5)

```


#Remove the NMDS axes since we include the NMDS plots

*Water Alpha Diversity*

#Observed
```{r}
hist(water.microbes.seabirds$Observed) #not normal
qqPlot(water.microbes.seabirds$Observed) #not bad

#Check poisson 
distplot(water.microbes.seabirds$Observed, type="poisson") #looks literally perfect!
#using a Poisson distribution

wat.rich.glm <- glmer(Observed~algae.N15*Exposure + (1|site.name), family = "poisson", data = water.microbes.seabirds)
plot(wat.rich.glm)

hist(resid(wat.rich.glm))
qqnorm(resid(wat.rich.glm)) #not bad

summary(wat.rich.glm) 
#Fixed effects:
#                             Estimate Std. Error z value Pr(>|z|)    
#(Intercept)                  5.980877   0.302296  19.785  < 2e-16 ***
#algae.N15                    0.057467   0.008926   6.438 1.21e-10 ***
#ExposureProtected            0.125538   0.425414   0.295    0.768    
#algae.N15:ExposureProtected -0.044306   0.010825  -4.093 4.26e-05 ***
Anova(wat.rich.glm)
#Response: Observed
#                     Chisq Df Pr(>Chisq)    
#algae.N15          29.3138  1  6.156e-08 ***
#Exposure            0.1299  1     0.7185    
#algae.N15:Exposure 16.7527  1  4.258e-05 ***
anova(wat.rich.glm)
#Analysis of Variance Table
#                   npar  Sum Sq Mean Sq F value
#algae.N15             1 29.3276 29.3276 29.3276
#Exposure              1  0.1299  0.1299  0.1299
#algae.N15:Exposure    1 16.7518 16.7518 16.7518

test(emtrends(wat.rich.glm, ~ Exposure, var = "algae.N15", adjust = "fdr"))

#Exposure  algae.N15.trend      SE  df z.ratio p.value
# Exposed            0.0575 0.00893 Inf   6.438  <.0001
# Protected          0.0132 0.00612 Inf   2.149  0.0317


test(emtrends(wat.rich.glm, pairwise~ Exposure, var = "algae.N15", adjust = "fdr"))
#contrasts
# contrast            estimate     SE  df z.ratio p.value
# Exposed - Protected   0.0443 0.0108 Inf   4.093  <.0001

```

#Plot

```{r}
range(water.microbes.seabirds$algae.N15, na.rm = T) #these should all be the same as above

rich_plot_dat <- emmip(wat.rich.glm,  ~ algae.N15|Exposure, at = list(algae.N15 = seq(2.73, 10.66, 0.1)), CIs = TRUE, plotit=FALSE, type = "response")

range(water.microbes.seabirds[water.microbes.seabirds$Exposure == "Protected",]$algae.N15, na.rm = T) #2.73, 10.66
range(water.microbes.seabirds[water.microbes.seabirds$Exposure == "Exposed",]$algae.N15, na.rm = T) #4.64, 8.45

rich_plot_dat.protected<-
  rich_plot_dat%>%
  filter(Exposure == "Protected")%>%
  filter(algae.N15>=2.73&algae.N15<=10.66)

rich_plot_dat.exposed<-
  rich_plot_dat%>%
  filter(Exposure == "Exposed")%>%
  filter(algae.N15>=4.64&algae.N15<=8.45)

my_colors <- RColorBrewer::brewer.pal(3, "Dark2")[c(1,2)]
##Plot the richness according to N15 & exposure
p.wat.rich <- ggplot(water.microbes.seabirds, aes(x = algae.N15, y = Observed, color = Exposure, 
                      fill = Exposure, group = Exposure))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(shape = Exposure))+
  geom_line(data = rich_plot_dat.protected, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = rich_plot_dat.protected, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL, fill = Exposure, color = Exposure), alpha = .2, lwd=0)+
    geom_line(data = rich_plot_dat.exposed, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = rich_plot_dat.exposed, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL, fill = Exposure, color = Exposure), alpha = .2, lwd=0)+
  ylab("Microbial ASV richness \n(Seawater Microbiome)") +
  xlab(expression(italic(delta)^15*N))+
  scale_fill_manual(values = my_colors, labels = c('windward', 'leeward'))+
  scale_color_manual(values = my_colors, labels = c('windward', 'leeward')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = c(0.85, 0.85)) +
  #theme(legend.position = "none") +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))

#ggsave("../output/seabird-microbes/clean_output/4_water_micro-richness_model_w_exp_HE.jpg", plot = last_plot(), width = 7, height = 5)

rich_plot_dat_no_exp <- emmip(wat.rich.glm,  ~ algae.N15, at = list(algae.N15 = seq(2.73, 10.66, .1)), CIs = TRUE, plotit=FALSE, type = "response")

##Plot the richness according to N15 & exposure (combined effect line)--=--
ggplot(water.microbes.seabirds, aes(x = algae.N15, y = Observed))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(fill = Exposure, colour = Exposure, shape = Exposure))+
  geom_line(data = rich_plot_dat_no_exp, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = rich_plot_dat_no_exp, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
  ylab("Microbial Observed ASV richness \n") +
  xlab(expression(italic(delta)^15*N))+
   scale_fill_manual(values = my_colors, labels = c('windward', 'leeward'))+
  scale_color_manual(values = my_colors, labels = c('windward', 'leeward')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = c(0.85, 0.75)) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))



#ggsave("../output/seabird-microbes/clean_output/4_water_micro-richness_model_HE.jpg", plot = last_plot(), width = 7, height = 5)


#try plotting by motu-----
my_colors_3 <- RColorBrewer::brewer.pal(3, "Dark2")[c(1:3)]
ggplot(water.microbes.seabirds, aes(x = algae.N15, y = Observed))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(fill = motu, colour = motu, shape = Exposure))+
  geom_line(data = rich_plot_dat_no_exp, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = rich_plot_dat_no_exp, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
  ylab("Microbial Observed ASV Richness \n") +
  xlab(expression(italic(delta)^15*N))+
   scale_fill_manual(values = my_colors_3, labels = c('Aie', 'Reiono', 'Rimatuu'))+
  scale_color_manual(values = my_colors_3, labels = c('Aie', 'Reiono', 'Rimatuu')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = c(0.9, 0.7)) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))


#looks like driven by protected side of aie, what happens when removed?-----

```

#Can we remove protected side of Aie?
```{r}
water.microbes.seabirds.noaiepro <- filter(water.microbes.seabirds, site.name != "Aie_Protected")

wat.rich.glm.noaie <- glmer(Observed~algae.N15*Exposure + (1|site.name), family = "poisson", data = water.microbes.seabirds.noaiepro)
plot(wat.rich.glm.noaie)

Anova(wat.rich.glm.noaie)
#Response: Observed
#                    Chisq Df Pr(>Chisq)
#algae.N15          31.3892  1  2.112e-08 ***
#Exposure            5.0686  1  0.0243637 *  
#algae.N15:Exposure 14.4095  1  0.0001471 ***


#plot it-----
rich_plot_dat <- emmip(wat.rich.glm.noaie,  ~ algae.N15|Exposure, at = list(algae.N15 = seq(2.73, 10.66, 0.1)), CIs = TRUE, plotit=FALSE, type = "response")

range(water.microbes.seabirds.noaiepro[water.microbes.seabirds.noaiepro$Exposure == "Protected",]$algae.N15, na.rm = T) #2.73, 10.66
range(water.microbes.seabirds.noaiepro[water.microbes.seabirds.noaiepro$Exposure == "Exposed",]$algae.N15, na.rm = T) #4.64, 8.45

rich_plot_dat.protected<-
  rich_plot_dat%>%
  filter(Exposure == "Protected")%>%
  filter(algae.N15>=2.73&algae.N15<=10.66)

rich_plot_dat.exposed<-
  rich_plot_dat%>%
  filter(Exposure == "Exposed")%>%
  filter(algae.N15>=4.64&algae.N15<=8.45)

my_colors <- RColorBrewer::brewer.pal(3, "Dark2")[c(1,2)]
##Plot the richness according to N15 & exposure
p.rich.wat.noaie <- ggplot(water.microbes.seabirds.noaiepro, aes(x = algae.N15, y = Observed, 
                                                                 color = Exposure, fill = Exposure, 
                                                                 group = Exposure))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(shape = Exposure))+
  geom_line(data = rich_plot_dat.protected, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = rich_plot_dat.protected, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL, fill = Exposure, color = Exposure), alpha = .2, lwd=0)+
    geom_line(data = rich_plot_dat.exposed, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = rich_plot_dat.exposed, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL, fill = Exposure, color = Exposure), alpha = .2, lwd=0)+
  ylab("Microbial ASV richness \n(Seawater Microbiome)") +
  xlab(expression(italic(delta)^15*N))+
  scale_fill_manual(values = my_colors, labels = c('windward', 'leeward'))+
  scale_color_manual(values = my_colors, labels = c('windward', 'leeward')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = c(0.1, 0.9),
        legend.background = element_rect(fill='transparent')) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))

p.rich.wat.noaie
ggsave("../output/seabird-microbes/water_microbe_richness-noaiepro.jpg", plot = p.rich.wat.noaie, width = 7, height = 5)
ggsave("../output/seabird-microbes/water_microbe_richness-noaiepro.pdf", plot = p.rich.wat.noaie, width = 7, height = 5)

#ggsave("../output/seabird-microbes/clean_output/4_water_micro-richness_model_w_exp_no_aie_HE.jpg", plot = #last_plot(), width = 7, height = 5)


```


#Shannon
```{r}
hist(water.microbes.seabirds$Shannon) #not great, looks bimodal??

plot(Shannon ~ algae.N15, water.microbes.seabirds)
qqPlot((water.microbes.seabirds$Shannon)) #oooooof

ggplot(water.microbes.seabirds, aes(x = algae.N15, y = Shannon)) +
  geom_point(aes(color = site.name)) ##This is definitely driven by location differences, confounded with rat history


wat.sh.lmer <-lmerTest::lmer(Shannon ~ algae.N15* Exposure + (1|site.name), data=water.microbes.seabirds)
hist(resid(wat.sh.lmer)) #the residual plot actually isnt that crazy
plot(resid(wat.sh.lmer))
qqnorm(resid(wat.sh.lmer)) # a little wonky


summary(wat.sh.lmer)
#Fixed effects:
#                             Estimate Std. Error        df t value Pr(>|t|)    
#(Intercept)                  4.400460   0.844579 17.134526   5.210  6.9e-05 ***
#algae.N15                    0.006689   0.098828 57.677352   0.068    0.946    
#ExposureProtected            0.223576   1.094878 12.477228   0.204    0.841    
#algae.N15:ExposureProtected -0.041042   0.118840 58.916341  -0.345    0.731   
Anova(wat.sh.lmer)
#Response: Shannon
#                    Chisq Df Pr(>Chisq)
#algae.N15          0.1562  1     0.6927
#Exposure           0.0015  1     0.9687
#algae.N15:Exposure 0.1193  1     0.7298

anova(wat.sh.lmer)
#Type III Analysis of Variance Table with Satterthwaite's method
#                      Sum Sq   Mean Sq NumDF  DenDF F value Pr(>F)
#algae.N15          0.0108917 0.0108917     1 58.916  0.0542 0.8167
#Exposure           0.0083816 0.0083816     1 12.477  0.0417 0.8415
#algae.N15:Exposure 0.0239740 0.0239740     1 58.916  0.1193 0.7311

#No significant differences. 

```

#Plot
```{r}
#Can we plot coloured instead by site though?

sh_plot_dat <- emmip(wat.sh.lmer,  ~ algae.N15|Exposure, at = list(algae.N15 = seq(2.73, 10.66, 0.1)), CIs = TRUE, plotit=FALSE, type = "response")

sh_plot_dat.protected<-
  sh_plot_dat%>%
  filter(Exposure == "Protected")%>%
  filter(algae.N15>=2.73&algae.N15<=10.66)

sh_plot_dat.exposed<-
  sh_plot_dat%>%
  filter(Exposure == "Exposed")%>%
  filter(algae.N15>=4.64&algae.N15<=8.45)

my_colors <- RColorBrewer::brewer.pal(3, "Dark2")[c(1,2)]
##Plot the shannon according to N15 & exposure
ggplot(water.microbes.seabirds, aes(x = algae.N15, y = Shannon, color = Exposure, 
                      fill = Exposure, group = Exposure))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(shape = Exposure))+
  geom_line(data = sh_plot_dat.protected, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = sh_plot_dat.protected, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL, fill = Exposure, color = Exposure), alpha = .2, lwd=0)+
    geom_line(data = sh_plot_dat.exposed, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = sh_plot_dat.exposed, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL, fill = Exposure, color = Exposure), alpha = .2, lwd=0)+
  ylab("Microbial Shannon Diversity \n(Seawater Microbiome)") +
  xlab(expression(italic(delta)^15*N))+
  scale_fill_manual(values = my_colors, labels = c('windward', 'leeward'))+
  scale_color_manual(values = my_colors, labels = c('windward', 'leeward')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = c(0.85, 0.82)) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))


#This is driven by motu really, so let's colour by motu 

sh_plot_dat_no_exp <- emmip(wat.sh.lmer,  ~ algae.N15, at = list(algae.N15 = seq(2.73, 10.66, .1)), CIs = TRUE, plotit=FALSE, type = "response")

my_colors_6 <- RColorBrewer::brewer.pal(6, "Dark2")[c(1:6)]

p.wat.sh <- ggplot(water.microbes.seabirds, aes(x = algae.N15, y = Shannon))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(fill = motu, colour = motu, shape = Exposure))+
  geom_line(data = sh_plot_dat_no_exp, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = sh_plot_dat_no_exp, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
  ylab("Microbial Shannon Diversity \n(Seawater Microbiome)") +
  xlab(expression(italic(delta)^15*N))+
   scale_fill_manual(values = my_colors_6, labels = c('Aie',  'Reiono', 'Rimatuu')) +
  scale_color_manual(values = my_colors_6, labels = c('Aie',  'Reiono', 'Rimatuu')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = "None") +
  #theme(legend.position = c(0.15, 0.3),
      #  legend.background = element_rect(fill='transparent')) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))

p.wat.sh
#ggsave( "../output/seabird-microbes/water_shannon_motu.jpg",plot = p.wat.sh, width = 7, height = 5)
#ggsave( "../output/seabird-microbes/water_shannon_motu.pdf",plot = p.wat.sh, width = 7, height = 5)


```


#Evenness
```{r}
hist((water.microbes.seabirds$Evenness)) #a bit simialr to shannon div (makes sense)

plot(Evenness ~ algae.N15, water.microbes.seabirds)
qqPlot(water.microbes.seabirds$Evenness) #a bit similar to shannon (makes sense)

ggplot(water.microbes.seabirds, aes(x = algae.N15, y = Evenness)) +
  geom_point(aes(color = site.name)) ##This is definitely driven by location differences, confounded with rat history

#Can we get away with what we did for shannon?
wat.even.lmer <-lmerTest::lmer(Evenness~ algae.N15*Exposure + (1|site.name), data=water.microbes.seabirds)
plot(resid(wat.even.lmer))
qqnorm(resid(wat.even.lmer)) #not great 


summary(wat.even.lmer)
#Fixed effects:
#                             Estimate Std. Error        df t value Pr(>|t|)    
#(Intercept)                  0.736876   0.094526 24.861698   7.795  3.9e-08 ***
#algae.N15                   -0.005792   0.012045 58.003959  -0.481    0.632    
#ExposureProtected            0.011996   0.120146 17.342331   0.100    0.922    
#algae.N15:ExposureProtected -0.001366   0.014437 59.640046  -0.095    0.925    

Anova(wat.even.lmer)
#RResponse: Evenness
##                    Chisq Df Pr(>Chisq)
#algae.N15          1.0315  1     0.3098
#Exposure           0.0019  1     0.9651
#algae.N15:Exposure 0.0090  1     0.9246

anova(wat.even.lmer)
#Type III Analysis of Variance Table with Satterthwaite's method
#                       Sum Sq    Mean Sq NumDF  DenDF F value Pr(>F)
#algae.N15          0.00240963 0.00240963     1 59.640  0.8047 0.3733
#Exposure           0.00002985 0.00002985     1 17.342  0.0100 0.9216
#algae.N15:Exposure 0.00002683 0.00002683     1 59.640  0.0090 0.9249


#Just a quick trial by motu - if it's not significantly different by distance from shore or exposure, how about just motu?
motu.mod <- lm(Evenness ~ algae.N15*motu, data = water.microbes.seabirds)

anova(motu.mod)
#Response: Evenness
#               Df  Sum Sq  Mean Sq F value    Pr(>F)    
#algae.N15       1 0.01741 0.017414  5.8060   0.01911 *  
#motu            2 0.37092 0.185458 61.8327 3.321e-15 ***
#algae.N15:motu  2 0.00660 0.003302  1.1008   0.33935    
#Residuals      59 0.17696 0.002999   

#yes this is significantly different by motu

#Not going to plot 

```


#Faith's Phylogenetic Diversity
```{r}
hist(water.microbes.seabirds$FaithPD) #not bad

plot(FaithPD ~ algae.N15, water.microbes.seabirds) #pretty good
qqPlot(water.microbes.seabirds$FaithPD) #not the worst


wat.fpd.lmer <-lmerTest::lmer(FaithPD ~ algae.N15*Exposure + (1|site.name), data=water.microbes.seabirds)
plot(resid(wat.fpd.lmer))
qqnorm(resid(wat.fpd.lmer)) #actually looks pretty good

summary(wat.fpd.lmer)
#Fixed effects:
#                            Estimate Std. Error     df t value Pr(>|t|)  
#(Intercept)                   48.704     23.931 16.201   2.035   0.0585 .
#algae.N15                      3.393      2.760 57.634   1.229   0.2239  
#ExposureProtected             14.872     31.113 11.892   0.478   0.6413  
#algae.N15:ExposureProtected   -2.651      3.320 58.817  -0.799   0.4277  

Anova(wat.fpd.lmer)
#Response: FaithPD
 #                   Chisq Df Pr(>Chisq)
#algae.N15          1.0353  1     0.3089
#Exposure           0.0048  1     0.9445
#algae.N15:Exposure 0.6379  1     0.4245

anova(wat.fpd.lmer)
#Type III Analysis of Variance Table with Satterthwaite's method
#                    Sum Sq Mean Sq NumDF  DenDF F value Pr(>F)
#algae.N15          243.008 243.008     1 58.817  1.5511 0.2179
#Exposure            35.796  35.796     1 11.892  0.2285 0.6413
#algae.N15:Exposure  99.932  99.932     1 58.817  0.6379 0.4277

test(emtrends(wat.fpd.lmer, ~ Exposure, var = "algae.N15", adjust = "fdr"))

# Exposure  algae.N15.trend   SE   df t.ratio p.value
# Exposed             3.393 2.77 57.6   1.226  0.4503
# Protected           0.742 1.89 60.6   0.393  0.6958


test(emtrends(wat.fpd.lmer, pairwise~ Exposure, var = "algae.N15", adjust = "fdr"))
#$contrasts
# contrast            estimate   SE   df t.ratio p.value
# Exposed - Protected     2.65 3.35 58.8   0.792  0.4318

#nothing significant - not going to plot
```



*Top Taxa*

#Corals 

```{r}
hist(coral.microbes.seabirds$RelAbund_Endozoicomonas)
qqPlot(coral.microbes.seabirds$RelAbund_Endozoicomonas)#terrible
#Hmmm can't use log-link because it is skewed the opposite way. 
#What about proportional data?

##Since Endoz are skewed toward 1, what about using a beta distribution?
?glmmTMB()

#Cool let's loop! 
head(coral.microbes.seabirds)
###If they are all betas, can we transform & then loop it 
beta_trans_coral_microbes <- dplyr::mutate(coral.microbes.seabirds, RelAbund_Cellvibrionales_Aestuariicella = (RelAbund_Cellvibrionales_Aestuariicella*(n()-1) + 0.5)/n())
beta_trans_coral_microbes <- dplyr::mutate(beta_trans_coral_microbes, RelAbund_Alteromonadales_Agaribacter = (RelAbund_Alteromonadales_Agaribacter*(n()-1) + 0.5)/n())
beta_trans_coral_microbes <- dplyr::mutate(beta_trans_coral_microbes, RelAbund_Cytophagales_Candidatus_Amoebophilus = (RelAbund_Cytophagales_Candidatus_Amoebophilus*(n()-1) + 0.5)/n())
beta_trans_coral_microbes <- dplyr::mutate(beta_trans_coral_microbes, RelAbund_Endozoicomonas = (RelAbund_Endozoicomonas*(n()-1) + 0.5)/n())
beta_trans_coral_microbes <- dplyr::mutate(beta_trans_coral_microbes, RelAbund_Alteromonadales_Glaciecola = (RelAbund_Alteromonadales_Glaciecola*(n()-1) + 0.5)/n())
beta_trans_coral_microbes <- dplyr::mutate(beta_trans_coral_microbes, RelAbund_Oceanospirillales_Neptuniibacter = (RelAbund_Oceanospirillales_Neptuniibacter*(n()-1) + 0.5)/n())
beta_trans_coral_microbes <- dplyr::mutate(beta_trans_coral_microbes, RelAbund_Cellvibrionales_Porticoccus = (RelAbund_Cellvibrionales_Porticoccus*(n()-1) + 0.5)/n())
beta_trans_coral_microbes <- dplyr::mutate(beta_trans_coral_microbes, RelAbund_Woesearchaeales_SCGC_AAA286E23 = (RelAbund_Woesearchaeales_SCGC_AAA286E23*(n()-1) + 0.5)/n())
beta_trans_coral_microbes <- dplyr::mutate(beta_trans_coral_microbes, RelAbund_Litoricola = (RelAbund_Litoricola*(n()-1) + 0.5)/n())
beta_trans_coral_microbes <- dplyr::mutate(beta_trans_coral_microbes, RelAbund_Uncultured_Alteromonadaceaeae = (RelAbund_Uncultured_Alteromonadaceaeae*(n()-1) + 0.5)/n())

print(colnames(beta_trans_coral_microbes))
columns <- c( "RelAbund_Cellvibrionales_Aestuariicella" , "RelAbund_Alteromonadales_Agaribacter",
              "RelAbund_Cytophagales_Candidatus_Amoebophilus", "RelAbund_Endozoicomonas","RelAbund_Alteromonadales_Glaciecola",
              "RelAbund_Oceanospirillales_Neptuniibacter","RelAbund_Cellvibrionales_Porticoccus",
              "RelAbund_Woesearchaeales_SCGC_AAA286E23","RelAbund_Litoricola","RelAbund_Uncultured_Alteromonadaceaeae")
#Loop
dat <- beta_trans_coral_microbes
models <- list()
for (i in columns) {
  f <- formula(paste(i, "~ algae.N15*Exposure + (1|site.name)"))
  models[[i]] <- glmmTMB(f, data=dat, family = beta_family(), na.action = na.omit)
  print(Anova(models[[i]])) 

}


#Interesting, none of the top taxa have any significant differences..
#only marginal effects:
#Response: RelAbund_Oceanospirillales_Neptuniibacter
#                    Chisq Df Pr(>Chisq)  
#algae.N15          1.0170  1    0.31323  
#Exposure           1.4356  1    0.23085  
#algae.N15:Exposure 3.6000  1    0.05778 .

#Response: RelAbund_Endozoicomonas
 #                   Chisq Df Pr(>Chisq)  
#algae.N15          3.3976  1    0.06529 .
#Exposure           0.4147  1    0.51959  
#algae.N15:Exposure 0.0979  1    0.75439  

```

#check plots for marginal effects - coral top taxa
```{r}

#RelAbund_Oceanospirillales_Neptuniibacter-----
coral.nept.beta <- glmmTMB(RelAbund_Oceanospirillales_Neptuniibacter ~ algae.N15*Exposure+ (1|site.name), data=beta_trans_coral_microbes, family = beta_family(), na.action = na.omit)
Anova(coral.nept.beta)


test(emtrends(coral.nept.beta, ~ Exposure, var = "algae.N15", adjust = "fdr"))
# Exposure  algae.N15.trend     SE df t.ratio p.value
# Exposed          0.270487 0.1259 Inf   2.149  0.0633
# Protected       -0.000377 0.0681 Inf  -0.006  0.9956

test(emtrends(coral.nept.beta, pairwise~Exposure, var = "algae.N15", adjust = "fdr"))
#Exposed - Protected    0.271 0.143 Inf   1.897  0.0578

###RelAbund_Endozoicomonas-----
coral.end.beta <- glmmTMB(RelAbund_Endozoicomonas ~ algae.N15*Exposure+ (1|site.name), data=beta_trans_coral_microbes, family = beta_family(), na.action = na.omit)
Anova(coral.end.beta)

test(emtrends(coral.end.beta, ~ Exposure, var = "algae.N15", adjust = "fdr"))
# Exposure  algae.N15.trend     SE df t.ratio p.value
# Exposed            -0.242 0.2453 Inf  -0.985  0.3248
# Protected          -0.159 0.0995 Inf  -1.598  0.2200

#nothing significant, so not very relevant....


```




#Water
#Top taxa include: Synnechococcus, Litoricola, Prochlorococcus, Uncultured Alteromonadaceae & SAR86

```{r}
hist(water.microbes.seabirds$RelAbund_Synechococcus)
qqPlot(water.microbes.seabirds$RelAbund_Synechococcus) #yuck


#use a beta distribution - can't use poisson (not count data), negative binomial looked terrible

###If they are all betas, can we transform & then loop it 
beta_trans_water_microbes <- dplyr::mutate(water.microbes.seabirds, RelAbund_Synechococcus = (RelAbund_Synechococcus*(n()-1) + 0.5)/n())
beta_trans_water_microbes <- dplyr::mutate(beta_trans_water_microbes, RelAbund_Litoricola = (RelAbund_Litoricola*(n()-1) + 0.5)/n())
beta_trans_water_microbes <- dplyr::mutate(beta_trans_water_microbes, RelAbund_Prochlorococcus = (RelAbund_Prochlorococcus*(n()-1) + 0.5)/n())
beta_trans_water_microbes <- dplyr::mutate(beta_trans_water_microbes, RelAbund_SAR86_Clade = (RelAbund_SAR86_Clade*(n()-1) + 0.5)/n())
beta_trans_water_microbes <- dplyr::mutate(beta_trans_water_microbes, RelAbund_Uncultured_Alteromonadaceaeae = (RelAbund_Uncultured_Alteromonadaceaeae*(n()-1) + 0.5)/n())
beta_trans_water_microbes <- dplyr::mutate(beta_trans_water_microbes, RelAbund_SAR116_Clade = (RelAbund_SAR116_Clade*(n()-1) + 0.5)/n())
beta_trans_water_microbes <- dplyr::mutate(beta_trans_water_microbes, RelAbund_SAR11_CladeIa = (RelAbund_SAR11_CladeIa*(n()-1) + 0.5)/n())
beta_trans_water_microbes <- dplyr::mutate(beta_trans_water_microbes, RelAbund_SAR11_CladeIb = (RelAbund_SAR11_CladeIb*(n()-1) + 0.5)/n())
beta_trans_water_microbes <- dplyr::mutate(beta_trans_water_microbes, RelAbund_Rhodospirillales_AEGEAN_169_marine_group = (RelAbund_Rhodospirillales_AEGEAN_169_marine_group*(n()-1) + 0.5)/n())

print(colnames(beta_trans_water_microbes))
columns <- c( "RelAbund_Synechococcus" , "RelAbund_Litoricola", "RelAbund_Prochlorococcus", "RelAbund_SAR86_Clade",
              "RelAbund_Uncultured_Alteromonadaceaeae", "RelAbund_SAR116_Clade", 
              "RelAbund_SAR11_CladeIa", "RelAbund_SAR11_CladeIb","RelAbund_Rhodospirillales_AEGEAN_169_marine_group")
#Loop
dat <- beta_trans_water_microbes
models <- list()
for (i in columns) {
  f <- formula(paste(i, "~ algae.N15*Exposure + (1|site.name)"))
  models[[i]] <- glmmTMB(f, data=dat, family = beta_family(), na.action = na.omit)
  print(Anova(models[[i]])) 

}

#Cool - there are some taxa that ahve a significant relationship with algae N15 (no interactions), including: 
# Synechococcus: ChiSq = 24.4740, p = 7.532e -07
# SAR 86: Chisq = 4.20, p = 0.04042
# SAR116: ChiSq = 5.45, p = 0.01947
#
```

#Plot significant ones - DOES THE DATA FOR THESE NEED TO BE BETA TRANS FILE?!!!
#Synechococcus
```{r}

wat.syn.beta <- glmmTMB(RelAbund_Synechococcus ~ algae.N15*Exposure+ (1|site.name), data=water.microbes.seabirds, family = beta_family(), na.action = na.omit)

plot(resid(wat.syn.beta))

Anova(wat.syn.beta)
#Response: RelAbund_Synechococcus
#                     Chisq Df Pr(>Chisq)    
#algae.N15          24.1061  1  9.117e-07 ***
#Exposure            0.9128  1     0.3394    
#algae.N15:Exposure  0.1004  1     0.7514    


test(emtrends(wat.syn.beta, ~ Exposure, var = "algae.N15", adjust = "fdr"))
# Exposure  algae.N15.trend     SE df t.ratio p.value
# Exposed            -0.106 0.0726 59  -1.461  0.1494
# Protected          -0.131 0.0278 59  -4.702  <.0001

test(emtrends(wat.syn.beta, pairwise~Exposure, var = "algae.N15", adjust = "fdr"))
#contrast            estimate     SE df t.ratio p.value
# Exposed - Protected   0.0246 0.0777 59   0.317  0.7525

#No significant interaction with exposure 

#Plot

syn_plot_dat_no_exp <- emmip(wat.syn.beta,  ~ algae.N15, at = list(algae.N15 = seq(2.73, 10.66, .1)), CIs = TRUE, plotit=FALSE, type = "response")

ggplot(water.microbes.seabirds, aes(x = algae.N15, y = RelAbund_Synechococcus))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(fill = Exposure, colour = Exposure, shape = Exposure))+
  geom_line(data = syn_plot_dat_no_exp, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = syn_plot_dat_no_exp, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
  ylab("Relative Abundance of Synechococcus (Water Microbiome) \n") +
  xlab(expression(italic(delta)^15*N))+
   scale_fill_manual(values = my_colors, labels = c('windward', 'leeward'))+
  scale_color_manual(values = my_colors, labels = c('windward', 'leeward')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = c(0.85, 0.75)) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))


#You can see that it's by location here too

my_colors_3 <- RColorBrewer::brewer.pal(3, "Dark2")[c(1:3)]
p.wat.syn <- ggplot(water.microbes.seabirds, aes(x = algae.N15, y = RelAbund_Synechococcus))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(fill = motu, colour = motu, shape = Exposure))+
  geom_line(data = syn_plot_dat_no_exp, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = syn_plot_dat_no_exp, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
  ylab(expression(paste("Relative Abundance of", italic("Synechococcus")))) +
  xlab(expression(italic(delta)^15*N))+
   scale_fill_manual(values = my_colors_3, labels = c('Aie', 'Reiono', 'Rimatuu'))+
  scale_color_manual(values = my_colors_3, labels = c('Aie', 'Reiono', 'Rimatuu')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = c(0.15, 0.68),
        legend.background = element_rect(fill = 'transparent')) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))

p.wat.syn
#ggsave("../output/seabird-microbes/clean_output/6_water_micro-synechococcus_motu_HE.jpg", plot = #last_plot(), width = 7, height = 5)


```


#Can we remove protected side of Aie?
```{r}
water.microbes.seabirds.noaiepro <- filter(water.microbes.seabirds, site.name != "Aie_Protected")

syn_trans_noaie <- dplyr::mutate(water.microbes.seabirds.noaiepro, RelAbund_Synechococcus = (RelAbund_Synechococcus*(n()-1) + 0.5)/n())
syn.beta.noaie <- glmmTMB(RelAbund_Synechococcus ~ algae.N15*Exposure + (1|site.name), family = beta_family(), data = syn_trans_noaie, na.action = na.omit)

Anova(syn.beta.noaie)
#Response: RelAbund_Synechococcus
#                    Chisq Df Pr(>Chisq)
#algae.N15          0.0800  1     0.7773
#Exposure           0.0745  1     0.7849
#algae.N15:Exposure 2.3486  1     0.1254

#Yep, no longer significant when removing aie protected
```

#SAR86

```{r}
wat.sar86.beta <- glmmTMB(RelAbund_SAR86_Clade ~ algae.N15*Exposure+ (1|site.name), data=water.microbes.seabirds, family = beta_family(), na.action = na.omit)

plot(resid(wat.sar86.beta))

Anova(wat.sar86.beta)
#Response: RelAbund_SAR86_Clade
#                    Chisq Df Pr(>Chisq)  
#algae.N15          3.9319  1    0.04738 *
#Exposure           0.1355  1    0.71278  
#algae.N15:Exposure 2.3965  1    0.12160  

test(emtrends(wat.sar86.beta, ~ Exposure, var = "algae.N15", adjust = "fdr"))
# Exposure  algae.N15.trend     SE df t.ratio p.value
# Exposed           -0.1261 0.0515 59  -2.449  0.0346
# Protected         -0.0241 0.0413 59  -0.583  0.5623
test(emtrends(wat.sar86.beta, pairwise~Exposure, var = "algae.N15", adjust = "fdr"))
#$contrasts
# contrast            estimate     SE df t.ratio p.value
# Exposed - Protected   -0.102 0.0659 59  -1.548  0.1270


#No significant interaction with exposure 

#Plot

sar86_plot_dat_no_exp <- emmip(wat.sar86.beta,  ~ algae.N15, at = list(algae.N15 = seq(2.73, 10.66, .1)), CIs = TRUE, plotit=FALSE, type = "response")

ggplot(water.microbes.seabirds, aes(x = algae.N15, y = RelAbund_SAR86_Clade))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(fill = Exposure, colour = Exposure, shape = Exposure))+
  geom_line(data = sar86_plot_dat_no_exp, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = sar86_plot_dat_no_exp, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
  ylab("Relative Abundance of SAR86 (Water Microbiome) \n") +
  xlab(expression(italic(delta)^15*N))+
   scale_fill_manual(values = my_colors, labels = c('windward', 'leeward'))+
  scale_color_manual(values = my_colors, labels = c('windward', 'leeward')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = c(0.85, 0.75)) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))


#ggsave("../output/seabird-microbes/clean_output/7_water_micro-sar86_motu_HE.jpg", plot = last_plot(), width = 7, height = 5)


#looks better than synechococcus! 

#Quick look via motu

my_colors_3 <- RColorBrewer::brewer.pal(3, "Dark2")[c(1:3)]
p.wat.sar86 <- ggplot(water.microbes.seabirds, aes(x = algae.N15, y = RelAbund_SAR86_Clade))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(fill = motu, colour = motu, shape = Exposure))+
  geom_line(data = sar86_plot_dat_no_exp, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = sar86_plot_dat_no_exp, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
  ylab("Relative Abundance of SAR86") +
  xlab(expression(italic(delta)^15*N))+
   scale_fill_manual(values = my_colors_3, labels = c('Aie', 'Reiono', 'Rimatuu'))+
  scale_color_manual(values = my_colors_3, labels = c('Aie', 'Reiono', 'Rimatuu')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = "None") +
  #theme(legend.position = c(0.9, 0.7),
  #      legend.background = element_rect(fill = "transparent")) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))
p.wat.sar86
#ggsave("../output/seabird-microbes/clean_output/7b_water_micro-sar86_motu_HE.jpg", plot = last_plot(), width = 7, height = 5)

#Aie is all alone but the trend seems to hold - check without aie?

water.microbes.seabirds.noaie <- filter(water.microbes.seabirds, motu != "Aie")

sar86_trans_noaie <- dplyr::mutate(water.microbes.seabirds.noaie, RelAbund_SAR86_Clade = (RelAbund_SAR86_Clade*(n()-1) + 0.5)/n())
sar86.beta.noaie <- glmmTMB(RelAbund_SAR86_Clade ~ algae.N15*Exposure + (1|site.name), family = beta_family(), data = sar86_trans_noaie, na.action = na.omit)

Anova(sar86.beta.noaie)
#Response: RelAbund_SAR86_Clade
#                   Chisq Df Pr(>Chisq)  
#algae.N15          4.200  1    0.04042 *
#Exposure           0.157  1    0.69194  
#algae.N15:Exposure 2.664  1    0.10264  

#Yes! Still holds 


```


#SAR116

```{r}
#RelAbund_SAR116_Clade

wat.sar116.beta <- glmmTMB(RelAbund_SAR116_Clade ~ algae.N15*Exposure+ (1|site.name), data=water.microbes.seabirds, family = beta_family(), na.action = na.omit)

plot(resid(wat.sar116.beta)) #resids look great!

Anova(wat.sar116.beta)
#Response: RelAbund_SAR116_Clade
#                    Chisq Df Pr(>Chisq)  
#algae.N15          5.4757  1    0.01928 *
#Exposure           0.4973  1    0.48069  
#algae.N15:Exposure 0.5444  1    0.46060 

test(emtrends(wat.sar116.beta, ~ Exposure, var = "algae.N15", adjust = "fdr"))
#  Exposure  algae.N15.trend     SE df t.ratio p.value
# Exposed           -0.0794 0.0437 59  -1.818  0.1172
# Protected         -0.0414 0.0260 59  -1.590  0.1172
test(emtrends(wat.sar116.beta, pairwise~Exposure, var = "algae.N15", adjust = "fdr"))
#$contrasts
# contrast            estimate     SE df t.ratio p.value
# Exposed - Protected   -0.038 0.0515 59  -0.738  0.4635


#No significant interaction with exposure 

#Plot

sar116_plot_dat_no_exp <- emmip(wat.sar116.beta,  ~ algae.N15, at = list(algae.N15 = seq(2.73, 10.66, .1)), CIs = TRUE, plotit=FALSE, type = "response")

ggplot(water.microbes.seabirds, aes(x = algae.N15, y = RelAbund_SAR116_Clade))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(fill = Exposure, colour = Exposure, shape = Exposure))+
  geom_line(data = sar116_plot_dat_no_exp, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = sar116_plot_dat_no_exp, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
  ylab("Relative Abundance of SAR116 (Water Microbiome) \n") +
  xlab(expression(italic(delta)^15*N))+
   scale_fill_manual(values = my_colors, labels = c('windward', 'leeward'))+
  scale_color_manual(values = my_colors, labels = c('windward', 'leeward')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = c(0.85, 0.75)) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))

#ggsave("../output/seabird-microbes/clean_output/8_water_micro-sar116_HE.jpg", plot = last_plot(), width = 7, height = 5)


#looks better than synechococcus! 

#Quick look via motu

my_colors_3 <- RColorBrewer::brewer.pal(3, "Dark2")[c(1:3)]
p.wat.sar116 <- ggplot(water.microbes.seabirds, aes(x = algae.N15, y = RelAbund_SAR116_Clade))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(fill = motu, colour = motu, shape = Exposure))+
  geom_line(data = sar116_plot_dat_no_exp, aes(x = algae.N15, y = yvar))+
   geom_ribbon(data = sar116_plot_dat_no_exp, aes(x = algae.N15, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
  ylab("Relative Abundance of SAR116") +
  xlab(expression(italic(delta)^15*N))+
   scale_fill_manual(values = my_colors_3, labels = c('Aie', 'Reiono', 'Rimatuu'))+
  scale_color_manual(values = my_colors_3, labels = c('Aie', 'Reiono', 'Rimatuu')) +
    scale_shape_manual(values = c(24,  21), labels = c('windward', 'leeward'))+
  theme_classic() +
  theme(legend.position = "None") +
  #theme(legend.position = c(0.9, 0.7),
   #     legend.background = element_rect(fill = 'transparent')) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))
p.wat.sar116

#minimal visual location effect


```
#Let's combine the plots necessary for supplement
```{r}
#1) p.wat.sh

#2) p.wat.syn

#3) p.wat.sar86

#4) p.wat.sar116

##Only need Synechococcus with the legend I think?? Try again

library(cowplot)

microbe_supp_plots<-cowplot::plot_grid(p.wat.sh, p.wat.syn, p.wat.sar86, p.wat.sar116, labels = "auto", label_fontface = "plain")
microbe_supp_plots

ggsave("../output/seabird-microbes/water_microbe_supp_plots.jpg", plot = microbe_supp_plots, width = 10, height = 8)
ggsave("../output/seabird-microbes/water_microbe_supp_plots.pdf", plot = microbe_supp_plots, width = 10, height = 8)

```


##Woohoo! Done with the main stuff

# How about top taxa by restoration status (motu) just bc 

#Coral
```{r}

beta_trans_coral_microbes$reststat <- beta_trans_coral_microbes$motu

beta_trans_coral_microbes$reststat[beta_trans_coral_microbes$reststat == "aie"] <- "reference"
beta_trans_coral_microbes$reststat[beta_trans_coral_microbes$reststat == "reiono"] <- "recovering"
beta_trans_coral_microbes$reststat[beta_trans_coral_microbes$reststat == "rimatuu"] <- "unrestored"


print(colnames(beta_trans_coral_microbes))
columns <- c( "RelAbund_Cellvibrionales_Aestuariicella" , "RelAbund_Alteromonadales_Agaribacter",
              "RelAbund_Cytophagales_Candidatus_Amoebophilus", "RelAbund_Endozoicomonas","RelAbund_Alteromonadales_Glaciecola",
              "RelAbund_Oceanospirillales_Neptuniibacter","RelAbund_Cellvibrionales_Porticoccus",
              "RelAbund_Woesearchaeales_SCGC_AAA286E23","RelAbund_Litoricola","RelAbund_Uncultured_Alteromonadaceaeae")
#Loop
dat <- beta_trans_coral_microbes
models <- list()
for (i in columns) {
  f <- formula(paste(i, "~ reststat*Distance_to_shore + reststat*Exposure + (1|site.name)"))
  models[[i]] <- glmmTMB(f, data=dat, family = beta_family(), na.action = na.omit)
  print(Anova(models[[i]])) 

}


#Way more significant by motu

#Agaribacter (sig by reststat, exposure and int btw reststat and exp)
#Ca Amoebophilus (sig by distance to shore, and int btw reststat and distance to shore)
#Endozoicomonas (sig by reststat and int btw restat and exposure)
#Alteromonadales_Glaciecola (sig by reststat, exposure and int with exposure)
#Neptuniibacter (sig by reststat, exposure and int with exposure)
#Litoricola  (sig only by reststat)
#Alteromonadaceae (sig by reststat, exposure and int with exposure)
```

#Water
```{r}

beta_trans_water_microbes$reststat <- beta_trans_water_microbes$motu

beta_trans_water_microbes$reststat[beta_trans_water_microbes$reststat == "aie"] <- "reference"
beta_trans_water_microbes$reststat[beta_trans_water_microbes$reststat == "reiono"] <- "recovering"
beta_trans_water_microbes$reststat[beta_trans_water_microbes$reststat == "rimatuu"] <- "unrestored"

print(colnames(beta_trans_water_microbes))
columns <- c( "RelAbund_Synechococcus" , "RelAbund_Litoricola", "RelAbund_Prochlorococcus", "RelAbund_SAR86_Clade",
              "RelAbund_Uncultured_Alteromonadaceaeae", "RelAbund_SAR116_Clade", 
              "RelAbund_SAR11_CladeIa", "RelAbund_SAR11_CladeIb","RelAbund_Rhodospirillales_AEGEAN_169_marine_group")
#Loop
dat <- beta_trans_water_microbes
models <- list()
for (i in columns) {
  f <- formula(paste(i, "~ reststat*Distance_to_shore + reststat*Exposure + (1|site.name)"))
  models[[i]] <- glmmTMB(f, data=dat, family = beta_family(), na.action = na.omit)
  print(Anova(models[[i]])) 

}


#Almost all
#Synechococcus (all sig )
#Litoricola (sig by reststat, exp +sig int with exp)
#Prochlorococcus (sig by reststat, exp +sig int with exp)
#SAR86 (sig by reststat, exp +sig int with exp)
#Alteromonadaceae (sig by reststat, exposure only)
#SAR116 (not with restat, but all the rest)
#SAR11 Clade 1a (not with restat, but exposure and sig int)
#SAR11 Clade 1b (sig by reststat, exp,+ sig int with exp)
#Rhodospirillales marine group (sig by reststat only)

```


#Can we plot the main coral taxa by restoration status and exposure?
#1. Endo, 2. Litoricola 3. Alteromonadacaea, 4. Neptunibacter
```{r}
beta_trans_coral_microbes <- beta_trans_coral_microbes %>% mutate(reststat = fct_relevel(reststat, "reference", "recovering", "unrestored"))
p.cor.endo <- ggplot(beta_trans_coral_microbes, aes(y = RelAbund_Endozoicomonas, x = reststat, fill = Exposure))+
  geom_boxplot( alpha = 0.6) +
  ylab(expression(paste("Relative Abundance of ", italic("Endozoicomonas")))) +
  xlab("")+
  scale_fill_manual(values = c("Protected" = "#D76127", "Exposed" = "#1C9E77")) +
  scale_colour_manual(values = c("Protected" = "#D76127", "Exposed" = "#1C9E77")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
        legend.position = "none")
p.cor.endo

```

```{r}
mod.nept <- glmmTMB(RelAbund_Oceanospirillales_Neptuniibacter ~ reststat*Distance_to_shore + Exposure + (1|site.name), data=beta_trans_coral_microbes, family = beta_family(), na.action = na.omit)
Anova(mod.nept)
emmeans(mod.nept,list(pairwise ~ reststat + Exposure), type = "response", adjust = "fdr" )

beta_trans_coral_microbes <- beta_trans_coral_microbes %>% mutate(reststat = fct_relevel(reststat, "reference", "recovering", "unrestored"))

p.cor.nept <- ggplot(beta_trans_coral_microbes, aes(y = RelAbund_Oceanospirillales_Neptuniibacter, x = reststat, fill = Exposure))+
  geom_boxplot( alpha = 0.6) +
  ylab(expression(paste("Relative Abundance of ", italic("Neptunibacter")))) +
  xlab("")+
  scale_fill_manual(values = c("Protected" = "#D76127", "Exposed" = "#1C9E77")) +
  scale_colour_manual(values = c("Protected" = "#D76127", "Exposed" = "#1C9E77")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
        legend.position = c(.85,.85))
p.cor.nept
```

```{r}
p.cor.lito <- ggplot(beta_trans_coral_microbes, aes(y = RelAbund_Litoricola, x = reststat, fill = Exposure))+
  geom_boxplot( alpha = 0.6) +
  ylab(expression(paste("Relative Abundance of ", italic("Litoricola")))) +
  xlab("") +
  scale_fill_manual(values = c("Protected" = "#D76127", "Exposed" = "#1C9E77")) +
  scale_colour_manual(values = c("Protected" = "#D76127", "Exposed" = "#1C9E77")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
        legend.position ="none")
p.cor.lito
```


```{r}

p.cor.alter <- ggplot(beta_trans_coral_microbes, aes(y = RelAbund_Uncultured_Alteromonadaceaeae, x = reststat, fill = Exposure))+
  geom_boxplot( alpha = 0.6) +
  ylab("Relative Abundance of \nUncultured Alteromonadaceae") +
  xlab("")+
  scale_fill_manual(values = c("Protected" = "#D76127", "Exposed" = "#1C9E77")) +
  scale_colour_manual(values = c("Protected" = "#D76127", "Exposed" = "#1C9E77")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
        legend.position = "none")
p.cor.alter

```

```{r}
#Final plot for supps 

#1)Endo: p.cor.endo
#1) Litoricola: p.cor.lito
#3) Altero: p.cor.alter
#4) Neptu: p.cor.nept (this has the legend)


cor_taxa_plots <- cowplot::plot_grid(p.cor.endo, p.cor.lito, p.cor.alter, p.cor.nept, labels = "auto", label_fontface = "plain")
cor_taxa_plots

ggsave("../output/seabird-microbes/coral_microbe_supp_taxaplots.jpg", plot = cor_taxa_plots, width = 10, height = 8)
ggsave("../output/seabird-microbes/coral_microbe_supp_taxaplots.pdf", plot = cor_taxa_plots, width = 10, height = 8)
```

