---
title: "algaen15_vs_fish"
author: "CEB"
date: '2023-10-03'
output: html_document
---

#load packages
```{r}
library(tidyverse)

library(lme4)
library(car)
library(jtools)

library(emmeans)
library(corrplot)
library(vegan)

library(cowplot)



```



#load data
```{r}
seabirds <- read.csv("../output/n15_seabirds_combined_no_iti.csv", strip.white = T, header = T)
load("../../fish_benthic_surveys/output/data/fish_community_data.Rdata")

fish_bio_dat<-nmds_fish_diet_log_bio_site_scores

```



#merge data
```{r}
fish_bio_dat

#make combined site name column in fish data
fish_bio_dat2<-
  fish_bio_dat%>%
  mutate(protection = if_else(wind.exposure == "leeward", "Protected", "Exposed"))%>%
  relocate(protection, .before = wind.exposure)%>%
    mutate(motu = str_to_title(motu))%>%
  unite("site.name", c(motu, protection), sep = "_", remove = FALSE)


fish_bio_dat2

fish.bio.seabirds<-left_join(fish_bio_dat2,
                           dplyr::select(seabirds, c("site.name", "breeding_biomass_kgha_side")), 
                                   by = "site.name")%>%
  mutate(site.name = as.factor(site.name))
fish.bio.seabirds

```


##need to also add in transect metadata
```{r}

#load data-----
tet_trans_meta<-read.csv("../../metadata/fish_benthic_focal_transect_metadata.csv", stringsAsFactors = TRUE)
str(tet_trans_meta)

#make site name to do easy merge:----
tet_trans_meta2<-
  tet_trans_meta%>%
  rename_all(str_to_lower)%>%
  mutate(protection = if_else(exposure == "Leeward", "Protected", "Exposed"))%>%
  relocate(protection, .before = exposure)%>%
    mutate(motu = str_to_title(motu))%>%
  unite("site.name", c(motu, protection), sep = "_", remove = FALSE)

tet_trans_meta2

fish.bio.seabirds.trans<-right_join(dplyr::select(tet_trans_meta2, c("site.name", "transect", "start_distance_to_shore_m",
                                                             "end_distance_to_shore_m", "depth_min_m", "depth_max_m", "structural_complexity_0to5",
                                                             "transect.location")),
                                          fish.bio.seabirds,
                                          by = c("site.name", "transect"))%>%
  relocate(breeding_biomass_kgha_side, .after = rat.eradication.status) %>%
  mutate(transect.in.out = case_when(grepl(pattern = "off", x = transect.location) ~ "offshore",
                                     grepl(pattern = "in", x = transect.location) ~ "inshore"))%>%
  mutate(transect.in.out = as.factor(transect.in.out))%>%
  relocate(transect.in.out, .after = transect.location)
  
fish.bio.seabirds.trans


###add transect data to fish density----
#density by feeding group/diet:
fish_fg_dens_dat<-
  nmds_fish_diet_log_site_scores%>%
 dplyr::select(c(motu, site.name, wind.exposure, transect, Herb, InvMob, Omnivr, Plktiv, FisCep, InvSes))%>%
  rename_with(~paste0(.,"_density"), Herb:InvSes)%>%
   mutate(protection = if_else(wind.exposure == "leeward", "Protected", "Exposed"))%>%
  relocate(protection, .before = wind.exposure)%>%
  mutate(motu = str_to_title(motu))%>%
  unite("site.name", c(motu, protection), sep = "_", remove = FALSE)
fish_fg_dens_dat

fish.dens.seabirds<-left_join(fish_fg_dens_dat,
                           dplyr::select(seabirds, c("site.name", "breeding_biomass_kgha_side")), 
                                   by = "site.name")%>%
  mutate(site.name = as.factor(site.name))
fish.dens.seabirds

#and combine with transect metadata
fish.dens.seabirds.trans<-right_join(dplyr::select(tet_trans_meta2, c("site.name", "transect", "start_distance_to_shore_m",
                                                             "end_distance_to_shore_m", "depth_min_m", "depth_max_m", "structural_complexity_0to5",
                                                             "transect.location")),
                                          fish.dens.seabirds,
                                          by = c("site.name", "transect"))%>%
  relocate(breeding_biomass_kgha_side, .after = wind.exposure) %>%
    mutate(transect.in.out = case_when(grepl(pattern = "off", x = transect.location) ~ "offshore",
                                     grepl(pattern = "in", x = transect.location) ~ "inshore"))%>%
  mutate(transect.in.out = as.factor(transect.in.out))%>%
  relocate(transect.in.out, .after = transect.location)

fish.dens.seabirds.trans

```



##combine relevant data - aggregate metrics
```{r}
tet_fish_dens_div_comm_dat
tet_fish_div_comm_tl_dat
nmds_fish_diet_log_site_scores
nmds_fish_diet_log_bio_site_scores

#total density, and diversity stats based on density:
fish_dens_div_dat<-
  tet_fish_dens_div_comm_dat%>%
 dplyr::select(c(motu, site.name, wind.exposure, transect, shannon, evenness, sum_dens, PD, SR))%>%
  mutate(protection = if_else(wind.exposure == "leeward", "Protected", "Exposed"))%>%
  relocate(protection, .before = wind.exposure)%>%
  mutate(motu = str_to_title(motu))%>%
  unite("site.name", c(motu, protection), sep = "_", remove = FALSE)


#relative biomass by trophic level:
fish_tl_bio_dat<-
  tet_fish_div_comm_tl_dat%>%
 dplyr::select(c(motu, site.name, wind.exposure, transect, rel_bio_TL1, rel_bio_TL2, rel_bio_TL3, rel_bio_TL4, rel_bio_TL5))%>%
   mutate(protection = if_else(wind.exposure == "leeward", "Protected", "Exposed"))%>%
  relocate(protection, .before = wind.exposure)%>%
  mutate(motu = str_to_title(motu))%>%
  unite("site.name", c(motu, protection), sep = "_", remove = FALSE)



#biomass by feeding group/diet, and keep in metadata from above:
fish_fg_bio_dat<-
  fish.bio.seabirds.trans%>%
  dplyr::select(c(motu, site.name,wind.exposure, transect, start_distance_to_shore_m, end_distance_to_shore_m, 
           depth_min_m, depth_max_m, structural_complexity_0to5, transect.in.out, breeding_biomass_kgha_side, 
           Herb, InvMob, Omnivr, Plktiv, FisCep, InvSes))%>%
  rename_with(~paste0(.,"_biomass"), Herb:InvSes)%>%
    rowwise%>%
 dplyr::mutate(sum_fish_biomass = sum(c_across(Herb_biomass:InvSes_biomass)))%>%
  ungroup

fish_fg_bio_dat


#now combine----
fish_comb_dat_1<- full_join(fish_dens_div_dat, fish_tl_bio_dat, by = c("motu", "site.name", "wind.exposure", "protection", "transect"))
fish_comb_dat_1

fish_comb_dat_2<- full_join(fish_comb_dat_1, fish_fg_dens_dat, by = c("motu", "site.name", "wind.exposure", "protection", "transect"))
fish_comb_dat_2


fish_comb_dat<- full_join(fish_fg_bio_dat, dplyr::select(fish_comb_dat_2,-protection), by = c("motu", "site.name", "wind.exposure",  "transect"))
fish_comb_dat

```



##add seabird levels and algae n15----
```{r}
#to seabird biomass----
#seabird levels----
fish_comb_dat_levels<-
  fish_comb_dat%>%
  mutate(seabird_level = case_when(breeding_biomass_kgha_side<10 ~"low",
                                   breeding_biomass_kgha_side>10&breeding_biomass_kgha_side <200 ~"mid",
                                   breeding_biomass_kgha_side>200 ~"high"))%>%
  mutate(seabird_level = as.factor(seabird_level))%>%
  mutate(seabird_level = fct_relevel(seabird_level, "low", "mid", "high"))%>%
  relocate(seabird_level, .before = breeding_biomass_kgha_side) 

fish_comb_dat_levels


#algae n15----
algae_n15<-read.csv("../output/n15_seabirds_combined_no_iti.csv")
algae_n15


fish_comb_dat_levels_algae<-left_join(fish_comb_dat_levels, 
                                            dplyr::select(algae_n15, c("site.name", "N.15_at_10m",  "N.15_at_20m", "N.15_at_30m", "N.15_at_40m")),
                                            by = "site.name")

fish_comb_dat_levels_algae


#to seabird density-----
fish.dens.seabirds.trans

fish_fg_dens_dat_levels<-
  fish.dens.seabirds.trans%>%
  mutate(seabird_level = case_when(breeding_biomass_kgha_side<10 ~"low",
                                   breeding_biomass_kgha_side>10&breeding_biomass_kgha_side <200 ~"mid",
                                   breeding_biomass_kgha_side>200 ~"high"))%>%
  mutate(seabird_level = as.factor(seabird_level))%>%
  mutate(seabird_level = fct_relevel(seabird_level, "low", "mid", "high"))%>%
  relocate(seabird_level, .before = breeding_biomass_kgha_side) 

fish_fg_dens_dat_levels




fish_fg_dens_dat_levels_algae<-left_join(fish_fg_dens_dat_levels, 
                                            dplyr::select(algae_n15, c("site.name", "N.15_at_10m",  "N.15_at_20m", "N.15_at_30m", "N.15_at_40m")),
                                            by = "site.name")

fish_fg_dens_dat_levels_algae

```


##-----------------do NMDS with algae n15 as overlay, seabird levels - FEEDING GROUP, DENSITY, No transformations------

#run nmds
```{r}
#create species matrix
fish.dens.seabirds.trans_sp<-
  fish_fg_dens_dat_levels_algae%>%
  ungroup()%>%
  dplyr::select(Herb_density:InvSes_density)

#run NMDS (data frame created above)
nmds_fish_dens_autoF<-metaMDS(fish.dens.seabirds.trans_sp, distance = "bray", trymax=200, k=2, autotransform = FALSE)
nmds_fish_dens_autoF
#2 axis stress = 0.1287778

plot(nmds_fish_dens_autoF)
scores(nmds_fish_dens_autoF, display="species")

#look at ordfit - offshore algae n15
ord.fit.algae.autoF<-envfit(nmds_fish_dens_autoF~N.15_at_30m+protection + structural_complexity_0to5, data = fish_fg_dens_dat_levels_algae, na.rm=TRUE)
ord.fit.algae.autoF #Algae n15 is not significant

scores(nmds_fish_dens_autoF, display="species")


#rotate by algae n15 so can more easily interpret----
nmds_fish_dens_autoF.rotate<-MDSrotate(nmds_fish_dens_autoF, fish_fg_dens_dat_levels_algae$N.15_at_30m)
nmds_fish_dens_autoF.rotate

scores(nmds_fish_dens_autoF.rotate, display="species")
cor(fish.dens.seabirds.trans_sp,
      nmds_fish_dens_autoF.rotate$points,
      use = "complete.obs",
      method = "pearson")
#looks like positive correlations with axis 1 (n15) = piscivores, herbivores, mobile invertebrate feeders. 
#negative correlations with axis 1 (n15) = sessile invertebrate feeders, planktivores
#neutral = omnivores

ord.fit.algae.autoF.rotate<-envfit(nmds_fish_dens_autoF.rotate~N.15_at_30m+protection + structural_complexity_0to5, data = fish_fg_dens_dat_levels_algae, na.rm=TRUE)
ord.fit.algae.autoF.rotate #Algae n15 is not significant****
plot(nmds_fish_dens_autoF.rotate)
plot(ord.fit.algae.autoF.rotate)


##extract site/transect scores (rotated)----
fish_spp.sc.rotate.autoF <- as.data.frame(scores(nmds_fish_dens_autoF.rotate, "species")) %>% #Using the scores function from vegan to extract the species scores and convert
   rownames_to_column(var="Species") %>% # create a column of species, from the rownames of species.scores
  mutate(Species = str_remove(Species, '_density'))%>%
  mutate(species2 = c("herbivore", "mobile invertebrate feeder", "omnivore", "planktivore", "piscivore", "sessile invertebrate feeder"))
fish_spp.sc.rotate.autoF

fish_site.sc.rotate.autoF <- scores(nmds_fish_dens_autoF.rotate, display = "sites", shrink = FALSE) 
fish_site.sc.rotate.autoF

#merge site.sc with site and transect
nmds_fish_site_scores_rotate.autoF<-
  bind_cols(fish_fg_dens_dat_levels_algae$site.name, fish_fg_dens_dat_levels_algae$transect,
                    as_tibble(fish_site.sc.rotate.autoF))%>%
  dplyr::rename('site.name' = '...1', 'transect' = '...2')
nmds_fish_site_scores_rotate.autoF

#combine with other metadata
nmds_fish_site_scores_rotate.autoF.w.mnmds<-
 left_join(nmds_fish_site_scores_rotate.autoF,
           fish_fg_dens_dat_levels_algae, 
             by = c("site.name", "transect")) 
nmds_fish_site_scores_rotate.autoF.w.mnmds


#NMDS plot----

##rotated plot-----

##get arrows: - UPDATED, NEED TO MULTIPLY BY * ordiArrowMul(ord.fit.fish.rotate.autoF))
sb.scrs.fish.rotate.autoF   <- as.data.frame(scores(ord.fit.algae.autoF.rotate  , display = "vectors")* ordiArrowMul(ord.fit.algae.autoF.rotate))

sb.scrs.fish.rotate.autoF   <- cbind(sb.scrs.fish.rotate.autoF  , variable = rownames(sb.scrs.fish.rotate.autoF  ))
sb.scrs.fish.rotate.autoF  <-
  sb.scrs.fish.rotate.autoF  %>%
  mutate(variable2 = c("algae n15", "structural complexity"))


fish_dens_nmds_plot_rotate.autoF.newcolors<-
ggplot() + 
  geom_point(data=nmds_fish_site_scores_rotate.autoF.w.mnmds ,aes(x=NMDS1,y=NMDS2,colour=N.15_at_30m, fill = N.15_at_30m), stat="identity", size=5, alpha = .9) +
scale_fill_distiller(palette = "YlGnBu", direction = -1)+
    scale_colour_distiller(palette = "YlGnBu", direction = -1)+
  #scale_fill_viridis_c(option = "inferno", direction = -1)+
  #  scale_colour_viridis_c(option = "inferno", direction = -1)+
#coord_fixed() + ## need aspect ratio of 1!
  geom_text(data=fish_spp.sc.rotate.autoF ,aes(x=NMDS1,y=NMDS2 ,label=species2), alpha = .5, hjust = "inward") +  # add the species labels - 
  geom_segment(data = sb.scrs.fish.rotate.autoF ,
               aes(x = 0, xend = NMDS1, y = 0, yend = NMDS2),
               arrow = arrow(length = unit(0.25, "cm")), colour = "black") +
    geom_text(data = sb.scrs.fish.rotate.autoF, aes(x = NMDS1, y = NMDS2, label = variable2), 
            size = 3, hjust = c(.75,.4), vjust = -1)+
  labs(colour = expression(algae~delta^15~N), fill = expression(algae~delta^15~N))+
  theme_bw() + 
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.9,.78))
        #legend.title = element_blank()) #remove legend title
        #legend.box.background = element_rect(colour = "black", fill='white', linetype='solid', size=1), 
       # legend.justification=c(1,.9), legend.position=c(1,.9))  #  fix legend

fish_dens_nmds_plot_rotate.autoF.newcolors 

#save plot
ggsave(fish_dens_nmds_plot_rotate.autoF.newcolors, file = "../output/seabird-fish/fish_nmds_plot_rotate_new_colours_notrans.jpg",
    width = 7, height = 5)



```


#PERMANOVA
```{r}

##permanova - NOT LOG DENSITY----
#Can't use blocks because we don't have blocks in our data (treatments are not distributed across sites)... And PERMANOVA does not accept random effects.

fish_dens_algaen15_ad_notlog<-adonis2(fish.dens.seabirds.trans_sp ~ N.15_at_30m  + wind.exposure + structural_complexity_0to5, data = fish_fg_dens_dat_levels_algae)
fish_dens_algaen15_ad_notlog
#                           Df SumOfSqs      R2      F Pr(>F)   
#N.15_at_30m                 1  0.05392 0.02866 0.6411  0.649
#wind.exposure               1  0.04253 0.02261 0.5057  0.749
#structural_complexity_0to5  1  0.10263 0.05455 1.2202  0.295
#Residual                   20  1.68216 0.89418              
#Total                      23  1.88123 1.00000   

##NOW NOTHING SIGNIFICANT***


fish_dens_algaen15_ad_notlog<-adonis2(fish.dens.seabirds.trans_sp ~ N.15_at_30m  * wind.exposure + N.15_at_30m  *structural_complexity_0to5, data = fish_fg_dens_dat_levels_algae)
fish_dens_algaen15_ad_notlog
#N.15_at_30m                             1  0.05392 0.02866 0.7306  0.576   
#wind.exposure                           1  0.04253 0.02261 0.5763  0.728   
#structural_complexity_0to5              1  0.10263 0.05455 1.3906  0.236   
#N.15_at_30m:wind.exposure               1  0.06259 0.03327 0.8482  0.515   
#N.15_at_30m:structural_complexity_0to5  1  0.29119 0.15479 3.9458  0.008 **
#Residual                               18  1.32837 0.70612                 
#Total                                  23  1.88123 1.00000     


#log-----
fish_dens_algaen15_ad_log<-adonis2(log(fish.dens.seabirds.trans_sp+1) ~ N.15_at_30m  + wind.exposure + structural_complexity_0to5, data = fish_fg_dens_dat_levels_algae)
fish_dens_algaen15_ad_log
#                           Df SumOfSqs      R2      F Pr(>F)   
#N.15_at_30m                 1  0.06332 0.19989 5.2540  0.008 **
#wind.exposure               1  0.00342 0.01079 0.2835  0.765   
#structural_complexity_0to5  1  0.00901 0.02843 0.7473  0.513   
#Residual                   20  0.24102 0.76089                 
#Total                      23  0.31676 1.00000              


fish_dens_algaen15_ad_log<-adonis2(log(fish.dens.seabirds.trans_sp+1) ~ N.15_at_30m *wind.exposure + N.15_at_30m *structural_complexity_0to5, data = fish_fg_dens_dat_levels_algae)
fish_dens_algaen15_ad_log
#N.15_at_30m                             1  0.06332 0.19989 6.3475  0.002 **
#wind.exposure                           1  0.00342 0.01079 0.3425  0.695   
#structural_complexity_0to5              1  0.00901 0.02843 0.9029  0.476   
#N.15_at_30m:wind.exposure               1  0.01583 0.04996 1.5867  0.240   
#N.15_at_30m:structural_complexity_0to5  1  0.04564 0.14410 4.5759  0.019 * 
#Residual                               18  0.17955 0.56683                 
#Total                                  23  0.31676 1.00000                 

cor(fish_fg_dens_dat_levels_algae$structural_complexity_0to5, fish_fg_dens_dat_levels_algae$N.15_at_30m)


library(AICcPermanova)
AllModels <- make_models(vars = c("N.15_at_30m", "wind.exposure", "structural_complexity_0to5", 
                                  "N.15_at_30m:wind.exposure", "N.15_at_30m:structural_complexity_0to5"))

fit_models(all_forms = AllModels,
           veg_data = log(fish.dens.seabirds.trans_sp+1),
           env_data = fish_fg_dens_dat_levels_algae)


```


##NMDS - log transformation-----
```{r}
#run nmds----
#run NMDS (data frame created above)
nmds_fish_dens_log<-metaMDS(fish.dens.seabirds.trans_sp, distance = "bray", trymax=200, k=2, autotransform = TRUE)
nmds_fish_dens_log
#2 axis stress = .1378

plot(nmds_fish_dens_log)
scores(nmds_fish_dens_log, display="species")

#look at ordfit - offshore algae n15
ord.fit.algae.log<-envfit(nmds_fish_dens_log~N.15_at_30m+protection + structural_complexity_0to5, data = fish_fg_dens_dat_levels_algae, na.rm=TRUE)
ord.fit.algae.log #Algae n15 is significant****

scores(nmds_fish_dens_log, display="species")


#rotate by algae n15 so can more easily interpret----
nmds_fish_dens_log.rotate<-MDSrotate(nmds_fish_dens_log, fish_fg_dens_dat_levels_algae$N.15_at_30m)
nmds_fish_dens_log.rotate

scores(nmds_fish_dens_log.rotate, display="species")
cor(fish.dens.seabirds.trans_sp,
      nmds_fish_dens_log.rotate$points,
      use = "complete.obs",
      method = "spearman")
#looks like positive correlations with axis 1 (n15) = piscivores, herbivores, mobile invertebrate feeders. 
#negative correlations with axis 1 (n15) = sessile invertebrate feeders, planktivores
#neutral = omnivores

ord.fit.algae.log.rotate<-envfit(nmds_fish_dens_log.rotate~N.15_at_30m+protection + structural_complexity_0to5, data = fish_fg_dens_dat_levels_algae, na.rm=TRUE)
ord.fit.algae.log.rotate #Algae n15 is significant****
plot(nmds_fish_dens_log.rotate)
plot(ord.fit.algae.log.rotate)


##extract site/transect scores (rotated)----
fish_spp.sc.rotate.log <- as.data.frame(scores(nmds_fish_dens_log.rotate, display = "species")) %>% #Using the scores function from vegan to extract the species scores and convert
   rownames_to_column(var="Species") %>% # create a column of species, from the rownames of species.scores
  mutate(Species = str_remove(Species, '_density'))%>%
  mutate(species2 = c("herbivore", "mobile invertebrate feeder", "omnivore", "planktivore", "piscivore", "sessile invertebrate feeder"))
fish_spp.sc.rotate.log

fish_site.sc.rotate.log <- scores(nmds_fish_dens_log.rotate, display = "sites", shrink = FALSE) 
fish_site.sc.rotate.log

#merge site.sc with site and transect
nmds_fish_site_scores_rotate.log<-
  bind_cols(fish_fg_dens_dat_levels_algae$site.name, fish_fg_dens_dat_levels_algae$transect,
                    as_tibble(fish_site.sc.rotate.log))%>%
  dplyr::rename('site.name' = '...1', 'transect' = '...2')
nmds_fish_site_scores_rotate.log

#combine with other metadata
nmds_fish_site_scores_rotate.log.w.mnmds<-
 left_join(nmds_fish_site_scores_rotate.log,
           fish_fg_dens_dat_levels_algae, 
             by = c("site.name", "transect")) 
nmds_fish_site_scores_rotate.log.w.mnmds


#NMDS plot----

##rotated plot-----

##get arrows: - UPDATED, NEED TO MULTIPLY BY * ordiArrowMul(ord.fit.fish.rotate.autoF))
sb.scrs.fish.rotate.log   <- as.data.frame(scores(ord.fit.algae.log.rotate  , display = "vectors")* ordiArrowMul(ord.fit.algae.log.rotate))

sb.scrs.fish.rotate.log   <- cbind(sb.scrs.fish.rotate.log  , variable = rownames(sb.scrs.fish.rotate.log  ))
sb.scrs.fish.rotate.log  <-
  sb.scrs.fish.rotate.log  %>%
  mutate(variable2 = c("algae n15", "structural complexity"))


fish_dens_nmds_plot_rotate.log.newcolors<-
ggplot() + 
  geom_point(data=nmds_fish_site_scores_rotate.log.w.mnmds ,aes(x=NMDS1,y=NMDS2,colour=N.15_at_30m, fill = N.15_at_30m), stat="identity", size=5, alpha = .9) +
scale_fill_distiller(palette = "YlGnBu", direction = -1)+
    scale_colour_distiller(palette = "YlGnBu", direction = -1)+
  #scale_fill_viridis_c(option = "inferno", direction = -1)+
  #  scale_colour_viridis_c(option = "inferno", direction = -1)+
#coord_fixed() + ## need aspect ratio of 1!
  geom_text(data=fish_spp.sc.rotate.log ,aes(x=NMDS1,y=NMDS2 ,label=species2), alpha = .5, hjust = "inward") +  # add the species labels - 
  geom_segment(data = sb.scrs.fish.rotate.log ,
               aes(x = 0, xend = NMDS1, y = 0, yend = NMDS2),
               arrow = arrow(length = unit(0.25, "cm")), colour = "black") +
    geom_text(data = sb.scrs.fish.rotate.log, aes(x = NMDS1, y = NMDS2, label = variable2), 
            size = 3, hjust = c(.75,.4), vjust = -1)+
  labs(colour = expression(algae~delta^15~N), fill = expression(algae~delta^15~N))+
  theme_bw() + 
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.9,.78))
        #legend.title = element_blank()) #remove legend title
        #legend.box.background = element_rect(colour = "black", fill='white', linetype='solid', size=1), 
       # legend.justification=c(1,.9), legend.position=c(1,.9))  #  fix legend

fish_dens_nmds_plot_rotate.log.newcolors 

#save plot
ggsave(fish_dens_nmds_plot_rotate.autoF.newcolors, file = "../output/seabird-fish/fish_nmds_plot_rotate_new_colours_log.jpg",
    width = 7, height = 5)



```



###--------------------LOOK AT FISH DIVERSITY METRICS (and overall density, biomass, etc.) VS. SEABIRD LEVELS AND ALGAE N15-----------

```{r}

#run lmms----
#total biomass----
fish_bio_full_mod_algae <-lmer(sum_fish_biomass~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae) #
summary(fish_bio_full_mod_algae)
plot(fish_bio_full_mod_algae)
qqnorm(resid(fish_bio_full_mod_algae))
qqline(resid(fish_bio_full_mod_algae))
#LOOKS BAD

#use log again: 
fish_bio_full_mod_algae_log <-lmer(log(sum_fish_biomass)~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae) #
summary(fish_bio_full_mod_algae_log)
plot(fish_bio_full_mod_algae_log)
qqnorm(resid(fish_bio_full_mod_algae_log))
qqline(resid(fish_bio_full_mod_algae_log))
#looks better - use this
#still some high correlations of fixed effects?

Anova(fish_bio_full_mod_algae_log) #nothing significant***
vif(fish_bio_full_mod_algae_log) #all good

#see below for corr checks between algae n15 and structure

fish_bio_full_mod_algae_log_int <-lmer(log(sum_fish_biomass)~N.15_at_30m * wind.exposure + N.15_at_30m *structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae) #
summary(fish_bio_full_mod_algae_log_int)
plot(fish_bio_full_mod_algae_log_int)
qqnorm(resid(fish_bio_full_mod_algae_log))
qqline(resid(fish_bio_full_mod_algae_log))
#looks better - use this
#still some high correlations of fixed effects?

Anova(fish_bio_full_mod_algae_log_int) #structure significant
car::vif(fish_bio_full_mod_algae_log_int) #SUPER HIGH


#species richness----
fish_rich_full_mod_algae <-lmer(SR~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae) 
summary(fish_rich_full_mod_algae)
plot(fish_rich_full_mod_algae)
qqnorm(resid(fish_rich_full_mod_algae))
qqline(resid(fish_rich_full_mod_algae))
#all looks good*


Anova(fish_rich_full_mod_algae) #nothing significant****
vif(fish_rich_full_mod_algae) #all fine

#with interactions:
fish_rich_full_mod_algae_int <-lmer(SR~N.15_at_30m  * wind.exposure + N.15_at_30m  *structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae) 
summary(fish_rich_full_mod_algae_int)
Anova(fish_rich_full_mod_algae_int)
vif(fish_rich_full_mod_algae_int) #super high

#species evenness----
fish_even_full_mod_algae <-lmer(evenness~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae) #singular
summary(fish_even_full_mod_algae)
plot(fish_even_full_mod_algae)
qqnorm(resid(fish_even_full_mod_algae))
qqline(resid(fish_even_full_mod_algae))
#looks okay

Anova(fish_even_full_mod_algae) #nothing significant anyway....
plot_summs(fish_even_full_mod_algae)

#try removing exposure:
fish_even_red_mod_algae <-lmer(evenness~N.15_at_30m   + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae)
#still singular.

range(fish_comb_dat_levels_algae$evenness) #very small range of values.


fish_even_full_mod_algae <-lmer(evenness~N.15_at_30m  * wind.exposure + N.15_at_30m*structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae) 
summary(fish_even_full_mod_algae)
Anova(fish_even_full_mod_algae) #nothing significant anyway....



#shannon----
fish_shannon_full_mod_algae <-lmer(shannon~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae)   #singular
summary(fish_shannon_full_mod_algae)
plot(fish_shannon_full_mod_algae)
qqnorm(resid(fish_shannon_full_mod_algae))
qqline(resid(fish_shannon_full_mod_algae))


Anova(fish_shannon_full_mod_algae) #nothing significant****
plot_summs(fish_shannon_full_mod_algae)

fish_shannon_full_mod_algae <-lmer(shannon~N.15_at_30m * wind.exposure + N.15_at_30m *structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae)   #singular
summary(fish_shannon_full_mod_algae)
Anova(fish_shannon_full_mod_algae) #nothing significant****

```



###look at individual trophic groups versus algae n15-----
```{r}
fish_fg_dens_dat_levels_algae

#density----
fish_herb_dens_mod_algae <-lmer(log(Herb_density+1)~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae)   
summary(fish_herb_dens_mod_algae)
plot(fish_herb_dens_mod_algae)
qqnorm(resid(fish_herb_dens_mod_algae))
Anova(fish_herb_dens_mod_algae)
anova(fish_herb_dens_mod_algae)
#nothing sig


fish_herb_dens_mod_algae <-lmer(log(Herb_density+1)~N.15_at_30m  * wind.exposure +N.15_at_30m  *  structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae)   
#sig interaction.....
vif(fish_herb_dens_mod_algae) #but high vif...


fish_invmob_dens_mod_algae <-lmer(log(InvMob_density+1)~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae)   #singular
summary(fish_invmob_dens_mod_algae)
plot(fish_invmob_dens_mod_algae)
qqnorm(resid(fish_invmob_dens_mod_algae))
Anova(fish_invmob_dens_mod_algae)
anova(fish_invmob_dens_mod_algae)
#algae n15 sig

fish_omni_dens_mod_algae <-lmer(log(Omnivr_density+1)~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae)   #singular
summary(fish_omni_dens_mod_algae)
plot(fish_omni_dens_mod_algae)
qqnorm(resid(fish_omni_dens_mod_algae))
Anova(fish_omni_dens_mod_algae)
anova(fish_omni_dens_mod_algae)
#nothing sig

fish_plank_dens_mod_algae <-lmer(log(Plktiv_density+1)~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae)   
summary(fish_plank_dens_mod_algae)
plot(fish_plank_dens_mod_algae)
qqnorm(resid(fish_plank_dens_mod_algae))
Anova(fish_plank_dens_mod_algae)
anova(fish_plank_dens_mod_algae)
#nothing sig

fish_fiscep_dens_mod_algae <-lmer(log(FisCep_density+1)~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae)   #singular
summary(fish_fiscep_dens_mod_algae)
plot(fish_fiscep_dens_mod_algae)
qqnorm(resid(fish_fiscep_dens_mod_algae))
Anova(fish_fiscep_dens_mod_algae)
anova(fish_fiscep_dens_mod_algae)
#algae n15 very sig

fish_invses_dens_mod_algae <-lmer(log(InvSes_density+1)~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae)    #singular
summary(fish_invses_dens_mod_algae)
plot(fish_invses_dens_mod_algae)
qqnorm(resid(fish_invses_dens_mod_algae))
Anova(fish_invses_dens_mod_algae)
anova(fish_invses_dens_mod_algae)
#nothing sig


###biomass-----
fish_herb_bio_mod_algae <-lmer(log(Herb_biomass+1)~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae)   
summary(fish_herb_bio_mod_algae)
plot(fish_herb_bio_mod_algae)
qqnorm(resid(fish_herb_bio_mod_algae))
Anova(fish_herb_bio_mod_algae)
anova(fish_herb_bio_mod_algae)
#nothing sig

fish_invmob_bio_mod_algae <-lmer(log(InvMob_biomass+1)~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae) 
summary(fish_invmob_bio_mod_algae)
plot(fish_invmob_bio_mod_algae)
qqnorm(resid(fish_invmob_bio_mod_algae))
Anova(fish_invmob_bio_mod_algae)
anova(fish_invmob_bio_mod_algae)
#algae n15 and structural complexity sig

fish_omni_bio_mod_algae <-lmer(log(Omnivr_biomass+1)~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae) 
summary(fish_omni_bio_mod_algae)
plot(fish_omni_bio_mod_algae)
qqnorm(resid(fish_omni_bio_mod_algae))
Anova(fish_omni_bio_mod_algae)
anova(fish_omni_bio_mod_algae)
#nothing sig

fish_plank_bio_mod_algae <-lmer(log(Plktiv_biomass+1)~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae)   
summary(fish_plank_bio_mod_algae)
plot(fish_plank_bio_mod_algae)
qqnorm(resid(fish_plank_bio_mod_algae))
Anova(fish_plank_bio_mod_algae)
anova(fish_plank_bio_mod_algae)
#nothing sig

fish_fiscep_bio_mod_algae <-lmer(log(FisCep_biomass+1)~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae)   #singular
summary(fish_fiscep_bio_mod_algae)
plot(fish_fiscep_bio_mod_algae)
qqnorm(resid(fish_fiscep_bio_mod_algae))
Anova(fish_fiscep_bio_mod_algae)
anova(fish_fiscep_bio_mod_algae)
#algae n15 very sig

fish_invses_bio_mod_algae <-lmer(log(InvSes_biomass+1)~N.15_at_30m  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae)    #singular
summary(fish_invses_bio_mod_algae)
plot(fish_invses_bio_mod_algae)
qqnorm(resid(fish_invses_bio_mod_algae))
Anova(fish_invses_bio_mod_algae)
anova(fish_invses_bio_mod_algae)
#nothing sig


#then would need to check for non-linearities:

#looks like positive effect of n15 on piscivores, mobile invertebrate feeders (biomass and density) no effect on anything else

fish_comb_dat_levels_algae%>%
  ggplot(aes(x = N.15_at_30m, y = log(FisCep_biomass+1)))+
  geom_point()+
  geom_smooth(method = "lm")


fish_comb_dat_levels_algae%>%
  ggplot(aes(x = N.15_at_30m, y = FisCep_biomass))+
  geom_point()+
  geom_smooth(method = "lm")


fish_comb_dat_levels_algae%>%
  ggplot(aes(x = N.15_at_30m, y = log(InvMob_biomass+1)))+
  geom_point()+
  geom_smooth(method = "lm")

fish_comb_dat_levels_algae%>%
  ggplot(aes(x = N.15_at_30m, y = InvMob_biomass))+
  geom_point()+
  geom_smooth(method = "lm")


fish_comb_dat_levels_algae%>%
  dplyr::select(motu, site.name, wind.exposure, transect, structural_complexity_0to5, N.15_at_30m, FisCep_density,
         Plktiv_density, Omnivr_density, InvMob_density, Herb_density)%>%
  pivot_longer(cols = ends_with("density"),
               names_to = c("Feeding_Group", "type"), values_to = "Density", names_sep = "_")%>%
  group_by(N.15_at_30m, Feeding_Group)%>%
  summarize(mean_dens = mean(Density))%>%
  ggplot(aes(x = N.15_at_30m, y = mean_dens, colour = Feeding_Group, fill = Feeding_Group ))+
  geom_point()+
  geom_line()
 # stat_smooth(method = "lm")

fish_comb_dat_levels_algae%>%
  dplyr::select(motu, site.name, wind.exposure, transect, structural_complexity_0to5, N.15_at_30m, FisCep_density,
         Plktiv_density, Omnivr_density, InvMob_density, Herb_density)%>%
  pivot_longer(cols = ends_with("density"),
               names_to = c("Feeding_Group", "type"), values_to = "Density", names_sep = "_")%>%
  group_by(N.15_at_30m, Feeding_Group)%>%
  summarize(mean_dens = mean(log(Density+1)))%>%
  ggplot(aes(x = N.15_at_30m, y = mean_dens, colour = Feeding_Group, fill = Feeding_Group ))+
  geom_point()+
  geom_line()
 # stat_smooth(method = "lm", formula = y ~ poly(x, 2))



fish_comb_dat_levels_algae%>%
  dplyr::select(motu, site.name, wind.exposure, transect, structural_complexity_0to5, N.15_at_30m, FisCep_biomass,
         Plktiv_biomass, Omnivr_biomass, InvMob_biomass, Herb_biomass)%>%
  pivot_longer(cols = ends_with("biomass"),
               names_to = c("Feeding_Group", "type"), values_to = "Biomass", names_sep = "_")%>%
  group_by(N.15_at_30m, Feeding_Group)%>%
  summarize(mean_bio = mean(Biomass))%>%
  ggplot(aes(x = N.15_at_30m, y = mean_bio, colour = Feeding_Group, fill = Feeding_Group ))+
  geom_point()+
  geom_line()
 # stat_smooth(method = "lm")

fish_comb_dat_levels_algae%>%
dplyr::select(motu, site.name, wind.exposure, transect, structural_complexity_0to5, N.15_at_30m, FisCep_biomass,
         Plktiv_biomass, Omnivr_biomass, InvMob_biomass, Herb_biomass)%>%
  pivot_longer(cols = ends_with("biomass"),
               names_to = c("Feeding_Group", "type"), values_to = "Biomass", names_sep = "_")%>%
  group_by(N.15_at_30m, Feeding_Group)%>%
  summarize(mean_bio= mean(log(Biomass+1)))%>%
  ggplot(aes(x = N.15_at_30m, y = mean_bio, colour = Feeding_Group, fill = Feeding_Group ))+
  geom_point()+
  geom_line()
 # stat_smooth(method = "lm", formula = y ~ poly(x, 2))

```

##by restoration status----
```{r}
#run lmms----
#total biomass----
fish_bio_full_mod_rest <-lmer(sum_fish_biomass~motu  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae) #
summary(fish_bio_full_mod_rest)
plot(fish_bio_full_mod_rest)
qqnorm(resid(fish_bio_full_mod_rest))
qqline(resid(fish_bio_full_mod_rest))
#LOOKS BAD

#use log again: 
fish_bio_full_mod_rest_log <-lmer(log(sum_fish_biomass)~motu  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae) #
summary(fish_bio_full_mod_rest_log)
plot(fish_bio_full_mod_rest_log)
qqnorm(resid(fish_bio_full_mod_rest_log))
qqline(resid(fish_bio_full_mod_rest_log))
#looks better - use this
#still some high correlations of fixed effects?

Anova(fish_bio_full_mod_rest_log) #nothing significant***
vif(fish_bio_full_mod_rest_log) #all good

#see below for corr checks between algae n15 and structure



#species richness----
fish_rich_full_mod_rest <-lmer(SR~motu  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae) #depth_max_m + start_distance_to_shore_m
summary(fish_rich_full_mod_algae)
plot(fish_rich_full_mod_algae)
qqnorm(resid(fish_rich_full_mod_rest))
qqline(resid(fish_rich_full_mod_rest))
#all looks good*


Anova(fish_rich_full_mod_rest) #nothing significant****
vif(fish_rich_full_mod_rest) #all fine



#species evenness----
fish_even_full_mod_rest<-lmer(evenness~motu  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae) #singular
summary(fish_even_full_mod_rest)
plot(fish_even_full_mod_rest)
qqnorm(resid(fish_even_full_mod_rest))
qqline(resid(fish_even_full_mod_rest))
#looks okay

Anova(fish_even_full_mod_rest) #nothing significant except wind exposure anyway....
plot_summs(fish_even_full_mod_rest)

#try removing exposure:
fish_even_red_mod_rest <-lmer(evenness~motu   + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae)
#still singular.

range(fish_comb_dat_levels_algae$evenness) #very small range of values.


#shannon----
fish_shannon_full_mod_rest <-lmer(shannon~motu  + wind.exposure + structural_complexity_0to5  + (1|site.name), data = fish_comb_dat_levels_algae)   #singular
summary(fish_shannon_full_mod_rest)
plot(fish_shannon_full_mod_rest)
qqnorm(resid(fish_shannon_full_mod_rest))
qqline(resid(fish_shannon_full_mod_rest))


Anova(fish_shannon_full_mod_rest) #nothing significant except wind exposure
plot_summs(fish_shannon_full_mod_rest)



```


##---------create model estimated plots for responses in paper------------
```{r}

#fish biomass-----
emmeans(fish_bio_full_mod_rest_log, ~ motu|structural_complexity_0to5, type = "response")

pairs(emmeans(fish_bio_full_mod_sb_level_log, ~ motu, type = "response"))

plot_data_fish_bio<-emmip(fish_bio_full_mod_sb_level_log, ~ motu,
    CIs = TRUE, plotit=FALSE) #      type = "response", 

plot_data_fish_bio

fish_total_bio_est_plot_sb<-
ggplot(data = plot_data_fish_bio, aes(x = seabird_level, y = yvar, color = seabird_level, fill = seabird_level, group = seabird_level))+
#  geom_point(pch = 4,  position = position_dodge(.3))+
  geom_pointrange(aes(ymin = LCL, ymax = UCL), alpha = .3, linewidth = 2, size = 0,  position = position_dodge(.1)) + #,  position = position_dodge(.3)
  geom_point(data = fish_comb_dat_levels_algae, 
             aes(y = log(sum_fish_biomass), x = seabird_level), size = 2.5, alpha = .5,  position = position_dodge(.3))+ 
    geom_line(alpha = .5 ,  position = position_dodge(.1))+
scale_fill_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+ #low-mid-high = red-yellow-green
    scale_colour_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+#low-mid-high = red-yellow-green
  ylab("fish biomass (log kg/ha)")+
  xlab("seabird biomass")+
   theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = "none")

fish_total_bio_est_plot_sb

range(fish_comb_dat_levels_algae$N.15_at_30m) #3.430000 6.993333

plot_data_fish_bio_n15<-emmip(fish_bio_full_mod_algae_log, ~ N.15_at_30m, at = list(N.15_at_30m = seq(3.430000, 6.994, by = .01)),
    CIs = TRUE, plotit=FALSE) #      type = "response", 

plot_data_fish_bio_n15

fish_total_bio_est_plot_n15<-
fish_comb_dat_levels_algae %>%
   ggplot(aes(x = N.15_at_30m, y = log(sum_fish_biomass)))+
   geom_ribbon(data = plot_data_fish_bio_n15, aes(x = N.15_at_30m, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
 geom_line(data = plot_data_fish_bio_n15, aes(x = N.15_at_30m, y = yvar))+
    geom_point(alpha = .5, aes(color = motu, fill = motu))+
 # scale_fill_manual(values = c( "Rimatuu" = "#CD1913", "Reiono" = "#F2BB05", "Aie" ="#2F9D3E"))+ #low-mid-high = red-yellow-green
    scale_colour_manual(values = c( "Rimatuu" = "#CD1913", "Reiono" = "#F2BB05", "Aie" ="#2F9D3E"))+#low-mid-high = red-yellow-green
 # ylab("fish biomass (log kg/ha)")+
  xlab("algae N15")+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = "none")

fish_total_bio_est_plot_n15

#richness----
emmeans(fish_rich_full_mod_sb_level, ~ seabird_level|structural_complexity_0to5, type = "response")

pairs(emmeans(fish_rich_full_mod_sb_level, ~ seabird_level, type = "response"))

plot_data_fish_rich<-emmip(fish_rich_full_mod_sb_level, ~ seabird_level,
    CIs = TRUE, plotit=FALSE) #      type = "response", 

plot_data_fish_rich

fish_total_rich_est_plot_sb<-
ggplot(data = plot_data_fish_rich, aes(x = seabird_level, y = yvar, color = seabird_level, fill = seabird_level, group = seabird_level))+
#  geom_point(pch = 4,  position = position_dodge(.3))+
  geom_pointrange(aes(ymin = LCL, ymax = UCL), alpha = .3, linewidth = 2, size = 0,  position = position_dodge(.1)) + #,  position = position_dodge(.3)
  geom_point(data = fish_comb_dat_levels_algae, 
             aes(y = SR, x = seabird_level), size = 2.5, alpha = .5,  position = position_dodge(.3))+ 
    geom_line(alpha = .5 ,  position = position_dodge(.1))+
scale_fill_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+ #low-mid-high = red-yellow-green
    scale_colour_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+#low-mid-high = red-yellow-green
  ylab("fish species richness (#)")+
  xlab("seabird biomass")+
   theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = "none")

fish_total_rich_est_plot_sb


plot_data_fish_rich_n15<-emmip(fish_rich_full_mod_algae, ~ N.15_at_30m, at = list(N.15_at_30m = seq(3.430000, 6.994, by = .01)),
    CIs = TRUE, plotit=FALSE) #      type = "response", 

plot_data_fish_rich_n15

fish_total_rich_est_plot_n15<-
fish_comb_dat_levels_algae %>%
   ggplot(aes(x = N.15_at_30m, y = SR))+
   geom_ribbon(data = plot_data_fish_rich_n15, aes(x = N.15_at_30m, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
 geom_line(data = plot_data_fish_rich_n15, aes(x = N.15_at_30m, y = yvar))+
    geom_point(alpha = .5, aes(color = seabird_level, fill = seabird_level))+
  scale_fill_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+ #low-mid-high = red-yellow-green
    scale_colour_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+#low-mid-high = red-yellow-green
  ylab("fish species richness (#)")+
  xlab("algae N15")+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
       legend.position = "none")

fish_total_rich_est_plot_n15



#evenness----
emmeans(fish_even_full_mod_sb_level, ~ seabird_level|structural_complexity_0to5, type = "response")

pairs(emmeans(fish_even_full_mod_sb_level, ~ seabird_level, type = "response"))

plot_data_fish_even<-emmip(fish_even_full_mod_sb_level, ~ seabird_level,
    CIs = TRUE, plotit=FALSE) #      type = "response", 

plot_data_fish_even

fish_total_even_est_plot_sb<-
ggplot(data = plot_data_fish_even, aes(x = seabird_level, y = yvar, color = seabird_level, fill = seabird_level, group = seabird_level))+
#  geom_point(pch = 4,  position = position_dodge(.3))+
  geom_pointrange(aes(ymin = LCL, ymax = UCL), alpha = .3, linewidth = 2, size = 0,  position = position_dodge(.1)) + #,  position = position_dodge(.3)
  geom_point(data = fish_comb_dat_levels_algae, 
             aes(y = evenness, x = seabird_level), size = 2.5, alpha = .5,  position = position_dodge(.3))+ 
    geom_line(alpha = .5 ,  position = position_dodge(.1))+
scale_fill_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+ #low-mid-high = red-yellow-green
    scale_colour_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+#low-mid-high = red-yellow-green
  ylab("fish evenness")+
  xlab("seabird biomass")+
   theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = "none" )

fish_total_even_est_plot_sb


plot_data_fish_even_n15<-emmip(fish_even_full_mod_algae, ~ N.15_at_30m, at = list(N.15_at_30m = seq(3.430000, 6.994, by = .01)),
    CIs = TRUE, plotit=FALSE) #      type = "response", 

plot_data_fish_even_n15

fish_total_even_est_plot_n15<-
fish_comb_dat_levels_algae %>%
   ggplot(aes(x = N.15_at_30m, y = evenness))+
   geom_ribbon(data = plot_data_fish_even_n15, aes(x = N.15_at_30m, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
 geom_line(data = plot_data_fish_even_n15, aes(x = N.15_at_30m, y = yvar))+
    geom_point(alpha = .5, aes(color = seabird_level, fill = seabird_level))+
  scale_fill_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+ #low-mid-high = red-yellow-green
    scale_colour_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+#low-mid-high = red-yellow-green
  ylab("fish evenness")+
  xlab("algae N15")+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = "none")

fish_total_even_est_plot_n15



#shannon----
emmeans(fish_shannon_full_mod_sb_level, ~ seabird_level|structural_complexity_0to5, type = "response")

pairs(emmeans(fish_shannon_full_mod_sb_level, ~ seabird_level, type = "response"))

plot_data_fish_shannon<-emmip(fish_shannon_full_mod_sb_level, ~ seabird_level,
    CIs = TRUE, plotit=FALSE) #      type = "response", 

plot_data_fish_shannon

fish_total_shannon_est_plot_sb<-
ggplot(data = plot_data_fish_shannon, aes(x = seabird_level, y = yvar, color = seabird_level, fill = seabird_level, group = seabird_level))+
#  geom_point(pch = 4,  position = position_dodge(.3))+
  geom_pointrange(aes(ymin = LCL, ymax = UCL), alpha = .3, linewidth = 2, size = 0,  position = position_dodge(.1)) + #,  position = position_dodge(.3)
  geom_point(data = fish_comb_dat_levels_algae, 
             aes(y = shannon, x = seabird_level), size = 2.5, alpha = .5,  position = position_dodge(.3))+ 
    geom_line(alpha = .5 ,  position = position_dodge(.1))+
scale_fill_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+ #low-mid-high = red-yellow-green
    scale_colour_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+#low-mid-high = red-yellow-green
  ylab("fish shannon diversity")+
  xlab("seabird biomass")+
   theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = "none" )

fish_total_shannon_est_plot_sb


plot_data_fish_shannon_n15<-emmip(fish_shannon_full_mod_algae, ~ N.15_at_30m, at = list(N.15_at_30m = seq(3.430000, 6.994, by = .01)),
    CIs = TRUE, plotit=FALSE) #      type = "response", 

plot_data_fish_shannon_n15

fish_total_shannon_est_plot_n15<-
fish_comb_dat_levels_algae %>%
   ggplot(aes(x = N.15_at_30m, y = shannon))+
   geom_ribbon(data = plot_data_fish_shannon_n15, aes(x = N.15_at_30m, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
 geom_line(data = plot_data_fish_shannon_n15, aes(x = N.15_at_30m, y = yvar))+
    geom_point(alpha = .5)+ #aes(color = seabird_level, fill = seabird_level)
 # scale_fill_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+ #low-mid-high = red-yellow-green
  #  scale_colour_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+#low-mid-high = red-yellow-green
  ylab("fish shannon diversity")+
  xlab("algae N15")+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = "none")

fish_total_shannon_est_plot_n15


##combine all plots and save:----
fish_comm_tots_mod_est_plots<-
  plot_grid(fish_total_bio_est_plot_sb, fish_total_bio_est_plot_n15,
            fish_total_rich_est_plot_sb, fish_total_rich_est_plot_n15,
            fish_total_even_est_plot_sb, fish_total_even_est_plot_n15,
            fish_total_shannon_est_plot_sb, fish_total_shannon_est_plot_n15,
            ncol = 2) #, labels = "auto", label_fontface = "plain"

fish_comm_tots_mod_est_plots

ggsave(fish_comm_tots_mod_est_plots, file = "../output/seabird-fish/fish_comm_tots_mod_est_plots_COMBINED.jpg",
    width = 7, height = 9)


```

###new: just line plots by algae n15, no colors:
```{r}
#fish biomass-----
range(fish_comb_dat_levels_algae$N.15_at_30m) #3.430000 6.993333

plot_data_fish_bio_n15<-emmip(fish_bio_full_mod_algae_log, ~ N.15_at_30m, at = list(N.15_at_30m = seq(3.430000, 6.994, by = .01)),
    CIs = TRUE, plotit=FALSE) #      type = "response", 

plot_data_fish_bio_n15

fish_total_bio_est_plot_n15<-
fish_comb_dat_levels_algae %>%
   ggplot(aes(x = N.15_at_30m, y = log(sum_fish_biomass)))+
   geom_ribbon(data = plot_data_fish_bio_n15, aes(x = N.15_at_30m, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
 geom_line(data = plot_data_fish_bio_n15, aes(x = N.15_at_30m, y = yvar))+
    geom_point(alpha = .5)+
 # scale_fill_manual(values = c( "Rimatuu" = "#CD1913", "Reiono" = "#F2BB05", "Aie" ="#2F9D3E"))+ #low-mid-high = red-yellow-green
   # scale_colour_manual(values = c( "Rimatuu" = "#CD1913", "Reiono" = "#F2BB05", "Aie" ="#2F9D3E"))+#low-mid-high = red-yellow-green
  ylab("fish biomass (log kg/ha)")+
  xlab(expression(algal~delta^15~N))+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = "none")

fish_total_bio_est_plot_n15

#richness----

plot_data_fish_rich_n15<-emmip(fish_rich_full_mod_algae, ~ N.15_at_30m, at = list(N.15_at_30m = seq(3.430000, 6.994, by = .01)),
    CIs = TRUE, plotit=FALSE) #      type = "response", 

plot_data_fish_rich_n15

fish_total_rich_est_plot_n15<-
fish_comb_dat_levels_algae %>%
   ggplot(aes(x = N.15_at_30m, y = SR))+
   geom_ribbon(data = plot_data_fish_rich_n15, aes(x = N.15_at_30m, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
 geom_line(data = plot_data_fish_rich_n15, aes(x = N.15_at_30m, y = yvar))+
    geom_point(alpha = .5)+ # aes(color = seabird_level, fill = seabird_level)
 # scale_fill_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+ #low-mid-high = red-yellow-green
  #  scale_colour_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+#low-mid-high = red-yellow-green
  ylab("fish species richness (#)")+
  xlab(expression(algal~delta^15~N))+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
       legend.position = "none")

fish_total_rich_est_plot_n15



#evenness----

plot_data_fish_even_n15<-emmip(fish_even_full_mod_algae, ~ N.15_at_30m, at = list(N.15_at_30m = seq(3.430000, 6.994, by = .01)),
    CIs = TRUE, plotit=FALSE) #      type = "response", 

plot_data_fish_even_n15

fish_total_even_est_plot_n15<-
fish_comb_dat_levels_algae %>%
   ggplot(aes(x = N.15_at_30m, y = evenness))+
   geom_ribbon(data = plot_data_fish_even_n15, aes(x = N.15_at_30m, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
 geom_line(data = plot_data_fish_even_n15, aes(x = N.15_at_30m, y = yvar))+
    geom_point(alpha = .5)+ #, aes(color = seabird_level, fill = seabird_level)
#  scale_fill_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+ #low-mid-high = red-yellow-green
  #  scale_colour_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+#low-mid-high = red-yellow-green
  ylab("fish evenness")+
  xlab(expression(algal~delta^15~N))+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = "none")

fish_total_even_est_plot_n15



#shannon----

plot_data_fish_shannon_n15<-emmip(fish_shannon_full_mod_algae, ~ N.15_at_30m, at = list(N.15_at_30m = seq(3.430000, 6.994, by = .01)),
    CIs = TRUE, plotit=FALSE) #      type = "response", 

plot_data_fish_shannon_n15

fish_total_shannon_est_plot_n15<-
fish_comb_dat_levels_algae %>%
   ggplot(aes(x = N.15_at_30m, y = shannon))+
   geom_ribbon(data = plot_data_fish_shannon_n15, aes(x = N.15_at_30m, y = yvar, ymin = LCL, ymax=UCL), alpha = .2, lwd=0)+
 geom_line(data = plot_data_fish_shannon_n15, aes(x = N.15_at_30m, y = yvar))+
    geom_point(alpha = .5)+ #aes(color = seabird_level, fill = seabird_level)
 # scale_fill_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+ #low-mid-high = red-yellow-green
  #  scale_colour_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+#low-mid-high = red-yellow-green
  ylab("fish shannon diversity")+
  xlab(expression(algal~delta^15~N))+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = "none")

fish_total_shannon_est_plot_n15


##combine all plots and save:----

fish_total_bio_est_plot_n152<-
  fish_total_bio_est_plot_n15+
  labs(subtitle = "a.")

fish_total_rich_est_plot_n152<-
  fish_total_rich_est_plot_n15+
  labs(subtitle = "b.")

fish_total_even_est_plot_n152<-
  fish_total_even_est_plot_n15+
  labs(subtitle = "c.")

fish_total_shannon_est_plot_n152<-
  fish_total_shannon_est_plot_n15+
  labs(subtitle = "d.")


fish_comm_tots_mod_est_plots<-
  plot_grid( fish_total_bio_est_plot_n152,
            fish_total_rich_est_plot_n152,
             fish_total_even_est_plot_n152,
             fish_total_shannon_est_plot_n152,
            ncol = 2) #, labels = "auto", label_fontface = "plain"

fish_comm_tots_mod_est_plots

ggsave(fish_comm_tots_mod_est_plots, file = "../output/seabird-fish/fish_comm_tots_mod_est_plots_COMBINED_no_color.jpg",
    width = 7, height = 7)


```



####stacked bar plot by seabird levels----
```{r}


##add structure to seabird level stacked bar plot----

fish_fg_bio_stack_barplot_seabird_level_structure<-
fish_comb_dat_levels_algae%>%
  pivot_longer(cols = c(Herb_biomass:InvSes_biomass),
                                          names_to = "feeding_group",
                                          values_to = "biomass_kg_ha")%>%
  group_by(feeding_group, seabird_level)%>%
  summarize(mean_biomass = mean(biomass_kg_ha),
            mean_structure = mean(structural_complexity_0to5),
            se_structure = sd(structural_complexity_0to5)/length(structural_complexity_0to5))%>%
  mutate(feeding_group = str_remove_all(feeding_group, '_biomass'))%>%
  mutate(feeding_group = as.factor(feeding_group))%>%
    mutate(feeding_group = fct_relevel(feeding_group, c("Herb", "Omnivr", "Plktiv", "InvSes", "InvMob", "FisCep")))%>%
  mutate(feeding_group = fct_recode(feeding_group, "Herbivore" = "Herb", "Mobile Invertebrate Feeder" = "InvMob", "Omnivore" = "Omnivr", 
                                                     "Planktivore" = "Plktiv", "Piscivore" = "FisCep", "Sessile Invertebrate Feeder" = "InvSes"))%>%
  ggplot(aes(x = seabird_level))+
  geom_bar(aes(fill = feeding_group, y = mean_biomass), position = "stack", stat =  "identity")+
  scale_fill_brewer(palette = "Set2")+
  geom_point(aes(y = mean_structure*120))+
  geom_line(aes(y =  mean_structure*120, group = feeding_group))+
  geom_errorbar(aes(y = mean_structure*120, ymin = (mean_structure*120)-se_structure*120, ymax = (mean_structure*120)+se_structure*120), width = .1)+
    scale_y_continuous(name = "mean biomass (kg/ha)", #    # Features of the first axis
    sec.axis = sec_axis(~./120, name="structural complexity (0-5)"))+    # Add a second axis and specify its features
  xlab("seabird level")+
  ylab("mean biomass (kg/ha)")+
  labs(fill = "Feeding group")+
    theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1)
        )
  
  fish_fg_bio_stack_barplot_seabird_level_structure
  

  
ggsave(fish_fg_bio_stack_barplot_seabird_level_structure, file = "../output/seabird-fish/fish_stack_plot_seabird_structure_1plot.jpg",
    width = 7, height = 5)


##repeat with density-----

fish_fg_dens_stack_barplot_seabird_level_structure<-
fish_fg_dens_dat_levels_algae%>%
  pivot_longer(cols = c(Herb_density:InvSes_density),
                                          names_to = "feeding_group",
                                          values_to = "density")%>%
  group_by(feeding_group, seabird_level)%>%
  summarize(mean_density = mean(density),
            mean_structure = mean(structural_complexity_0to5),
            se_structure = sd(structural_complexity_0to5)/length(structural_complexity_0to5))%>%
  mutate(feeding_group = str_remove_all(feeding_group, '_density'))%>%
  mutate(feeding_group = as.factor(feeding_group))%>%
    mutate(feeding_group = fct_relevel(feeding_group, c("Herb", "Omnivr", "Plktiv", "InvSes", "InvMob", "FisCep")))%>%
  mutate(feeding_group = fct_recode(feeding_group, "Herbivore" = "Herb", "Mobile Invertebrate Feeder" = "InvMob", "Omnivore" = "Omnivr", 
                                                     "Planktivore" = "Plktiv", "Piscivore" = "FisCep", "Sessile Invertebrate Feeder" = "InvSes"))%>%
  ggplot(aes(x = seabird_level))+
  geom_bar(aes(fill = feeding_group, y = mean_density), position = "stack", stat =  "identity")+
  scale_fill_brewer(palette = "Set2")+
  geom_point(aes(y = mean_structure*1500))+
  geom_line(aes(y =  mean_structure*1500, group = feeding_group))+
  geom_errorbar(aes(y = mean_structure*1500, ymin = (mean_structure*1500)-se_structure*1500, ymax = (mean_structure*1500)+se_structure*1500), width = .1)+
    scale_y_continuous(name = "mean density (#/ha)", #    # Features of the first axis
    sec.axis = sec_axis(~./1500, breaks = c(0,1,2,3,4,5), name="structural complexity (0-5)"))+    # Add a second axis and specify its features
  xlab("seabird level")+
  labs(fill = "Feeding group")+
    theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1)
        )
  
  fish_fg_dens_stack_barplot_seabird_level_structure
  

  
ggsave(fish_fg_dens_stack_barplot_seabird_level_structure, file = "../output/seabird-fish/fish_DENS_stack_plot_seabird_structure_1plot.jpg",
    width = 7, height = 5)


fish_stack_plots<-plot_grid(fish_fg_bio_stack_barplot_seabird_level_structure, fish_fg_dens_stack_barplot_seabird_level_structure, nrow = 2)
fish_stack_plots


ggsave(fish_stack_plots, file = "../output/seabird-fish/fish_stack_plots_COMBINED.jpg",
    width = 7, height = 7)


###redo by management status----------
fish_fg_bio_stack_barplot_mgmt_structure<-
fish_comb_dat_levels_algae%>%
  pivot_longer(cols = c(Herb_biomass:InvSes_biomass),
                                          names_to = "feeding_group",
                                          values_to = "biomass_kg_ha")%>%
  group_by(feeding_group, motu)%>%
  summarize(mean_biomass = mean(biomass_kg_ha),
            mean_structure = mean(structural_complexity_0to5),
            se_structure = sd(structural_complexity_0to5)/length(structural_complexity_0to5))%>%
  mutate(feeding_group = str_remove_all(feeding_group, '_biomass'))%>%
  mutate(feeding_group = as.factor(feeding_group))%>%
    mutate(feeding_group = fct_relevel(feeding_group, c("Herb", "Omnivr", "Plktiv", "InvSes", "InvMob", "FisCep")))%>%
  mutate(feeding_group = fct_recode(feeding_group, "Herbivore" = "Herb", "Mobile Invertebrate Feeder" = "InvMob", "Omnivore" = "Omnivr", 
                                                     "Planktivore" = "Plktiv", "Piscivore" = "FisCep", "Sessile Invertebrate Feeder" = "InvSes"))%>%
  ggplot(aes(x = motu))+
  geom_bar(aes(fill = feeding_group, y = mean_biomass), position = "stack", stat =  "identity")+
 # scale_fill_brewer(palette = "Set2")+
  geom_point(aes(y = mean_structure*120))+
  geom_line(aes(y =  mean_structure*120, group = feeding_group))+
  geom_errorbar(aes(y = mean_structure*120, ymin = (mean_structure*120)-se_structure*120, ymax = (mean_structure*120)+se_structure*120), width = .1)+
    scale_y_continuous(name = "mean biomass (kg/ha)", #    # Features of the first axis
    sec.axis = sec_axis(~./120, name="structural complexity (0-5)"))+    # Add a second axis and specify its features
  xlab("")+
  ylab("mean biomass (kg/ha)")+
  labs(fill = "Feeding group")+
    scale_fill_viridis_d(direction = -1)+
 scale_x_discrete(labels = c('reference','recovering','unrestored'))+
    theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1)
        )
fish_fg_bio_stack_barplot_mgmt_structure


fish_fg_dens_stack_barplot_mgmt_structure<-
fish_fg_dens_dat_levels_algae%>%
  pivot_longer(cols = c(Herb_density:InvSes_density),
                                          names_to = "feeding_group",
                                          values_to = "density")%>%
  group_by(feeding_group, motu)%>%
  summarize(mean_density = mean(density),
            mean_structure = mean(structural_complexity_0to5),
            se_structure = sd(structural_complexity_0to5)/length(structural_complexity_0to5))%>%
  mutate(feeding_group = str_remove_all(feeding_group, '_density'))%>%
  mutate(feeding_group = as.factor(feeding_group))%>%
    mutate(feeding_group = fct_relevel(feeding_group, c("Herb", "Omnivr", "Plktiv", "InvSes", "InvMob", "FisCep")))%>%
  mutate(feeding_group = fct_recode(feeding_group, "Herbivore" = "Herb", "Mobile Invertebrate Feeder" = "InvMob", "Omnivore" = "Omnivr", 
                                                     "Planktivore" = "Plktiv", "Piscivore" = "FisCep", "Sessile Invertebrate Feeder" = "InvSes"))%>%
  ggplot(aes(x = motu))+
  geom_bar(aes(fill = feeding_group, y = mean_density), position = "stack", stat =  "identity")+
 # scale_fill_brewer(palette = "Set2")+
  geom_point(aes(y = mean_structure*1500))+
  geom_line(aes(y =  mean_structure*1500, group = feeding_group))+
  geom_errorbar(aes(y = mean_structure*1500, ymin = (mean_structure*1500)-se_structure*1500, ymax = (mean_structure*1500)+se_structure*1500), width = .1)+
    scale_y_continuous(name = "mean density (#/ha)", #    # Features of the first axis
    sec.axis = sec_axis(~./1500, breaks = c(0,1,2,3,4,5), name="structural complexity (0-5)"))+    # Add a second axis and specify its features
  xlab("")+
  labs(fill = "Feeding group")+
      scale_fill_viridis_d(direction = -1)+
 scale_x_discrete(labels = c('reference','recovering','unrestored'))+
    theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1)
        )
  
  fish_fg_dens_stack_barplot_mgmt_structure
  

fish_stack_plots_by_management<-plot_grid(fish_fg_bio_stack_barplot_mgmt_structure, fish_fg_dens_stack_barplot_mgmt_structure, nrow = 2)
fish_stack_plots_by_management


ggsave(fish_stack_plots_by_management, file = "../output/seabird-fish/fish_stack_plots_COMBINED_BY_MANAGEMENT.jpg",
    width = 7, height = 7)

###redo by management status AND REVERSE TG ORDER----------
fish_fg_bio_stack_barplot_mgmt_structure<-
fish_comb_dat_levels_algae%>%
  pivot_longer(cols = c(Herb_biomass:InvSes_biomass),
                                          names_to = "feeding_group",
                                          values_to = "biomass_kg_ha")%>%
  group_by(feeding_group, motu)%>%
  summarize(mean_biomass = mean(biomass_kg_ha),
            mean_structure = mean(structural_complexity_0to5),
            se_structure = sd(structural_complexity_0to5)/length(structural_complexity_0to5))%>%
  mutate(feeding_group = str_remove_all(feeding_group, '_biomass'))%>%
  mutate(feeding_group = as.factor(feeding_group))%>%
    mutate(feeding_group = fct_relevel(feeding_group, c("FisCep", "InvMob", "InvSes",  "Plktiv",  "Omnivr","Herb")))%>%
  mutate(feeding_group = fct_recode(feeding_group, "Herbivore" = "Herb", "Mobile Invertebrate Feeder" = "InvMob", "Omnivore" = "Omnivr", 
                                                     "Planktivore" = "Plktiv", "Piscivore" = "FisCep", "Sessile Invertebrate Feeder" = "InvSes"))%>%
  ggplot(aes(x = motu))+
  geom_bar(aes(fill = feeding_group, y = mean_biomass), position = "stack", stat =  "identity")+
 # scale_fill_brewer(palette = "Set2")+
  geom_point(aes(y = mean_structure*120))+
  geom_line(aes(y =  mean_structure*120, group = feeding_group))+
  geom_errorbar(aes(y = mean_structure*120, ymin = (mean_structure*120)-se_structure*120, ymax = (mean_structure*120)+se_structure*120), width = .1)+
    scale_y_continuous(name = "mean biomass (kg/ha)", #    # Features of the first axis
    sec.axis = sec_axis(~./120, name="structural complexity (0-5)"))+    # Add a second axis and specify its features
  xlab("")+
  ylab("mean biomass (kg/ha)")+
  labs(fill = "Feeding group")+
    scale_fill_viridis_d(direction = 1)+
 scale_x_discrete(labels = c('reference','recovering','unrestored'))+
    theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1)
        )
fish_fg_bio_stack_barplot_mgmt_structure

fish_fg_dens_stack_barplot_mgmt_structure<-
fish_fg_dens_dat_levels_algae%>%
  pivot_longer(cols = c(Herb_density:InvSes_density),
                                          names_to = "feeding_group",
                                          values_to = "density")%>%
  group_by(feeding_group, motu)%>%
  summarize(mean_density = mean(density),
            mean_structure = mean(structural_complexity_0to5),
            se_structure = sd(structural_complexity_0to5)/length(structural_complexity_0to5))%>%
  mutate(feeding_group = str_remove_all(feeding_group, '_density'))%>%
  mutate(feeding_group = as.factor(feeding_group))%>%
    mutate(feeding_group = fct_relevel(feeding_group, c("FisCep", "InvMob", "InvSes",  "Plktiv",  "Omnivr","Herb")))%>%
  mutate(feeding_group = fct_recode(feeding_group, "Herbivore" = "Herb", "Mobile Invertebrate Feeder" = "InvMob", "Omnivore" = "Omnivr", 
                                                     "Planktivore" = "Plktiv", "Piscivore" = "FisCep", "Sessile Invertebrate Feeder" = "InvSes"))%>%
  ggplot(aes(x = motu))+
  geom_bar(aes(fill = feeding_group, y = mean_density), position = "stack", stat =  "identity")+
 # scale_fill_brewer(palette = "Set2")+
  geom_point(aes(y = mean_structure*1500))+
  geom_line(aes(y =  mean_structure*1500, group = feeding_group))+
  geom_errorbar(aes(y = mean_structure*1500, ymin = (mean_structure*1500)-se_structure*1500, ymax = (mean_structure*1500)+se_structure*1500), width = .1)+
    scale_y_continuous(name = "mean density (#/ha)", #    # Features of the first axis
    sec.axis = sec_axis(~./1500, breaks = c(0,1,2,3,4,5), name="structural complexity (0-5)"))+    # Add a second axis and specify its features
  xlab("")+
  labs(fill = "Feeding group")+
      scale_fill_viridis_d(direction = 1)+
 scale_x_discrete(labels = c('reference','recovering','unrestored'))+
    theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1)
        )
  
  fish_fg_dens_stack_barplot_mgmt_structure
  
  
fish_stack_plots_by_management2<-plot_grid(fish_fg_bio_stack_barplot_mgmt_structure, fish_fg_dens_stack_barplot_mgmt_structure, nrow = 2)
fish_stack_plots_by_management


ggsave(fish_stack_plots_by_management2, file = "../output/seabird-fish/fish_stack_plots_COMBINED_BY_MANAGEMENT_reverse_trophic.jpg",
    width = 7, height = 7)

```


#checking seabird~structure relationships:
```{r}
cor(fish_comb_dat_levels_algae$N.15_at_30m, fish_comb_dat_levels_algae$structural_complexity_0to5) #-0.6498289
cor.test(fish_comb_dat_levels_algae$N.15_at_30m, fish_comb_dat_levels_algae$structural_complexity_0to5)
#t = -4.0101, df = 22, p-value = 0.0005885
#alternative hypothesis: true correlation is not equal to 0
#95 percent confidence interval:
# -0.8344768 -0.3339817
#sample estimates:
#       cor 
#-0.6498289 


cor(fish_comb_dat_levels_algae$N.15_at_30m, fish_comb_dat_levels_algae$structural_complexity_0to5, method = "spearman") #-0.6750057
cor.test(fish_comb_dat_levels_algae$N.15_at_30m, fish_comb_dat_levels_algae$structural_complexity_0to5, method = "spearman")


fish_comb_dat_levels_algae%>%
  ggplot(aes(x = N.15_at_30m, y = structural_complexity_0to5))+ #, fill = seabird_level, colour = seabird_level
  geom_jitter(height = .05, width = .01, alpha = .4)+
  geom_smooth (method = "lm")



fish_comb_dat_levels_algae%>%
  ggplot(aes(x = seabird_level, y = structural_complexity_0to5, fill = seabird_level, colour = seabird_level))+
  geom_boxplot(alpha = .4)+
  geom_jitter(width = .3, height = 0)


```





