---
title: "seabirds_vs_fish_condition"
author: "CEB"
date: '2024-01-23'
output: html_document
---


#load packages
```{r}
library(tidyverse)

library(lme4)
library(car)
library(jtools)

library(emmeans)

library(corrplot)

```


#load data
```{r}
seabirds <- read.csv("../output/n15_seabirds_combined_no_iti.csv", strip.white = T, header = T)
fish_n15_cond <- read.csv("../../fish_isotopes/output/fish_n15_condition.csv", stringsAsFactors = TRUE)
algae_n15<-read.csv("../output/n15_seabirds_combined_no_iti.csv")

```



#merge data
```{r}
#make combined site name column in fish_n15

fishn15.seabirds.cond<-right_join(dplyr::select(seabirds, c("site.name", "breeding_biomass_kgha_side")), 
                                  dplyr::select(fish_n15_cond, c("site.name", "motu", "fish.id", "species", 
                                                   "month.caught", "year.caught", "protection", "TL.cm", "FL.cm", "SL.cm", "whole.weight.g", 
                                                    "n15", "c13", "n.percent", "c.percent")),
                            
                                   by = "site.name")%>%
  mutate(site.name = as.factor(site.name))
fishn15.seabirds.cond


##remove C. argus because n = 1 for Aie----
fishn15.seabirds.cond.r<-
  fishn15.seabirds.cond%>%
  filter(species != "Cephalopholis argus")%>%
  droplevels()


##check sample sizes, lengths per site:----
fishn15.seabirds.cond.r%>%
  group_by(species, site.name)%>%
  summarize(n = length(n15))

```

#run lm's USING ALGAE N15 AT 40
```{r}

#can use algae n15 at 40 m from shore as offshore, because this is present at all sites where we have fish
#because only one site per motu, random effects don't make sense, so run regular lm

#combine data with algae n15----
fishn15.seabirds.cond.algae<-
  left_join(fishn15.seabirds.cond.r, 
            dplyr::select(algae_n15, c("site.name", "N.15_at_10m", "N.15_at_20m","N.15_at_30m","N.15_at_40m")), 
            by = "site.name")
fishn15.seabirds.cond.algae


#n15----
fish_n15_algae_lm<-lm(n15~ N.15_at_40m*species, 
                          data = fishn15.seabirds.cond.algae)
summary(fish_n15_algae_lm)
anova(fish_n15_algae_lm)#everything significant
Anova(fish_n15_algae_lm)
plot(fish_n15_algae_lm) #okay

#N.15_at_40m          56.059  1 21.4254 2.17e-05 ***
#species              26.701  3  3.4017 0.023670 *  
#N.15_at_40m:species  33.384  3  4.2530 0.008836 ** 

#look at emmeans:----
emtrends(fish_n15_algae_lm,  ~ species, var = "N.15_at_40m")
#looks like Ab sept and Ac tri both are positive. Other two trending towards positive but overlaps 0

test(emtrends(fish_n15_algae_lm, ~ species, var = "N.15_at_40m", adjust = "fdr"))
# Abudefduf septemfasciatus             1.708 0.327 57   5.215  <.0001
#Acanthurus triostegus                   0.664 0.313 57   2.121  0.0765
# Lutjanus fulvus                       0.140 0.323 57   0.434  0.6663
# Stegastes nigricans                   0.501 0.330 57   1.515  0.1803


test(emtrends(fish_n15_algae_lm, pairwise~ species, var = "N.15_at_40m", adjust = "fdr"))
# Abudefduf septemfasciatus - Acanthurus triostegus    1.043 0.453 57   2.302  0.0500
# Abudefduf septemfasciatus - Lutjanus fulvus          1.568 0.460 57   3.407  0.0073
# Abudefduf septemfasciatus - Stegastes nigricans      1.207 0.465 57   2.596  0.0360
# Acanthurus triostegus - Lutjanus fulvus              0.524 0.450 57   1.165  0.3735
# Acanthurus triostegus - Stegastes nigricans          0.164 0.455 57   0.360  0.7202
# Lutjanus fulvus - Stegastes nigricans               -0.360 0.462 57  -0.780  0.5265

#Ab sept has strongest effect, all else similar. 


# plot ---------
range(fishn15.seabirds.cond.algae$N.15_at_40m) #3.043333 6.003333
levels(fishn15.seabirds.cond.algae$species)
(mylist <- list(
    N.15_at_40m = seq(3, 6, by = 1),
    species = c("Abudefduf septemfasciatus", "Acanthurus triostegus" ,   "Lutjanus fulvus"     ,     
 "Stegastes nigricans")
))

emmip(fish_n15_algae_lm, species ~ N.15_at_40m, at = mylist, CIs = TRUE)



#plot raw data + lines: 
plot_dat<-emmip(fish_n15_algae_lm, species ~ N.15_at_40m, at = mylist, CIs = TRUE, plotit=FALSE)
plot_dat

fishn15.seabirds.cond.algae %>%
  dplyr::group_by(species, N.15_at_40m)%>%
  dplyr::summarize(mean_n15 = mean(n15))%>%
   ggplot(aes(x = N.15_at_40m, y = mean_n15, color = species, fill = species, group = species))+
  geom_point(alpha = .5)+
geom_line(data = plot_dat, aes(x = N.15_at_40m, y = yvar, color = species, group = species))+
  theme_bw() 


fishn15.seabirds.cond.algae %>%
      mutate(species = fct_relevel(species, c("Acanthurus triostegus", "Stegastes nigricans", "Abudefduf septemfasciatus", "Lutjanus fulvus")))%>%
  group_by(species, N.15_at_40m)%>%
  dplyr::summarize(mean_n15 = mean(n15),
            se = sd(n15)/sqrt(length(n15)))%>%
   ggplot(aes(x = N.15_at_40m, y = mean_n15, color = species, fill = species, group = species))+
  geom_point(alpha = .8)+
  geom_errorbar(aes(ymin = mean_n15 - se, ymax = mean_n15+se))+
   geom_line(data = plot_dat, aes(x = N.15_at_40m, y = yvar, color = species, group = species))+
  ylab(expression(Fish~delta^15~N))+
  xlab(expression(Algae~delta^15~N))+
  labs(color = "", fill = "")+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.2,.85),
        legend.background = element_blank())
        #legent.key = element_rect) #,
        #legend.direction = "horizontal",
      #  legend.box.background = element_rect(colour = "black"))


(mylist2 <- list(
    N.15_at_40m = c(3.043333, 5.233333, 6.003333),
    species = c("Abudefduf septemfasciatus", "Acanthurus triostegus" ,   "Lutjanus fulvus"     ,     
 "Stegastes nigricans")
))
plot_dat2<-emmip(fish_n15_algae_lm, species ~ N.15_at_40m, at = mylist2, CIs = TRUE, plotit=FALSE)
plot_dat2

fishn15.seabirds.cond.algae %>%
      mutate(species = fct_relevel(species, c("Acanthurus triostegus", "Stegastes nigricans", "Abudefduf septemfasciatus", "Lutjanus fulvus")))%>%
   ggplot(aes(x = N.15_at_40m, y = n15, color = species, fill = species, group = species))+
  geom_point(alpha = .5)+
   geom_ribbon(data = plot_dat2, aes(x = N.15_at_40m, y = yvar, ymin = LCL, ymax=UCL, fill = species), alpha = .2, lwd=0)+
 geom_line(data = plot_dat2, aes(x = N.15_at_40m, y = yvar, color = species, group = species))+
  theme_bw() 

fishn15.algan15.plot<-
fishn15.seabirds.cond.algae %>%
      mutate(species = fct_relevel(species, c("Acanthurus triostegus", "Stegastes nigricans", "Abudefduf septemfasciatus", "Lutjanus fulvus")))%>%
   ggplot(aes(x = N.15_at_40m, y = n15, color = species, fill = species, group = species))+
 # geom_point(alpha = .8)+
    geom_jitter(alpha = .7, width = .05, height = 0, size = 2.5)+
   geom_ribbon(data = plot_dat2, aes(x = N.15_at_40m, y = yvar, ymin = LCL, ymax=UCL, fill = species), alpha = .1, lwd=0)+
 geom_line(data = plot_dat2, aes(x = N.15_at_40m, y = yvar, color = species, group = species))+ #, lwd =1.5
  ylab(expression(Fish~delta^15~N))+
  xlab(expression(Algal~delta^15~N))+
  scale_fill_viridis_d(labels = c("Acanthurus triostegus (herbivore)", "Stegastes nigricans (herbivore)", "Abudefduf septemfasciatus (omnivore)", "Lutjanus fulvus (piscivore)"))+
  scale_color_viridis_d(labels = c("Acanthurus triostegus (herbivore)", "Stegastes nigricans (herbivore)", "Abudefduf septemfasciatus (omnivore)", "Lutjanus fulvus (piscivore)"))+
  labs(color = "", fill = "")+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.2,.85),
        legend.background = element_blank())
        #legent.key = element_rect) #,
        #legend.direction = "horizontal",
      #  legend.box.background = element_rect(colour = "black"))
fishn15.algan15.plot


#ggsave("../output/seabird-fishn15/fish_n15_algae_n15_estplot_lines_points_update.jpg", plot = fishn15.algan15.plot, width = 7, height = 5)

#just raw data:
fishn15.seabirds.cond.algae %>%
   ggplot(aes(x = N.15_at_40m, y = n15, color = species, fill = species, group = species))+
  geom_point(alpha = .5)+
  stat_smooth(method = "lm")+
  theme_bw() 



```

#compare to lmer-----
```{r}
#compare to lmer----
fish_n15_algae_lmer<-lmer(n15~ N.15_at_40m*species + (1|site.name), 
                          data = fishn15.seabirds.cond.algae)
Anova(fish_n15_algae_lmer)
summary(fish_n15_algae_lmer)
#N.15_at_40m          1.5304  1   0.216050   
#species             14.9083  3   0.001897 **
#N.15_at_40m:species 14.8859  3   0.001917 **

emtrends(fish_n15_algae_lmer,  ~ species, var = "N.15_at_40m", lmer.df = "asymptotic")
#looks like Ab sept and Ac tri both are positive. Other two trending towards positive but overlaps 0

test(emtrends(fish_n15_algae_lmer, ~ species, var = "N.15_at_40m", adjust = "fdr", lmer.df = "asymptotic"))
# species                   N.15_at_40m.trend    SE  df z.ratio p.value
# Abudefduf septemfasciatus             1.651 0.638 Inf   2.590  0.0384
# Acanthurus triostegus                 0.630 0.632 Inf   0.997  0.6186
# Lutjanus fulvus                       0.173 0.636 Inf   0.271  0.7860
# Stegastes nigricans                   0.468 0.639 Inf   0.732  0.6186

test(emtrends(fish_n15_algae_lmer, pairwise~ species, var = "N.15_at_40m", adjust = "fdr", lmer.df = "asymptotic"))
# Abudefduf septemfasciatus - Acanthurus triostegus    1.021 0.400 Inf   2.553  0.0213
# Abudefduf septemfasciatus - Lutjanus fulvus          1.479 0.407 Inf   3.635  0.0017
# Abudefduf septemfasciatus - Stegastes nigricans      1.184 0.411 Inf   2.883  0.0118
# Acanthurus triostegus - Lutjanus fulvus              0.457 0.398 Inf   1.150  0.3751
# Acanthurus triostegus - Stegastes nigricans          0.162 0.402 Inf   0.404  0.6863
# Lutjanus fulvus - Stegastes nigricans               -0.295 0.408 Inf  -0.723  0.5637



(mylist2 <- list(
    N.15_at_40m = c(3.043333, 5.233333, 6.003333),
    species = c("Abudefduf septemfasciatus", "Acanthurus triostegus" ,   "Lutjanus fulvus"     ,     
 "Stegastes nigricans")
))
plot_dat_lmer2<-emmip(fish_n15_algae_lmer, species ~ N.15_at_40m, at = mylist2, CIs = TRUE, plotit=FALSE)
plot_dat_lmer2


fishn15.algan15.plot.lmer<-
fishn15.seabirds.cond.algae %>%
      mutate(species = fct_relevel(species, c("Acanthurus triostegus", "Stegastes nigricans", "Abudefduf septemfasciatus", "Lutjanus fulvus")))%>%
   ggplot(aes(x = N.15_at_40m, y = n15, color = species, fill = species, group = species))+
 # geom_point(alpha = .8)+
    geom_jitter(alpha = .7, width = .05, height = 0, size = 2.5)+
   geom_ribbon(data = plot_dat_lmer2, aes(x = N.15_at_40m, y = yvar, ymin = LCL, ymax=UCL, fill = species), alpha = .1, lwd=0)+
 geom_line(data = plot_dat_lmer2, aes(x = N.15_at_40m, y = yvar, color = species, group = species), lwd =1.5)+
  ylab(expression(Fish~delta^15~N))+
  xlab(expression(Algal~delta^15~N))+
  scale_fill_viridis_d(labels = c("Acanthurus triostegus (herbivore)", "Stegastes nigricans (herbivore)", "Abudefduf septemfasciatus (omnivore)", "Lutjanus fulvus (piscivore)"))+
  scale_color_viridis_d(labels = c("Acanthurus triostegus (herbivore)", "Stegastes nigricans (herbivore)", "Abudefduf septemfasciatus (omnivore)", "Lutjanus fulvus (piscivore)"))+
  labs(color = "", fill = "")+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.2,.85),
        legend.background = element_blank())
        #legent.key = element_rect) #,
        #legend.direction = "horizontal",
      #  legend.box.background = element_rect(colour = "black"))
fishn15.algan15.plot.lmer
#now crazy wide error bars....



fishn15.seabirds.cond.algae %>%
      mutate(species = fct_relevel(species, c("Acanthurus triostegus", "Stegastes nigricans", "Abudefduf septemfasciatus", "Lutjanus fulvus")))%>%
  dplyr::group_by(species, N.15_at_40m)%>%
  dplyr::summarize( mean_n15 = mean(n15), 
             n_n15 = length(n15), 
             se_n15 = sd(n15)/sqrt(n_n15))%>%
   ggplot(aes(x = N.15_at_40m, y = mean_n15, color = species, fill = species, group = species))+
 geom_point(alpha = 0.9, size = 5, aes(color = species)) +
  geom_errorbar(aes(ymin = (mean_n15-se_n15), ymax = (mean_n15+se_n15)), alpha = .5, width = 0.1)+
   #  geom_ribbon(data = plot_dat_lmer2, aes(x = N.15_at_40m, y = yvar, ymin = LCL, ymax=UCL, fill = species), alpha = .1, lwd=0)+
 geom_line(data = plot_dat_lmer2, aes(x = N.15_at_40m, y = yvar, color = species, group = species), lwd =1.5)+
  ylab(expression(Fish~delta^15~N))+
  xlab(expression(Algal~delta^15~N))+
  scale_fill_viridis_d(labels = c("Acanthurus triostegus (herbivore)", "Stegastes nigricans (herbivore)", "Abudefduf septemfasciatus (omnivore)", "Lutjanus fulvus (piscivore)"))+
  scale_color_viridis_d(labels = c("Acanthurus triostegus (herbivore)", "Stegastes nigricans (herbivore)", "Abudefduf septemfasciatus (omnivore)", "Lutjanus fulvus (piscivore)"))+
  labs(color = "", fill = "")+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.2,.85),
        legend.background = element_blank())
        #legent.key = element_rect) #,
        #legend.direction = "horizontal",
      #  legend.box.background = element_rect(colour = "black"))



##plot lines-----
fishn15.seabirds.cond.algae %>%
      mutate(species = fct_relevel(species, c("Acanthurus triostegus", "Stegastes nigricans", "Abudefduf septemfasciatus", "Lutjanus fulvus")))%>%
  dplyr::group_by(species, N.15_at_40m)%>%
  dplyr::summarize( mean_n15 = mean(n15), 
             n_n15 = length(n15), 
             se_n15 = sd(n15)/sqrt(n_n15))%>%
   ggplot(aes(x = N.15_at_40m, y = mean_n15, color = species, fill = species, group = species))+
 geom_point(alpha = 0.9, size = 5, aes(color = species)) +
  geom_errorbar(aes(ymin = (mean_n15-se_n15), ymax = (mean_n15+se_n15)), alpha = .5, width = 0.1)+
    geom_line(alpha = .6, lwd = 1.2)+
  ylab(expression(Fish~delta^15~N))+
  xlab(expression(Algal~delta^15~N))+
  scale_fill_viridis_d(labels = c("Acanthurus triostegus (herbivore)", "Stegastes nigricans (herbivore)", "Abudefduf septemfasciatus (omnivore)", "Lutjanus fulvus (piscivore)"))+
  scale_color_viridis_d(labels = c("Acanthurus triostegus (herbivore)", "Stegastes nigricans (herbivore)", "Abudefduf septemfasciatus (omnivore)", "Lutjanus fulvus (piscivore)"))+
  labs(color = "", fill = "")+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.2,.85),
        legend.background = element_blank())

```



#just log(algae n15) as x axis----
```{r}
#can use algae n15 at 40 m from shore as offshore, because this is present at all sites where we have fish
#because only one site per motu, random effects don't make sense, so run regular lm

fishn15.seabirds.cond.algae2<-
  fishn15.seabirds.cond.algae%>%
  mutate(log_n15_at_40m = log(N.15_at_40m))
fishn15.seabirds.cond.algae2

#n15----
fish_n15_algae_lm_log<-lm(n15~ log_n15_at_40m*species, 
                          data = fishn15.seabirds.cond.algae2)
summary(fish_n15_algae_lm_log)
anova(fish_n15_algae_lm_log)#everything significant
Anova(fish_n15_algae_lm_log)
plot(fish_n15_algae_lm_log) #okay
hist(resid(fish_n15_algae_lm_log))

##compare log and non-log model diagnostics----
plot(fish_n15_algae_lm) #okay
hist(resid(fish_n15_algae_lm))
plot(fish_n15_algae_lm_log) #okay
hist(resid(fish_n15_algae_lm_log))
#looks similar, maybe doesn't matter....



#look at emmeans:
emtrends(fish_n15_algae_lm_log,  ~ species, var = "log_n15_at_40m")
#looks like Ab sept and Ac tri both are positive. Other two trending towards positive but overlaps 0

test(emtrends(fish_n15_algae_lm_log, ~ species, var = "log_n15_at_40m", adjust = "fdr"))
 #Abudefduf septemfasciatus                7.377 1.37 57   5.396  <.0001
# Acanthurus triostegus                    3.041 1.31 57   2.321  0.0478
# Lutjanus fulvus                          0.729 1.36 57   0.535  0.5947
# Stegastes nigricans                      2.265 1.38 57   1.639  0.1423

test(emtrends(fish_n15_algae_lm_log, pairwise~ species, var = "log_n15_at_40m", adjust = "fdr"))
# Abudefduf septemfasciatus - Acanthurus triostegus    4.335 1.89 57   2.289  0.0516
# Abudefduf septemfasciatus - Lutjanus fulvus          6.648 1.93 57   3.444  0.0065
# Abudefduf septemfasciatus - Stegastes nigricans      5.112 1.94 57   2.630  0.0329
# Acanthurus triostegus - Lutjanus fulvus              2.312 1.89 57   1.223  0.3395
# Acanthurus triostegus - Stegastes nigricans          0.777 1.90 57   0.408  0.6849
# Lutjanus fulvus - Stegastes nigricans               -1.536 1.94 57  -0.791  0.5185


#Ab sept has strongest effect, all else similar. 


###lmer----
fish_n15_algae_lmer_log<-lmer(n15~ log_n15_at_40m*species + (1|site.name), 
                          data = fishn15.seabirds.cond.algae2)

test(emtrends(fish_n15_algae_lmer_log, ~ species, var = "log_n15_at_40m", adjust = "fdr", lmer.df = "asymptotic"))



# plot ---------
range(fishn15.seabirds.cond.algae2$log_n15_at_40m) #1.112953 1.792315
levels(fishn15.seabirds.cond.algae$species)
(mylist <- list(
    log_n15_at_40m = seq(1.11, 1.8, by = .001),
    species = c("Abudefduf septemfasciatus", "Acanthurus triostegus" ,   "Lutjanus fulvus"     ,     
 "Stegastes nigricans")
))

emmip(fish_n15_algae_lm_log, species ~ log_n15_at_40m, at = mylist, CIs = TRUE)


plot_dat3<-emmip(fish_n15_algae_lm_log, species ~ log_n15_at_40m, at = mylist, CIs = TRUE, plotit=FALSE, type = "response")
plot_dat3

fishn15.seabirds.cond.algae2 %>%
      mutate(species = fct_relevel(species, c("Acanthurus triostegus", "Stegastes nigricans", "Abudefduf septemfasciatus", "Lutjanus fulvus")))%>%
   ggplot(aes(x = exp(log_n15_at_40m), y = n15, color = species, fill = species, group = species))+
 # geom_point(alpha = .8)+
    geom_jitter(alpha = .7, width = .05, height = 0, size = 2.5)+
   geom_ribbon(data = plot_dat3, aes(x = exp(log_n15_at_40m), y = yvar, ymin = LCL, ymax=UCL, fill = species), alpha = .1, lwd=0)+
 geom_line(data = plot_dat3, aes(x = exp(log_n15_at_40m), y = yvar, color = species, group = species), lwd =1.5)+
  ylab(expression(Fish~delta^15~N))+
  xlab(expression(Algal~delta^15~N))+
  scale_fill_viridis_d(labels = c("Acanthurus triostegus (herbivore)", "Stegastes nigricans (herbivore)", "Abudefduf septemfasciatus (omnivore)", "Lutjanus fulvus (piscivore)"))+
  scale_color_viridis_d(labels = c("Acanthurus triostegus (herbivore)", "Stegastes nigricans (herbivore)", "Abudefduf septemfasciatus (omnivore)", "Lutjanus fulvus (piscivore)"))+
  labs(color = "", fill = "")+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.2,.85),
        legend.background = element_blank())

```

##log versus non-log model nearly identical, so just use linear...


#just log(fish n15) as 7 axis----
```{r}
#can use algae n15 at 40 m from shore as offshore, because this is present at all sites where we have fish
#because only one site per motu, random effects don't make sense, so run regular lm


#n15----
fish_n15_algae_lm_log_y<-lm(log(n15)~ N.15_at_40m*species, 
                          data = fishn15.seabirds.cond.algae)
summary(fish_n15_algae_lm_log_y)
anova(fish_n15_algae_lm_log_y)#everything significant
Anova(fish_n15_algae_lm_log_y)
plot(fish_n15_algae_lm_log_y) #okay
hist(resid(fish_n15_algae_lm_log_y))

##compare log and non-log model diagnostics----
plot(fish_n15_algae_lm) #okay
hist(resid(fish_n15_algae_lm))
plot(fish_n15_algae_lm_log) #okay
hist(resid(fish_n15_algae_lm_log))
#looks similar, maybe doesn't matter....



#look at emmeans:
emtrends(fish_n15_algae_lm_log_y,  ~ species, var = "N.15_at_40m")
#looks like Ab sept and Ac tri both are positive. Other two trending towards positive but overlaps 0

test(emtrends(fish_n15_algae_lm_log_y, ~ species, var = "N.15_at_40m", adjust = "fdr"))
# Abudefduf septemfasciatus            0.1825 0.0308 57   5.927  <.0001
# Acanthurus triostegus                0.0748 0.0295 57   2.540  0.0277
# Lutjanus fulvus                      0.0140 0.0304 57   0.461  0.6466
# Stegastes nigricans                  0.0568 0.0311 57   1.829  0.0969

test(emtrends(fish_n15_algae_lm_log_y, pairwise~ species, var = "N.15_at_40m", adjust = "fdr"))
#Abudefduf septemfasciatus - Acanthurus triostegus   0.1077 0.0426 57   2.527  0.0286
# Abudefduf septemfasciatus - Lutjanus fulvus         0.1685 0.0433 57   3.894  0.0016
# Abudefduf septemfasciatus - Stegastes nigricans     0.1257 0.0437 57   2.874  0.0171
# Acanthurus triostegus - Lutjanus fulvus             0.0608 0.0423 57   1.436  0.2345
# Acanthurus triostegus - Stegastes nigricans         0.0180 0.0428 57   0.421  0.6754
# Lutjanus fulvus - Stegastes nigricans              -0.0428 0.0435 57  -0.984  0.3949


#Ab sept has strongest effect, all else similar. 


###lmer----
fish_n15_algae_lmer_log_y<-lmer(log(n15)~ N.15_at_40m*species + (1|site.name), 
                          data = fishn15.seabirds.cond.algae)

test(emtrends(fish_n15_algae_lmer_log_y, ~ species, var = "N.15_at_40m", adjust = "fdr", lmer.df = "asymptotic"))
# Abudefduf septemfasciatus            0.1768 0.0631 Inf   2.803  0.0202
# Acanthurus triostegus                0.0713 0.0626 Inf   1.140  0.5086
# Lutjanus fulvus                      0.0173 0.0629 Inf   0.275  0.7834
 #Stegastes nigricans                  0.0535 0.0632 Inf   0.847  0.5295


# plot ---------
(mylist2 <- list(
    N.15_at_40m = c(3.043333, 5.233333, 6.003333),
    species = c("Abudefduf septemfasciatus", "Acanthurus triostegus" ,   "Lutjanus fulvus"     ,     
 "Stegastes nigricans")
))
plot_dat_lm_log2<-emmip(fish_n15_algae_lm_log_y, species ~ N.15_at_40m, at = mylist2, CIs = TRUE, plotit=FALSE)

fishn15.seabirds.cond.algae %>%
      mutate(species = fct_relevel(species, c("Acanthurus triostegus", "Stegastes nigricans", "Abudefduf septemfasciatus", "Lutjanus fulvus")))%>%
   ggplot(aes(x = N.15_at_40m, y = log(n15), color = species, fill = species, group = species))+
 # geom_point(alpha = .8)+
    geom_jitter(alpha = .7, width = .05, height = 0, size = 2.5)+
   geom_ribbon(data = plot_dat_lm_log2, aes(x = N.15_at_40m, y = yvar, ymin = LCL, ymax=UCL, fill = species), alpha = .1, lwd=0)+
 geom_line(data = plot_dat_lm_log2, aes(x = N.15_at_40m, y = yvar, color = species, group = species), lwd =1.5)+
  ylab(expression(Fish~delta^15~N))+
  xlab(expression(Algal~delta^15~N))+
  scale_fill_viridis_d(labels = c("Acanthurus triostegus (herbivore)", "Stegastes nigricans (herbivore)", "Abudefduf septemfasciatus (omnivore)", "Lutjanus fulvus (piscivore)"))+
  scale_color_viridis_d(labels = c("Acanthurus triostegus (herbivore)", "Stegastes nigricans (herbivore)", "Abudefduf septemfasciatus (omnivore)", "Lutjanus fulvus (piscivore)"))+
  labs(color = "", fill = "")+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.2,.85),
        legend.background = element_blank())
        #legent.key = element_rect) #,
        #legend.direction = "horizontal",
      #  legend.box.background = element_rect(colour = "black"))

fishn15.seabirds.cond.algae %>%
      mutate(species = fct_relevel(species, c("Acanthurus triostegus", "Stegastes nigricans", "Abudefduf septemfasciatus", "Lutjanus fulvus")))%>%
   ggplot(aes(x = N.15_at_40m, y = n15, color = species, fill = species, group = species))+
 # geom_point(alpha = .8)+
    geom_jitter(alpha = .7, width = .05, height = 0, size = 2.5)+
   geom_ribbon(data = plot_dat_lm_log2, aes(x = N.15_at_40m, y = exp(yvar), ymin = exp(LCL), ymax=exp(UCL), fill = species), alpha = .1, lwd=0)+
 geom_line(data = plot_dat_lm_log2, aes(x = N.15_at_40m, y = exp(yvar), color = species, group = species), lwd =1.5)+
  ylab(expression(Fish~delta^15~N))+
  xlab(expression(Algal~delta^15~N))+
  scale_fill_viridis_d(labels = c("Acanthurus triostegus (herbivore)", "Stegastes nigricans (herbivore)", "Abudefduf septemfasciatus (omnivore)", "Lutjanus fulvus (piscivore)"))+
  scale_color_viridis_d(labels = c("Acanthurus triostegus (herbivore)", "Stegastes nigricans (herbivore)", "Abudefduf septemfasciatus (omnivore)", "Lutjanus fulvus (piscivore)"))+
  labs(color = "", fill = "")+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.2,.85),
        legend.background = element_blank())
#doesn't look any different.....


```

#OR here because only 3 values anyway, just treat as factor (which is equivalent to rest status):--------
```{r}

fish_fact_lm<-lm(n15~ as.factor(N.15_at_40m)*species, 
                          data = fishn15.seabirds.cond.algae)
summary(fish_fact_lm)
anova(fish_fact_lm)#everything significant
Anova(fish_fact_lm)
plot(fish_fact_lm)

#as.factor(N.15_at_40m)          94.257  2 22.3758 9.016e-08 ***
#species                         30.632  3  4.8478  0.004704 ** 
#as.factor(N.15_at_40m):species  32.694  6  2.5871  0.028425 *  

#identical to rest stat, below, so can use those values


```


#OR here because only 3 values anyway, just treat as factor (which is equivalent to rest status):--------
```{r}

fishn15.seabirds.cond.algae.rest<-
  fishn15.seabirds.cond.algae%>%
 mutate(reststat = case_when(motu == "Aie" ~ "reference",
                              motu == "Reiono" ~ "recovering",
                              motu == "Rimatuu" ~ "unrestored"))%>%
   mutate(reststat = fct_relevel(reststat, "reference", "recovering", "unrestored")) %>% # relevel factor
  relocate(reststat, .after = motu)

fish_rest_lm<-lm(n15~ reststat*species, 
                          data = fishn15.seabirds.cond.algae.rest)
summary(fish_rest_lm)
anova(fish_rest_lm)#everything significant
Anova(fish_rest_lm)
plot(fish_rest_lm)

#reststat          94.257  2 22.3758 9.016e-08 ***
#species           30.632  3  4.8478  0.004704 ** 
#reststat:species  32.694  6  2.5871  0.028425 *  

#look at emmeans:
fish_rest_lm %>% 
  emmeans(~ reststat|species,
          type = "response") 


EMM_fish_n15 <- emmeans(fish_rest_lm, ~ species * reststat)

pairs(EMM_fish_n15, simple = "reststat", type = "response", adjust = "fdr")
#species = Abudefduf septemfasciatus:
# contrast                estimate    SE df t.ratio p.value
# reference - recovering   -0.4185 0.974 53  -0.430  0.6690
# reference - unrestored    4.4175 0.937 53   4.716  <.0001
# recovering - unrestored   4.8360 0.879 53   5.503  <.0001

#species = Acanthurus triostegus:
# contrast                estimate    SE df t.ratio p.value
# reference - recovering   -2.0300 0.879 53  -2.310  0.0372
# reference - unrestored    1.1217 0.879 53   1.276  0.2074
# recovering - unrestored   3.1517 0.838 53   3.761  0.0013

#species = Lutjanus fulvus:
# contrast                estimate    SE df t.ratio p.value
# reference - recovering   -1.3277 0.879 53  -1.511  0.2052
# reference - unrestored    0.0983 0.879 53   0.112  0.9113
# recovering - unrestored   1.4260 0.918 53   1.554  0.2052

#species = Stegastes nigricans:
# contrast                estimate    SE df t.ratio p.value
# reference - recovering   -0.9594 0.850 53  -1.129  0.2640
# reference - unrestored    1.0380 0.918 53   1.131  0.2640
# recovering - unrestored   1.9974 0.850 53   2.351  0.0675


emmeans(fish_n15_algae_lm_factor, list(pairwise ~ N.15_at_40m|species), adjust = "fdr")




```



#correlation test
```{r}
##also include n15 at various distances just to see if matches up:

fishn15.seabirds.cond.algae<-
  left_join(fishn15.seabirds.cond.r, 
            dplyr::select(algae_n15, c("site.name", "N.15_at_10m", "N.15_at_20m","N.15_at_30m","N.15_at_40m")), 
            by = "site.name")
fishn15.seabirds.cond.algae


##separate fish species----
#a little complicated bc different sample sizes for different species/site combos:
fishn15.seabirds.long<- 
  fishn15.seabirds.cond.algae %>%
    select(c(site.name, species, n15, breeding_biomass_kgha_side, N.15_at_10m, N.15_at_20m, N.15_at_30m, N.15_at_40m))%>%
  group_by(site.name, species) %>%
  mutate(Index=row_number())%>%
  relocate(Index, .before = site.name)
fishn15.seabirds.long

fishn15.seabirds.wide <- 
  pivot_wider(fishn15.seabirds.long,names_from = c("species"),values_from = c("n15"))
fishn15.seabirds.wide

corr_mat_fish_n15_sb_sp<-as.data.frame(fishn15.seabirds.wide[c(3,7:11)]) #only need to start with seabird biomass and offshore algae

cor(corr_mat_fish_n15_sb_sp, method = "spearman", use = "pairwise.complete.obs")
cor(corr_mat_fish_n15_sb_sp, method = "pearson", use = "pairwise.complete.obs")

##spearman:
cor.mat_sb_fishn15_byspp<- cor(fishn15.seabirds.wide[c(3,7,8,10,11,9)], method = "spearman", use = "pairwise.complete.obs")
cor.mat_sb_fishn15_byspp
corrplot(cor.mat_sb_fishn15_byspp, type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5)

##pearson:
cor.mat_sb_fishn15_byspp_pearson<- cor(fishn15.seabirds.wide[c(3,7,8,10,11,9)], method = "pearson", use = "pairwise.complete.obs")
cor.mat_sb_fishn15_byspp_pearson
corrplot(cor.mat_sb_fishn15_byspp_pearson, type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5)


##spearman, no algae:
cor.mat_sb_fishn15_byspp_no_algae<- cor(fishn15.seabirds.wide[c(3,8,10,11,9)], method = "spearman", use = "pairwise.complete.obs")
cor.mat_sb_fishn15_byspp_no_algae
corrplot(cor.mat_sb_fishn15_byspp_no_algae, type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5)

##save outputs----
#chunk 1
pdf(file = "../output/seabird-fishn15/seabirds_fishn15_corr_plot_by_sp_SPEARMAN.pdf")
corrplot(cor.mat_sb_fishn15_byspp, type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5)
dev.off()


#chunk 2
pdf(file = "../output/seabird-fishn15/seabirds_fishn15_corr_plot_by_sp_PEARSON.pdf")
corrplot(cor.mat_sb_fishn15_byspp_pearson, type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5)
dev.off()


##Oh wait, all a bit weird because of NAs, and correlations among fish species depend on order-----
cor(fishn15.seabirds.wide[c(3,8,10,11,9)], method = "spearman", use = "pairwise.complete.obs")
cor(fishn15.seabirds.wide[c(3,10)], method = "spearman", use = "pairwise.complete.obs")
cor(fishn15.seabirds.wide[c(3,11)], method = "spearman", use = "pairwise.complete.obs")
cor(fishn15.seabirds.wide[c(3,9)], method = "spearman", use = "pairwise.complete.obs")
cor(fishn15.seabirds.wide[c(3,8)], method = "spearman", use = "pairwise.complete.obs")
#okay, each species corr with seabird biomass matches*

#what if we arrange within each species/biomass level, n15 from high to low:
fishn15.seabirds.long2<- 
  fishn15.seabirds.cond.algae %>%
    dplyr::select(c(site.name, species, n15, breeding_biomass_kgha_side, N.15_at_10m, N.15_at_20m, N.15_at_30m, N.15_at_40m))%>%
    arrange(desc(n15))%>%
  group_by(site.name, species) %>%
  mutate(Index=row_number())%>%
  relocate(Index, .before = site.name)
fishn15.seabirds.long

fishn15.seabirds.wide2 <- 
  pivot_wider(fishn15.seabirds.long2,names_from = c("species"),values_from = c("n15"))
fishn15.seabirds.wide2

corrplot(cor(fishn15.seabirds.wide2[c(3,8,11,9, 10)], method = "spearman", use = "pairwise.complete.obs"), type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5)

cor(fishn15.seabirds.wide2[c(3,8,11,9, 10)], method = "spearman", use = "pairwise.complete.obs")
cor(fishn15.seabirds.wide[c(3,8,10,11,9)], method = "spearman", use = "pairwise.complete.obs")
#YUP, now really different cors***
#SO: can't show correlations across different fish species, unless we were to take a mean per site or something, but then we'd only have 3 points....


###save:----
cor.mat_sb_fishn15_byspp_no_algae<- cor(fishn15.seabirds.wide[c(3,8,10,11,9)], method = "spearman", use = "pairwise.complete.obs")

cor.mat_sb_fishn15_fish_by_sb_only<- cor(x = fishn15.seabirds.wide[c(3)], y =fishn15.seabirds.wide[c(8,10,11,9)], method = "spearman", use = "pairwise.complete.obs")



pdf(file = "../output/seabird-fishn15/seabirds_fishn15_corr_plot_by_sp_sb_onlySPEARMAN.pdf")
corrplot(cor.mat_sb_fishn15_fish_by_sb_only, type = "full",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5)
dev.off()


pdf(file = "../output/seabird-fishn15/seabirds_fishn15_corr_plot_by_sp_sb_onlySPEARMAN_LEGEND.pdf")
corrplot(cor.mat_sb_fishn15_byspp_no_algae, type = "full",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5, cl.pos = "b")
dev.off()


#try with seabirds and algae:
cor.mat_sb_fishn15_fish_by_sb_algae_only<- cor(x = fishn15.seabirds.wide[c(3,4,5,6,7)], y =fishn15.seabirds.wide[c(8,10,11,9)], method = "spearman", use = "pairwise.complete.obs")


```



#any way to combine algae and fish corr plots?? - NOPE


##simple boxplot of fish n15 veruss managemetn status
```{r}
fishn15_box<-
  fishn15.seabirds.cond.algae.rest%>%
        mutate(species = fct_relevel(species, c("Acanthurus triostegus", "Stegastes nigricans", "Abudefduf septemfasciatus", "Lutjanus fulvus")))%>%
  ggplot(aes(x = species, y = n15, fill = reststat))+
  geom_boxplot(alpha = .5, outlier.shape = NA)+ #
  geom_point(aes(color= reststat), position = position_dodge(.75), size = 2.5, alpha = .7)+
  ylab(expression(Fish~delta^15~N))+
  xlab("")+
  scale_fill_manual(values = c('#2F9D3E', '#F2BB05', '#CD1913'), labels = c('reference','recovering','unrestored'), name = "")+
  scale_colour_manual(values = c('#2F9D3E', '#F2BB05', '#CD1913'), labels = c('reference','recovering','unrestored'), name = "")+
      scale_x_discrete(labels = c("A. triostegus\n(herbivore)", "S. nigricans\n(herbivore)", "A. septemfasciatus\n(omnivore)", "L. fulvus\n(piscivore)"))+
   theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        axis.text = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        legend.position = c(.9, .85),
        legend.text = element_text(size = 12))
fishn15_box


ggsave("../output/seabird-fishn15/fishn15_box.jpg", plot = fishn15_box, width = 7, height = 5)

```






