---
title: "seabirds_vs_benthos"
author: "CEB"
date: '2023-09-29'
output: html_document
---

#load packages
```{r}
library(tidyverse)

library(lme4)
library(car)
library(jtools)

library(emmeans)

library(corrplot)

library(vegan)

library(cowplot)
library(ggtext)


```


#load data
```{r}
seabirds <- read.csv("../output/n15_seabirds_combined_no_iti.csv", strip.white = T, header = T)
load("../../fish_benthic_surveys/output/data/benthic_community_data.Rdata")

benthic_vid<-tet_video_div_comm_dat_w_cover
benthic_situ<-tet_insitu_div_comm_dat_w_cover

```




#start with video data-----------
#merge data
```{r}
benthic_vid

#make combined site name column in benthic data
benthic_vid_dat<-
  benthic_vid%>%
  mutate(motu = str_to_title(motu),
         protection = str_to_title(protection))%>%
  unite("site.name", c(motu, protection), sep = "_", remove = FALSE)

benthic_vid_dat

benthic.vid.seabirds<-left_join(benthic_vid_dat,
                            dplyr::select(seabirds, c("site.name", "breeding_biomass_kgha_side")), 
                                   by = "site.name")%>%
  mutate(site.name = as.factor(site.name))
benthic.vid.seabirds

```

##add algae n15 to data
```{r}
#add levels to data----
benthic.vid.seabirds.levels<-
  benthic.vid.seabirds%>%
    mutate(seabird_level = case_when(breeding_biomass_kgha_side<10 ~"low",
                                   breeding_biomass_kgha_side>10&breeding_biomass_kgha_side <200 ~"mid",
                                   breeding_biomass_kgha_side>200 ~"high"))%>%
  mutate(seabird_level = as.factor(seabird_level))%>%
  mutate(seabird_level = fct_relevel(seabird_level, "low", "mid", "high"))


#now add algae n15:----
algae_n15<-read.csv("../output/n15_seabirds_combined_no_iti.csv")
algae_n15


benthic.vid.seabirds.levels.algae<-left_join(benthic.vid.seabirds.levels, 
                                            dplyr::select(algae_n15, c("site.name", "N.15_at_10m",  "N.15_at_20m", "N.15_at_30m", "N.15_at_40m")),
                                            by = "site.name")

benthic.vid.seabirds.levels.algae


```


#Stacked bar plots - video----
```{r}

  
benthic.vid.seabirds.levels.algae%>%
 # dplyr::select(-c(total_percent_cover, transect_tape_percent_cover, cca_percent_cover, dead_coral_percent_cover, 
  #          other_fish_inverts_percent_cover))%>%
  pivot_longer(cols = ends_with("_percent_cover"),
                                          names_to = "group",
                                          values_to = "percent_cover")%>%
  mutate(group = str_remove(group, '_percent_cover'))%>%
  group_by(group, seabird_level)%>%
  summarize(mean_percent_cover = mean(percent_cover))



#limit stacked bar to major groups, and do by MOTU STATUS AND EXPOSURE : ----
  
# Plot it
benthic_stack_plot_video<-
benthic.vid.seabirds.levels.algae%>%
  dplyr::select(-c(total_percent_cover, transect_tape_percent_cover, cca_percent_cover, dead_coral_percent_cover, 
            other_fish_inverts_percent_cover))%>%
  pivot_longer(cols = ends_with("_percent_cover"),
                                          names_to = "group",
                                          values_to = "percent_cover")%>%
  mutate(group = str_remove(group, '_percent_cover'))%>%
  group_by(group, motu, wind.exposure)%>%
  summarize(mean_percent_cover = mean(percent_cover))%>%
  mutate(group = as.factor(group))%>%
  mutate(group = fct_relevel(group, c("hard_coral", "macroalgae", "pavement", "rubble", "sand")))%>%
 #  mutate(group = fct_relevel(group, c("sand", "rubble", "pavement", "macroalgae", "hard_coral")))%>%
  mutate(group = fct_recode(group, "hard coral" = "hard_coral"))%>%
  ggplot(aes(fill = group, y = mean_percent_cover, x = motu))+
  geom_bar(position = "stack", stat =  "identity")+
 # scale_fill_manual(values = spec) +
  scale_fill_brewer(palette = "Spectral")+ #, direction = -1
 scale_x_discrete(labels = c('reference','recovering','unrestored'))+
  xlab("")+
  ylab("Percent cover (video)")+
    theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
       #  axis.text.x = element_text(angle = 45, hjust = 1),
       strip.text = element_text(hjust = 0, size = 12))+
  facet_wrap(~wind.exposure, strip.position = "top",  
             labeller = labeller (wind.exposure = c("leeward" = "a. Leeward", "windward" = "b. Windward")))

benthic_stack_plot_video

```


##do NMDS with algae n15 as overlay
```{r}
#create data - all groups-----
tet_video_raw_meta_broad_sp_all<-
  benthic.vid.seabirds.levels.algae%>%
  ungroup()%>%
  dplyr::select(hard_coral_percent_cover:macroalgae_percent_cover)
tet_video_raw_meta_broad_sp_all

#create data - remove rare groups-----
colSums(tet_video_raw_meta_broad_sp_all)

#count 0s
tet_video_raw_meta_broad_sp_all %>% 
#  group_by(site.name) %>% 
  summarize(n = n(),
            across(-n, ~sum(is.na(.) | . == 0)))

#count >1%
tet_video_raw_meta_broad_sp_all %>% 
#  group_by(site.name) %>% 
  summarize(n = n(),
            across(-n, ~sum(is.na(.) | . >1)))
#only time fish/inverts > 1% = 1.09% (so still close to 1, and not > 1 at any one site***)


tet_video_raw_meta_broad_sp<-
  benthic.vid.seabirds.levels.algae%>%
  ungroup()%>%
  dplyr::select(hard_coral_percent_cover:macroalgae_percent_cover)%>%
  dplyr::select(-c(cca_percent_cover, dead_coral_percent_cover, 
            other_fish_inverts_percent_cover))
tet_video_raw_meta_broad_sp

#run nmds----
nmds_video<-metaMDS(tet_video_raw_meta_broad_sp, distance = "bray", trymax=200, k=2, autotransform = FALSE)
nmds_video
#2 axes stress = 0.06113269, so all good

plot(nmds_video)
scores(nmds_video, display="species")


#look at plot and centroids with ordfit

plot(nmds_video)
ord.fit.algae<-envfit(nmds_video~N.15_at_30m*protection, data = benthic.vid.seabirds.levels.algae, na.rm=TRUE)
ord.fit.algae 
plot(ord.fit.algae)
#not significant


#rotate by algae n15 so can more easily interpret----
nmds_video.rotate<-MDSrotate(nmds_video, benthic.vid.seabirds.levels.algae$N.15_at_30m)
nmds_video.rotate
plot(nmds_video.rotate)

ord.fit<-envfit(nmds_video.rotate~N.15_at_30m+protection, data = benthic.vid.seabirds.levels.algae, na.rm=TRUE)
ord.fit #p and r^2 are identical, just rotated so all with NMDS1 now.
plot(nmds_video.rotate)
plot(ord.fit)

##extract site/transect scores (non-rotated)----
video_spp.sc <- as.data.frame(scores(nmds_video, "species")) %>% #Using the scores function from vegan to extract the species scores and convert to a data.frame
  rownames_to_column(var="Species") %>% # create a column of species, from the rownames of species.scores
  mutate(Species = str_remove(Species, '_percent_cover'))%>%
  mutate(Species = str_replace(Species,  "_", " "))%>%
  mutate(Species= str_replace(Species,  "_", "/"))

video_spp.sc

video_site.sc <- scores(nmds_video, display = "sites", shrink = FALSE) 
video_site.sc

#merge site.sc with site and transect
nmds_video_site_scores<-
  bind_cols(benthic.vid.seabirds.levels.algae$site.name, benthic.vid.seabirds.levels.algae$transect,
                    as_tibble(video_site.sc))%>%
  rename('site.name' = '...1', 'transect' = '...2')
nmds_video_site_scores

#combine with other metadata:
benthic.vid.seabirds.levels.algae.w.nmds.norotate<-
 left_join(dplyr::select(benthic.vid.seabirds.levels.algae, -c("Distance_to_centroid", "NMDS1", "NMDS2")), #remove old nmds from before combined with seabird and algae data
           nmds_video_site_scores, 
             by = c("site.name", "transect"))
benthic.vid.seabirds.levels.algae.w.nmds.norotate


##extract site/transect scores (rotated)----
video_spp.sc.rotate <- as.data.frame(scores(nmds_video.rotate, "species")) %>% #Using the scores function from vegan to extract the species scores and convert
  rownames_to_column(var="Species") %>% # create a column of species, from the rownames of species.scores
  mutate(Species = str_remove(Species, '_percent_cover'))%>%
  mutate(Species = str_replace(Species,  "_", " "))%>%
  mutate(Species= str_replace(Species,  "_", "/"))
video_spp.sc.rotate

video_site.sc.rotate <- scores(nmds_video.rotate, display = "sites", shrink = FALSE) 
video_site.sc.rotate

#merge site.sc with site and transect
nmds_video_site_scores_rotate<-
  bind_cols(benthic.vid.seabirds.levels.algae$site.name, benthic.vid.seabirds.levels.algae$transect,
                    as_tibble(video_site.sc.rotate))%>%
  rename('site.name' = '...1', 'transect' = '...2')
nmds_video_site_scores_rotate


#combine with other metadata:
benthic.vid.seabirds.levels.algae.w.nmds<-
 left_join(benthic.vid.seabirds.levels.algae.w.nmds.norotate,
           nmds_video_site_scores_rotate, 
             by = c("site.name", "transect")) %>%
             rename("NMDS1" = "NMDS1.x",
                    "NMDS2" = "NMDS2.x",
                    "NMDS1.rotate" = "NMDS1.y",
                    "NMDS2.rotate" = "NMDS2.y")
benthic.vid.seabirds.levels.algae.w.nmds



#NMDS plots - rotated:----
#get hull data - seabird level:
##get arrows:
ord.fit.vid.rotate<-envfit(nmds_video.rotate ~ N.15_at_30m + wind.exposure, data = benthic.vid.seabirds.levels.algae.w.nmds, na.rm=TRUE)
ord.fit.vid.rotate #looks like seabird level is marginal

sb.scrs.vid.rotate <- as.data.frame(scores(ord.fit.vid.rotate, display = "vectors")* ordiArrowMul(ord.fit.vid.rotate))
sb.scrs.vid.rotate <- cbind(sb.scrs.vid.rotate, variable = rownames(sb.scrs.vid.rotate))
sb.scrs.vid.rotate<-
  sb.scrs.vid.rotate%>%
  mutate(variable2 = c("algal n15"))



cor(tet_video_raw_meta_broad_sp,
      nmds_video.rotate$points,
      use = "complete.obs",
      method = "spearman")
#                               MDS1        MDS2
#hard_coral_percent_cover -0.0200000 -0.67043478
#sand_percent_cover        0.8313043  0.58782609
#pavement_percent_cover   -0.4817391  0.76000000
#rubble_percent_cover     -0.2678843 -0.95151122
#macroalgae_percent_cover -0.6230151  0.01044159


cor(tet_video_raw_meta_broad_sp,
      nmds_video.rotate$points,
      use = "complete.obs",
      method = "pearson")
#                                MDS1       MDS2
#hard_coral_percent_cover -0.05603667 -0.7099176
#sand_percent_cover        0.93302043  0.4588428
#pavement_percent_cover   -0.50810972  0.7743748
#rubble_percent_cover     -0.33034600 -0.9252556
#macroalgae_percent_cover -0.60388932  0.1213062

benthic_video_nmds_plot_rotate_new_colours<-
ggplot() + 
  geom_point(data=benthic.vid.seabirds.levels.algae.w.nmds,aes(x=NMDS1.rotate,y=NMDS2.rotate,colour=N.15_at_30m, fill = N.15_at_30m, shape = wind.exposure), stat="identity", size=5, alpha = .9) +
  geom_segment(data = sb.scrs.vid.rotate,
               aes(x = 0, xend = NMDS1, y = 0, yend = NMDS2),
               arrow = arrow(length = unit(0.25, "cm"))) +
   geom_richtext(data = sb.scrs.vid.rotate, aes(x = NMDS1, y = NMDS2, label = paste0("algal \U03B4<sup>15</sup>N")),
                                       size = 3, fill = NA, label.colour = NA,  hjust = c(.75), vjust = -1)+
   # geom_text(data = sb.scrs.vid.rotate, aes(x = NMDS1, y = NMDS2, label = variable2),
    #        size = 3,  hjust = c(.75), vjust = -1)+
   # geom_text(data=video_spp.sc.rotate,aes(x=NMDS1,y=NMDS2,label=Species), alpha = .5, size = 3, hjust = .1) +  # add the species labels - 
  scale_fill_distiller(palette = "YlGnBu", direction = -1)+
    scale_colour_distiller(palette = "YlGnBu", direction = -1)+
  #scale_fill_viridis_c(option = "inferno", direction = -1)+
  #  scale_colour_viridis_c(option = "inferno", direction = -1)+
  labs(shape = "exposure", colour = expression(algal~delta^15~N), fill = expression(algal~delta^15~N))+
    scale_shape_manual(values = c(16, 17))+
  xlab("NMDS1")+
  ylab("NMDS2")+
theme_bw() + 
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.75,.78),
        legend.box = "horizontal",
        legend.background = element_blank()
     ) #   

benthic_video_nmds_plot_rotate_new_colours

#save plot
ggsave(benthic_video_nmds_plot_rotate_new_colours, file = "../output/seabird-benthic/benthic_video_nmds_plot_rotate_new_colours.jpg",
    width = 7, height = 5)


```


#repeat with in situ---------
#merge data
```{r}
benthic_situ

#make combined site name column in benthic data
benthic_situ_dat<-
  benthic_situ%>%
  mutate(protection = if_else(wind.exposure == "leeward", "Protected", "Exposed"))%>%
  mutate(motu = str_to_title(motu),
         protection = str_to_title(protection))%>%
  unite("site.name", c(motu, protection), sep = "_", remove = FALSE)%>%
  relocate(protection, .after = "wind.exposure")


benthic.situ.seabirds<-left_join(benthic_situ_dat,
                            dplyr::select(seabirds, c("site.name", "breeding_biomass_kgha_side")), 
                                   by = "site.name")%>%
  mutate(site.name = as.factor(site.name))
benthic.situ.seabirds

```



##add seabird levels and algae n15 to data
```{r}
#add levels to data----
benthic.situ.seabirds.levels<-
  benthic.situ.seabirds%>%
    mutate(seabird_level = case_when(breeding_biomass_kgha_side<10 ~"low",
                                   breeding_biomass_kgha_side>10&breeding_biomass_kgha_side <200 ~"mid",
                                   breeding_biomass_kgha_side>200 ~"high"))%>%
  mutate(seabird_level = as.factor(seabird_level))%>%
  mutate(seabird_level = fct_relevel(seabird_level, "low", "mid", "high"))


#now add algae n15:
algae_n15
benthic.situ.seabirds.levels.algae<-left_join(benthic.situ.seabirds.levels, 
                                            dplyr::select(algae_n15, c("site.name", "N.15_at_10m",  "N.15_at_20m", "N.15_at_30m", "N.15_at_40m")),
                                            by = "site.name")

benthic.situ.seabirds.levels.algae

```





#do stacked bar plot - in situ
```{r}

benthic.situ.seabirds.levels.algae%>%
 # dplyr::select(-c(total_percent_cover, transect_tape_percent_cover, cca_percent_cover, dead_coral_percent_cover, 
  #          other_fish_inverts_percent_cover))%>%
  pivot_longer(cols = ends_with("_percent_cover"),
                                          names_to = "group",
                                          values_to = "percent_cover")%>%
  mutate(group = str_remove(group, '_percent_cover'))%>%
  group_by(group, seabird_level)%>%
  dplyr::summarize(mean_percent_cover = mean(percent_cover))


#limit stacked bar to major groups, and do by MOTU STATUS AND EXPOSURE : ----
  
# Plot it
benthic_stack_plot_situ<-
benthic.situ.seabirds.levels.algae%>%
  dplyr::select(-c(cyano_percent_cover, other_invert_percent_cover))%>%
  pivot_longer(cols = ends_with("_percent_cover"),
                                          names_to = "group",
                                          values_to = "percent_cover")%>%
  mutate(group = str_remove(group, '_percent_cover'))%>%
  group_by(group, motu, wind.exposure)%>%
  summarize(mean_percent_cover = mean(percent_cover))%>%
  mutate(group = as.factor(group))%>%
  mutate(group = fct_relevel(group, c("coral", "macroalgae", "pavement", "rubble", "sand")))%>%
  ggplot(aes(fill = group, y = mean_percent_cover, x = motu))+
  geom_bar(position = "stack", stat =  "identity")+
 # scale_fill_manual(values = spec) +
  scale_fill_brewer(palette = "Spectral")+ #, direction = -1
 scale_x_discrete(labels = c('reference','recovering','unrestored'))+
  xlab("")+
  ylab("Percent cover (in situ)")+
    theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
      #   axis.text.x = element_text(angle = 45, hjust = 1),
       strip.text = element_text(hjust = 0, size = 12))+
  facet_wrap(~wind.exposure, strip.position = "top",  
             labeller = labeller (wind.exposure = c("leeward" = "c. Leeward", "windward" = "d. Windward")))

benthic_stack_plot_situ

```



##do NMDS with algae n15 as overlay - in situ-----
```{r}

#create data - all groups-----
tet_situ_raw_meta_broad_sp_all<-
  benthic.situ.seabirds.levels.algae%>%
  ungroup()%>%
  dplyr::select(coral_percent_cover:cyano_percent_cover)
tet_situ_raw_meta_broad_sp_all

#create data - remove rare groups-----
tet_situ_raw_meta_broad_sp<-
  benthic.situ.seabirds.levels.algae%>%
  ungroup()%>%
  dplyr::select(coral_percent_cover:cyano_percent_cover)%>%
  dplyr::select(-c(cyano_percent_cover, other_invert_percent_cover))
tet_situ_raw_meta_broad_sp

#run nmds----
nmds_situ<-metaMDS(tet_situ_raw_meta_broad_sp, distance = "bray", trymax=200, k=2, autotransform = FALSE)
nmds_situ
#2 axes stress = 0.07541151, so all good

plot(nmds_situ)
scores(nmds_situ, display="species")


#look at plot and centroids with ordfit
plot(nmds_situ)
ord.fit.level<-envfit(nmds_situ~seabird_level+protection, data = benthic.situ.seabirds.levels.algae, na.rm=TRUE)
ord.fit.level 
plot(ord.fit.level)

plot(nmds_situ)
ord.fit.algae<-envfit(nmds_situ~N.15_at_30m+protection, data = benthic.situ.seabirds.levels.algae, na.rm=TRUE)
ord.fit.algae 
plot(ord.fit.algae)



#rotate by algae n15 so can more easily interpret----
nmds_situ.rotate<-MDSrotate(nmds_situ, benthic.situ.seabirds.levels.algae$N.15_at_30m)
nmds_situ.rotate
plot(nmds_situ.rotate)

ord.fit<-envfit(nmds_situ.rotate~N.15_at_30m+protection, data = benthic.situ.seabirds.levels.algae, na.rm=TRUE)
ord.fit #p and r^2 are close, just rotated so all with NMDS1 now.


##extract site/transect scores (non-rotated)----
situ_spp.sc <- as.data.frame(scores(nmds_situ, "species")) %>% #Using the scores function from vegan to extract the species scores and convert to a data.frame
  rownames_to_column(var="Species") %>% # create a column of species, from the rownames of species.scores
  mutate(Species = str_remove(Species, '_percent_cover'))%>%
  mutate(Species = str_replace(Species,  "_", " "))%>%
  mutate(Species= str_replace(Species,  "_", "/"))

situ_spp.sc

situ_site.sc <- scores(nmds_situ, display = "sites", shrink = FALSE) 
situ_site.sc

#merge site.sc with site and transect
nmds_situ_site_scores<-
  bind_cols(benthic.situ.seabirds.levels.algae$site.name, benthic.situ.seabirds.levels.algae$transect,
                    as_tibble(situ_site.sc))%>%
  dplyr::rename('site.name' = '...1', 'transect' = '...2')
nmds_situ_site_scores

#combine with other metadata:
benthic.situ.seabirds.levels.algae.w.nmds.norotate<-
 left_join(dplyr::select(benthic.situ.seabirds.levels.algae, -c("Distance_to_centroid", "NMDS1", "NMDS2")), #remove old nmds from before combined with seabird and algae data
           nmds_situ_site_scores, 
             by = c("site.name", "transect"))
benthic.situ.seabirds.levels.algae.w.nmds.norotate


##extract site/transect scores (rotated)----
situ_spp.sc.rotate <- as.data.frame(scores(nmds_situ.rotate, "species")) %>% #Using the scores function from vegan to extract the species scores and convert
  rownames_to_column(var="Species") %>% # create a column of species, from the rownames of species.scores
  mutate(Species = str_remove(Species, '_percent_cover'))%>%
  mutate(Species = str_replace(Species,  "_", " "))%>%
  mutate(Species= str_replace(Species,  "_", "/"))%>%
  mutate(Species = fct_recode(Species,  "hard coral" = "coral")) #make match video name
situ_spp.sc.rotate

situ_site.sc.rotate <- scores(nmds_situ.rotate, display = "sites", shrink = FALSE) 
situ_site.sc.rotate

#merge site.sc with site and transect
nmds_situ_site_scores_rotate<-
  bind_cols(benthic.situ.seabirds.levels.algae$site.name, benthic.situ.seabirds.levels.algae$transect,
                    as_tibble(situ_site.sc.rotate))%>%
  dplyr::rename('site.name' = '...1', 'transect' = '...2')
nmds_situ_site_scores_rotate


#combine with other metadata:
benthic.situ.seabirds.levels.algae.w.nmds<-
 left_join(benthic.situ.seabirds.levels.algae.w.nmds.norotate,
           nmds_situ_site_scores_rotate, 
             by = c("site.name", "transect")) %>%
             dplyr::rename("NMDS1" = "NMDS1.x",
                    "NMDS2" = "NMDS2.x",
                    "NMDS1.rotate" = "NMDS1.y",
                    "NMDS2.rotate" = "NMDS2.y")
benthic.situ.seabirds.levels.algae.w.nmds


##check correlations between species and axes-----
cor(tet_situ_raw_meta_broad_sp,
      nmds_situ.rotate$points,
      use = "complete.obs",
      method = "pearson")
#                                MDS1        MDS2
#coral_percent_cover      -0.73119452 -0.05035492
#pavement_percent_cover    0.42068290 -0.90158400
#rubble_percent_cover     -0.83308345  0.45280192
#sand_percent_cover        0.53507287  0.77902515
#macroalgae_percent_cover  0.08999919 -0.69460130

cor(tet_situ_raw_meta_broad_sp,
      nmds_situ.rotate$points,
      use = "complete.obs",
      method = "spearman")
#coral_percent_cover      -0.78865381 -0.03362477
#pavement_percent_cover    0.38387891 -0.89629842
#rubble_percent_cover     -0.77861004  0.54367331
#sand_percent_cover        0.42247451  0.80444373
#macroalgae_percent_cover  0.08647449 -0.71939418

#NMDS plots - rotated:----

##get arrows: - UPDATED WITH CORRECT SCALING
ord.fit.situ.rotate<-envfit(nmds_situ.rotate ~ N.15_at_30m + wind.exposure, data = benthic.situ.seabirds.levels.algae.w.nmds, na.rm=TRUE)
ord.fit.situ.rotate #looks like seabird level is marginal

sb.scrs.situ.rotate <- as.data.frame(scores(ord.fit.situ.rotate, display = "vectors")* ordiArrowMul(ord.fit.situ.rotate))
sb.scrs.situ.rotate <- cbind(sb.scrs.situ.rotate, variable = rownames(sb.scrs.situ.rotate))
sb.scrs.situ.rotate<-
  sb.scrs.situ.rotate%>%
  mutate(variable2 = c("algal n15"))




benthic_situ_nmds_plot_rotate_new_colours<-
ggplot() + 
  geom_point(data=benthic.situ.seabirds.levels.algae.w.nmds,aes(x=NMDS1.rotate,y=NMDS2.rotate,colour=N.15_at_30m, fill = N.15_at_30m, shape = wind.exposure), stat="identity", size=5, alpha = .9) +
  geom_segment(data = sb.scrs.vid.rotate,
               aes(x = 0, xend = NMDS1, y = 0, yend = NMDS2),
               arrow = arrow(length = unit(0.25, "cm"))) +
  #  geom_text(data = sb.scrs.situ.rotate, aes(x = NMDS1, y = NMDS2, label = variable2),
  #          size = 3,  hjust = c(.75), vjust = -1)+
   geom_richtext(data = sb.scrs.vid.rotate, aes(x = NMDS1, y = .05, label = paste0("algal \U03B4<sup> 15</sup>N")),
                                       size = 3, fill = NA, label.colour = NA,  hjust = c(.75))+
   # geom_text(data=situ_spp.sc.rotate,aes(x=NMDS1,y=NMDS2,label=Species), alpha = .5, size = 3, hjust = .1) +  # add the species labels - 
  scale_fill_distiller(palette = "YlGnBu", direction = -1)+
    scale_colour_distiller(palette = "YlGnBu", direction = -1)+
  #scale_fill_viridis_c(option = "inferno", direction = -1)+
  #  scale_colour_viridis_c(option = "inferno", direction = -1)+
  labs(shape = "\n\n\n\n\nexposure", colour = expression(algal~delta^15~N), fill = expression(algal~delta^15~N))+
    scale_shape_manual(values = c(16, 17))+
      guides( col = guide_colorbar(order = 2),
      shape = guide_legend(order = 1),
      fill = guide_colorbar(order = 2))+
  xlab("NMDS1")+
  ylab("NMDS2")+
theme_bw() + 
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
           legend.position = c(.82, .25),
        legend.box = "horizontal",
        legend.background = element_blank()
     ) #   

benthic_situ_nmds_plot_rotate_new_colours

#save plot
ggsave(benthic_situ_nmds_plot_rotate_new_colours, file = "../output/seabird-benthic/benthic_situ_nmds_plot_rotate_new_colours.jpg",    width = 7, height = 5)

```



#COMBINE STACKED BAR PLOTS-----
```{r}
benthic_stack_plot_video
benthic_stack_plot_situ

benthic_stack_plots<-plot_grid(benthic_stack_plot_video, benthic_stack_plot_situ, nrow = 2)
benthic_stack_plots


#ggsave(benthic_stack_plots, file = "../output/seabird-benthic/benthic_stack_plots_by_reststat_exposure_COMBINED.jpg",
#   width = 7, height = 7)
#ggsave(benthic_stack_plots, file = "../output/seabird-benthic/benthic_stack_plots_by_reststat_exposure_COMBINED.pdf",
   # width = 7, height = 7)

```



#Run PERMANOVA----
```{r}


##video- remove rare groups-----
permanova_benthic_situ_n15_no_rare<-adonis2(tet_video_raw_meta_broad_sp ~ N.15_at_30m*protection,  data = benthic.vid.seabirds.levels.algae)
permanova_benthic_situ_n15_no_rare
#            Df SumOfSqs      R2      F Pr(>F)
#N.15_at_30m             1  0.00803 0.01174 0.2737  0.804  
#protection              1  0.01459 0.02134 0.4975  0.632  
#N.15_at_30m:protection  1  0.07463 0.10916 2.5452  0.088 .
#Residual               20  0.58646 0.85776                
#Total                  23  0.68371 1.00000                

#same results as with full community - marginal interaction


##situ- remove rare groups-----
permanova_benthic_situ_n15_no_rare<-adonis2(tet_situ_raw_meta_broad_sp ~ N.15_at_30m*protection,  data = benthic.vid.seabirds.levels.algae)
permanova_benthic_situ_n15_no_rare
#                      Df SumOfSqs      R2      F Pr(>F)
#N.15_at_30m             1  0.06943 0.06297 1.4717  0.238
#protection              1  0.04546 0.04123 0.9636  0.440
#N.15_at_30m:protection  1  0.04410 0.03999 0.9347  0.409
#Residual               20  0.94361 0.85580              
#Total                  23  1.10260 1.00000          

#same results as with full community - nothing significant


```


#Run LMMs using algae N15----------
#video and in situ:--------
#use beta distribution for major groups (hard coral) - because untransformed and log-transformed didn't work**
```{r}
transform01 <- function(x) {
  (x * (length(x) - 1) + 0.5) / (length(x))
}

div100<-function(x) {
  (x/100)
}

benthic.vid.seabirds.levels.algae.beta<-
  benthic.vid.seabirds.levels.algae %>%
  mutate_at(13:20, div100)%>%
  mutate_at(13:20, transform01)
benthic.vid.seabirds.levels.algae.beta


benthic.situ.seabirds.levels.algae.beta<-
    benthic.situ.seabirds.levels.algae %>%
  mutate_at(13:19, div100)%>%
  mutate_at(13:19, transform01)
benthic.situ.seabirds.levels.algae.beta

library(glmmTMB)


###video models -----------
hard_coral_vid.lmm.beta.n15<-glmmTMB(hard_coral_percent_cover~N.15_at_30m*wind.exposure + (1|site.name), family=beta_family(), data = benthic.vid.seabirds.levels.algae.beta)
summary(hard_coral_vid.lmm.beta.n15)
Anova(hard_coral_vid.lmm.beta.n15)
plot(resid(hard_coral_vid.lmm.beta.n15))
qqnorm(resid(hard_coral_vid.lmm.beta.n15))
#very significant interaction
#N.15_at_30m                0.0562  1   0.812629   
#wind.exposure              0.0023  1   0.961844   
#N.15_at_30m:wind.exposure 10.0606  1   0.001515 **


###in situ models
hard_coral_situ.lmm.beta.n15<-glmmTMB(coral_percent_cover~N.15_at_30m*wind.exposure + (1|site.name), family=beta_family(), data = benthic.situ.seabirds.levels.algae.beta)
summary(hard_coral_situ.lmm.beta.n15)
Anova(hard_coral_situ.lmm.beta.n15)
plot(resid(hard_coral_situ.lmm.beta.n15))
qqnorm(resid(hard_coral_situ.lmm.beta.n15))
#N.15_at_30m                6.2902  1    0.01214 *  
#wind.exposure              2.8025  1    0.09412 .  
#N.15_at_30m:wind.exposure 17.0591  1  3.624e-05 ***
#super sig interaction, and effect of n15


```

##emmeans-----
```{r}

#hard coral, video-----
test(emtrends(hard_coral_vid.lmm.beta.n15, ~ wind.exposure, var = "N.15_at_30m", adjust = "fdr"))
# wind.exposure N.15_at_30m.trend     SE  df z.ratio p.value
# leeward                 -0.0289 0.0664 Inf  -0.435  0.6638
# windward                 0.9756 0.3096 Inf   3.151  0.0033
#so on exposed side, sig positive effect of n15 on coral cover. 
#no effect on leeward side

test(emtrends(hard_coral_vid.lmm.beta.n15, pairwise~ wind.exposure, var = "N.15_at_30m", adjust = "fdr"))
#contrast           estimate    SE  df z.ratio p.value
# leeward - windward       -1 0.317 Inf  -3.172  0.0015


#hard coral, in situ-----
test(emtrends(hard_coral_situ.lmm.beta.n15, ~ wind.exposure, var = "N.15_at_30m", adjust = "fdr"))
# wind.exposure N.15_at_30m.trend     SE  df z.ratio p.value
# leeward                  -0.218 0.066 Inf  -3.311  0.0009
# windward                  1.114 0.315 Inf   3.530  0.0008
#so on exposed side, sig positive effect of n15 on coral cover. 
#and now sig negative effect on leeward side....weird.....

test(emtrends(hard_coral_situ.lmm.beta.n15, pairwise~ wind.exposure, var = "N.15_at_30m", adjust = "fdr"))
#contrast           estimate    SE  df z.ratio p.value
# leeward - windward    -1.33 0.322 Inf  -4.130  <.0001


```

#Plot - hard coral
```{r}
#in situ first-----
range(benthic.situ.seabirds.levels.algae.beta$N.15_at_30m, na.rm = T) #3.430000 6.993333

hc_s_plot_dat <- emmip(hard_coral_situ.lmm.beta.n15,  ~ N.15_at_30m|wind.exposure, at = list(N.15_at_30m = seq(3.43, 7.0, 0.01)), CIs = TRUE, plotit=FALSE, type = "response")

range(benthic.situ.seabirds.levels.algae.beta[benthic.situ.seabirds.levels.algae.beta$wind.exposure == "leeward",]$N.15_at_30m, na.rm = T) #3.430000 6.993333 - so whole range.
range(benthic.situ.seabirds.levels.algae.beta[benthic.situ.seabirds.levels.algae.beta$wind.exposure == "windward",]$N.15_at_30m, na.rm = T) #5.366667 6.226667 - ouch, very narrow range

hc_s_plot_dat <- 
  hc_s_plot_dat%>%
  mutate(wind.exposure = relevel(wind.exposure, "windward", "leeward"))

hc_s_plot_dat.protected<-
  hc_s_plot_dat%>%
  filter(wind.exposure == "leeward") #%>%
  #filter(N.15_at_30m>=2.73&N.15_at_30m<=10.66)

hc_s_plot_dat.exposed<-
  hc_s_plot_dat%>%
  filter(wind.exposure == "windward")%>%
  filter(N.15_at_30m>=5.36&N.15_at_30m<=6.3)

my_colors <- RColorBrewer::brewer.pal(3, "Dark2")[c(2, 1)]

##Plot hard coral, in situ according to N15 & exposure
coral_situ_plot<-
benthic.situ.seabirds.levels.algae.beta%>%
#  mutate(wind.exposure = relevel(wind.exposure, "windward", "leeward"))%>%
ggplot(aes(x = N.15_at_30m, y = coral_percent_cover, color = wind.exposure, 
                      fill = wind.exposure, group = wind.exposure))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(shape = wind.exposure))+
  geom_line(data = hc_s_plot_dat.protected, aes(x = N.15_at_30m, y = yvar))+
   geom_ribbon(data = hc_s_plot_dat.protected, aes(x = N.15_at_30m, y = yvar, ymin = LCL, ymax=UCL, fill = wind.exposure, color = wind.exposure), alpha = .2, linetype=0)+
    geom_line(data = hc_s_plot_dat.exposed, aes(x = N.15_at_30m, y = yvar))+
   geom_ribbon(data = hc_s_plot_dat.exposed, aes(x = N.15_at_30m, y = yvar, ymin = LCL, ymax=UCL, fill = wind.exposure, color = wind.exposure), alpha = .2, linetype=0)+
  ylab("Hard coral proportional cover") +
  xlab(expression(italic(delta)^15*N))+
 scale_fill_manual(values = my_colors)+
  scale_color_manual(values = my_colors) +
   scale_shape_manual(values = c(21, 24))+
  labs(shape = "exposure", color = "exposure", fill = "exposure")+
  theme_classic() +
  theme(legend.position = c(0.85, 0.82)) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))
coral_situ_plot


#ggsave("../output/seabird-benthic/hard_coral_in_situ_model_plot.jpg", plot = last_plot(), width = 7, height = 5)

##hard coral - video-----
hc_v_plot_dat <- emmip(hard_coral_vid.lmm.beta.n15,  ~ N.15_at_30m|wind.exposure, at = list(N.15_at_30m = seq(3.43, 7.0, 0.01)), CIs = TRUE, plotit=FALSE, type = "response")

range(benthic.situ.seabirds.levels.algae.beta[benthic.situ.seabirds.levels.algae.beta$wind.exposure == "leeward",]$N.15_at_30m, na.rm = T) #3.430000 6.993333 - so whole range.
range(benthic.situ.seabirds.levels.algae.beta[benthic.situ.seabirds.levels.algae.beta$wind.exposure == "windward",]$N.15_at_30m, na.rm = T) #5.366667 6.226667 - ouch, very narrow range

hc_v_plot_dat <- 
  hc_v_plot_dat%>%
  mutate(wind.exposure = relevel(wind.exposure, "windward", "leeward"))

hc_v_plot_dat.protected<-
  hc_v_plot_dat%>%
  filter(wind.exposure == "leeward") #%>%
  #filter(N.15_at_30m>=2.73&N.15_at_30m<=10.66)

hc_v_plot_dat.exposed<-
  hc_v_plot_dat%>%
  filter(wind.exposure == "windward")%>%
  filter(N.15_at_30m>=5.36&N.15_at_30m<=6.3)

my_colors <- RColorBrewer::brewer.pal(3, "Dark2")[c(2,1)]

##Plot hard coral, video according to N15 & exposure
hc_vid_plot<-
benthic.vid.seabirds.levels.algae.beta%>%
  mutate(wind.exposure = relevel(wind.exposure, "leeward", "windward"))%>%
ggplot(aes(x = N.15_at_30m, y = hard_coral_percent_cover, color = wind.exposure, 
                      fill = wind.exposure, group = wind.exposure))+
  #geom_point(stat = "summary", fun = "mean", alpha = 0.5, size  = 3) +
  geom_point(aes(shape = wind.exposure))+
  geom_line(data = hc_v_plot_dat.protected, aes(x = N.15_at_30m, y = yvar))+
   geom_ribbon(data = hc_v_plot_dat.protected, aes(x = N.15_at_30m, y = yvar, ymin = LCL, ymax=UCL, fill = wind.exposure, color = wind.exposure), alpha = .2, linetype=0)+
    geom_line(data = hc_v_plot_dat.exposed, aes(x = N.15_at_30m, y = yvar))+
   geom_ribbon(data = hc_v_plot_dat.exposed, aes(x = N.15_at_30m, y = yvar, ymin = LCL, ymax=UCL, fill = wind.exposure, color = wind.exposure), alpha = .2, linetype=0)+
  ylab("Hard coral proportional cover") +
  xlab(expression(italic(delta)^15*N))+
 scale_fill_manual(values = my_colors)+
  scale_color_manual(values = my_colors) +
   scale_shape_manual(values = c(21, 24))+
  labs(shape = "exposure", color = "exposure", fill = "exposure")+
  theme_classic() +
  theme(legend.position = c(0.85, 0.82)) +
  theme(panel.border = element_rect(color = "black", fill = NA, linetype = 1, linewidth = 0.5))
hc_vid_plot

#ggsave("../output/seabird-benthic/hard_coral_video_model_plot.jpg", plot = last_plot(), width = 7, height = 5)


```

##combine plots for supplement------
```{r}
hc_vid_plot
coral_situ_plot
benthic_situ_nmds_plot_rotate_new_colours

situ_supp_plots<-cowplot::plot_grid(hc_vid_plot, coral_situ_plot, benthic_situ_nmds_plot_rotate_new_colours, labels = "auto", label_fontface = "plain")
situ_supp_plots
#ggsave("../output/seabird-benthic/Supp_hc_situ_plots_combined.jpg", plot = situ_supp_plots, width = 10, height = 8)
#ggsave("../output/seabird-benthic/Supp_hc_situ_plots_combined.pdf", plot = situ_supp_plots, width = 10, height = 8)


```



#correlation analysis and plots for in situ versus video
```{r}

benthic.vid.seabirds.levels.algae
benthic.situ.seabirds.levels.algae


vid_for_cor<-
  benthic.vid.seabirds.levels.algae%>%
  dplyr::select(site.name, transect, hard_coral_percent_cover, macroalgae_percent_cover,
                sand_percent_cover,pavement_percent_cover,  rubble_percent_cover)%>%
  dplyr::rename_with(~str_replace(.,'_percent_cover', '_video'))
vid_for_cor

situ_for_cor<-
  benthic.situ.seabirds.levels.algae%>%
  dplyr::select(site.name, transect, coral_percent_cover, macroalgae_percent_cover, 
                sand_percent_cover, pavement_percent_cover, rubble_percent_cover)%>%
   dplyr::rename_with(~str_replace(.,'_percent_cover', '_insitu'))

vid_sit_for_corr<-
  full_join(vid_for_cor, situ_for_cor, by = c("site.name", "transect") )
vid_sit_for_corr



cor.mat_benthic<- cor(x = vid_sit_for_corr[c(3:7)], y =vid_sit_for_corr[c(8:12)], method = "spearman", use = "pairwise.complete.obs")
cor.mat_benthic

#cor.mat_benthic<- cor(vid_sit_for_corr[c(3:12)],  method = "spearman", use = "pairwise.complete.obs")


corrplot(cor.mat_benthic, type = "full",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5, cl.pos = "r", cl.ratio = .5)

#save plot:
pdf(file = "../output/seabird-benthic/corrplot_insitu_vs_vid.pdf")
corrplot(cor.mat_benthic, type = "full",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5, cl.pos = "r", cl.ratio = .5)
dev.off()


```

