---
title: "seabirds_vs_algae_N15"
author: "HEE"
date: "2024-06-04"
output: html_document
---

#Load libraries
```{r}
#library(plyr)
library(tidyverse)
library(corrplot)
library(nlme)
library(lme4)
library(car)
library(jtools)
library(emmeans)
library(sjPlot)

```


#Load combined seabird and algaeN15 data
```{r}

##Bring in seabird data
seabirds <- read.csv("../../seabird_data/outputs/seabird_dens_bio_focal_data.csv")

seabirds$site.name <- paste(seabirds$Motu, seabirds$Exposure, sep = "_") 

##bring in algae data
algae <- read.csv("../../algae_isotopes/data/Tetiaroa_Turbinaria_Transects_November_2021_compiledMarch2023.csv")
algae$Distance_to_shore <- as.factor(algae$Distance_to_shore)
algae$Side[algae$Side=="leeward"] <- "Protected"
algae$Side[algae$Side == "windward"] <- "Exposed"
names(algae)[names(algae) == 'Side'] <- 'Exposure'

algae

#bring in csv of combined data:----
algae.seabirds<-read.csv("../output/n15_seabirds_combined_no_iti.csv")

algae.seabirds<-
  algae.seabirds%>%
  dplyr::select(-X)

```


#Correlation plot - all seabird metrics versus algae n15 at 4 distances:
```{r}
cor.mat_sb__algae<- cor(x = algae.seabirds[c(3:18)], y =algae.seabirds[c(20:23)], method = "spearman", use = "pairwise.complete.obs")
cor.mat_sb__algae

corrplot(cor.mat_sb__algae, type = "full",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5, cl.pos = "r", cl.ratio = .5)

#save plot:
#pdf(file = "../output/seabird-algaen15/corrplot_allseabirds_vs_algaen15_spearman.pdf")
#corrplot(cor.mat_sb__algae, type = "full",
#         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5, cl.pos = "r", cl.ratio = .5)
#dev.off()

```


#Expand the data to include all algae data for running linear models. 
#add restoration status
```{r}
algae$site.name<-paste(algae$Motu, algae$Exposure, sep = "_") #seabirds$Exposure,

n15.all.seabirds <- merge(algae, seabirds[,-1], by = c("site.name"), all = TRUE, no.dups = TRUE)
names(n15.all.seabirds)[names(n15.all.seabirds) == 'Exposure.x'] <- 'Exposure'
names(n15.all.seabirds)[names(n15.all.seabirds) == 'Motu.x'] <- 'Motu'

n15.all.seabirds$reststat <- n15.all.seabirds$Motu

n15.all.seabirds$reststat[n15.all.seabirds$reststat == "Aie"] <- "reference"
n15.all.seabirds$reststat[n15.all.seabirds$reststat == "Reiono"] <- "recovering"
n15.all.seabirds$reststat[n15.all.seabirds$reststat == "Rimatuu"] <- "unrestored"

n15.all.seabirds <- 
  n15.all.seabirds %>% 
  mutate(reststat = fct_relevel(reststat, "reference", "recovering", "unrestored"))%>%
  mutate(Distance_to_shore_c = as.double(Distance_to_shore)*10) %>% #make distance to shore continuous
 relocate(Distance_to_shore_c, .after = Distance_to_shore) 

```


#Line plot by restoration status and exposure
```{r}

#with exposure:----
n15.line.sum.exp <- 
  n15.all.seabirds%>%
  dplyr::group_by(Distance_to_shore, reststat, Exposure)%>%
  dplyr::summarize( mean_n15 = mean(N15), 
             n_n15 = length(N15), 
             se_n15 = sd(N15)/sqrt(n_n15))%>%
  mutate(reststat = fct_relevel(reststat, "reference", "recovering", "unrestored"))


N15.lineplot.exposure <- 
  n15.line.sum.exp%>%
  mutate(Protection = case_when(Exposure == "Protected" ~ "Leeward",
                                Exposure == "Exposed" ~ "Windward"))%>%
  mutate(Protection = as.factor (Protection))%>%
  mutate(Protection = fct_relevel(Protection, "Leeward", "Windward"))%>%
  ggplot(aes(x = Distance_to_shore, y = mean_n15, fill = reststat, color = reststat, group = reststat) )+
  #geom_boxplot(alpha = 0.6) +
  geom_point(alpha = 0.9, size = 5, aes(color = reststat, shape = Protection)) +
  geom_errorbar(aes(ymin = (mean_n15-se_n15), ymax = (mean_n15+se_n15)), alpha = .5, width = 0.1)+
  geom_line(alpha = .6, lwd = 1.2)+
  ylab(expression(Algal~italic(delta)^15*N)) +
  scale_colour_manual(values = c( "unrestored" = "#CD1913", "recovering" = "#F2BB05", "reference" ="#2F9D3E")) +
  xlab("Distance to Shore (m)")+
  guides(shape = "none")+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
        legend.position = c(.88, .85),
        strip.text = element_text(hjust = 0, size = 12))+
  facet_wrap(~Protection)

N15.lineplot.exposure

#save panel:
#ggsave(N15.lineplot.exposure, file = "../output/seabird-algaen15/N15_lineplot_exposure.jpg",
#    width = 7, height = 5)

#ggsave(N15.lineplot.exposure, file = "../output/seabird-algaen15/N15_lineplot_exposure.pdf",
 #   width = 7, height = 5)

```


#N15 restoration status models
```{r}
#run lmm, including 2-way interactions we're interested in: -----
mod.lmer.rest <- lmer(N15 ~ reststat*Distance_to_shore + reststat*Exposure +(1|site.name), data = n15.all.seabirds)

hist(resid(mod.lmer.rest))
plot(mod.lmer.rest) 
qqnorm(resid(mod.lmer.rest))
#diagnostics look good

#test statistics
summary(mod.lmer.rest)
Anova(mod.lmer.rest)
#Response: N15
#                             Chisq Df Pr(>Chisq)    
#reststat                   45.4162  2  1.374e-10 ***
#Distance_to_shore          60.0721  3  5.673e-13 ***
#Exposure                    0.1411  1   0.707207    
#reststat:Distance_to_shore 18.1174  6   0.005945 ** 
#reststat:Exposure          62.2489  2  3.040e-14 ***


```


#post-hoc tests on rest status*exposure
```{r}

#extract pair-wise differences:
emmeans(mod.lmer.rest, list(pairwise ~ reststat|Distance_to_shore|Exposure), type = "response", adjust = "fdr", lmer.df = "asymptotic")
###On exposed side, no differences between restoration status********
##One protected side, all distances different between recovering/reference and unrestored*******


#$`pairwise differences of reststat | Distance_to_shore, Exposure`
#Distance_to_shore = 10, Exposure = Exposed:
# 3                       estimate    SE    df t.ratio p.value
# reference - recovering     0.541 0.588 131.3   0.919  0.3596
# reference - unrestored     1.118 0.588 131.3   1.901  0.1783
# recovering - unrestored    0.578 0.576 138.3   1.003  0.3596

#Distance_to_shore = 20, Exposure = Exposed:
# 3                       estimate    SE    df t.ratio p.value
# reference - recovering     0.780 0.583 134.0   1.338  0.4699
# reference - unrestored     0.198 0.583 134.0   0.340  0.7348
# recovering - unrestored   -0.583 0.576 138.3  -1.012  0.4699

#Distance_to_shore = 30, Exposure = Exposed:
# 3                       estimate    SE    df t.ratio p.value
# reference - recovering     0.697 0.583 134.0   1.196  0.3510
# reference - unrestored    -0.304 0.583 134.0  -0.521  0.6034
# recovering - unrestored   -1.001 0.576 138.3  -1.739  0.2528

#Distance_to_shore = 40, Exposure = Exposed:
# 3                       estimate    SE    df t.ratio p.value
# reference - recovering     0.459 0.714  93.6   0.643  0.5217
# reference - unrestored    -1.052 0.714  93.6  -1.473  0.2163
# recovering - unrestored   -1.511 0.576 138.3  -2.625  0.0289

#Distance_to_shore = 10, Exposure = Protected:
# 3                       estimate    SE    df t.ratio p.value
# reference - recovering    -0.487 0.608 122.3  -0.801  0.4246
# reference - unrestored     4.946 0.608 122.3   8.138  <.0001
# recovering - unrestored    5.433 0.576 138.3   9.439  <.0001

#Distance_to_shore = 20, Exposure = Protected:
# 3                       estimate    SE    df t.ratio p.value
# reference - recovering    -0.247 0.583 134.0  -0.424  0.6724
# reference - unrestored     4.025 0.583 134.0   6.903  <.0001
# recovering - unrestored    4.272 0.576 138.3   7.424  <.0001

#Distance_to_shore = 30, Exposure = Protected:
# 3                       estimate    SE    df t.ratio p.value
# reference - recovering    -0.330 0.583 134.0  -0.567  0.5718
# reference - unrestored     3.524 0.583 134.0   6.043  <.0001
# recovering - unrestored    3.854 0.576 138.3   6.697  <.0001

#Distance_to_shore = 40, Exposure = Protected:
# 3                       estimate    SE    df t.ratio p.value
 #reference - recovering    -0.568 0.627 115.0  -0.907  0.3664
# reference - unrestored     2.776 0.627 115.0   4.429  <.0001
# recovering - unrestored    3.344 0.576 138.3   5.811  <.0001

#Degrees-of-freedom method: kenward-roger 
#P value adjustment: fdr method for 3 tests 

#repeat with different df (asymptotic):
emmeans(mod.lmer.rest, list(pairwise ~ reststat|Distance_to_shore|Exposure), type = "response", adjust = "fdr",
        lmer.df = "asymptotic")
#nearly identical results!
#Distance_to_shore = 10, Exposure = Exposed:
# 3                       estimate    SE  df z.ratio p.value
# reference - recovering     0.541 0.588 Inf   0.919  0.3579
# reference - unrestored     1.118 0.588 Inf   1.901  0.1718
# recovering - unrestored    0.578 0.576 Inf   1.003  0.3579

#Distance_to_shore = 20, Exposure = Exposed:
# 3                       estimate    SE  df z.ratio p.value
# reference - recovering     0.780 0.583 Inf   1.338  0.4672
# reference - unrestored     0.198 0.583 Inf   0.340  0.7342
# recovering - unrestored   -0.583 0.576 Inf  -1.012  0.4672

# Distance_to_shore = 30, Exposure = Exposed:
# 3                       estimate    SE  df z.ratio p.value
# reference - recovering     0.697 0.583 Inf   1.196  0.3478
# reference - unrestored    -0.304 0.583 Inf  -0.521  0.6025
# recovering - unrestored   -1.001 0.576 Inf  -1.739  0.2461

#Distance_to_shore = 40, Exposure = Exposed:
# 3                       estimate    SE  df z.ratio p.value
# reference - recovering     0.459 0.714 Inf   0.643  0.5201
# reference - unrestored    -1.052 0.714 Inf  -1.473  0.2113
# recovering - unrestored   -1.511 0.576 Inf  -2.625  0.0260

#Distance_to_shore = 10, Exposure = Protected:
# 3                       estimate    SE  df z.ratio p.value
# reference - recovering    -0.487 0.608 Inf  -0.801  0.4230
# reference - unrestored     4.946 0.608 Inf   8.138  <.0001
# recovering - unrestored    5.433 0.576 Inf   9.439  <.0001

#Distance_to_shore = 20, Exposure = Protected:
# 3                       estimate    SE  df z.ratio p.value
# reference - recovering    -0.247 0.583 Inf  -0.424  0.6717
# reference - unrestored     4.025 0.583 Inf   6.903  <.0001
# recovering - unrestored    4.272 0.576 Inf   7.424  <.0001

#Distance_to_shore = 30, Exposure = Protected:
# 3                       estimate    SE  df z.ratio p.value
# reference - recovering    -0.330 0.583 Inf  -0.567  0.5709
# reference - unrestored     3.524 0.583 Inf   6.043  <.0001
# recovering - unrestored    3.854 0.576 Inf   6.697  <.0001

#Distance_to_shore = 40, Exposure = Protected:
# 3                       estimate    SE  df z.ratio p.value
# reference - recovering    -0.568 0.627 Inf  -0.907  0.3645
# reference - unrestored     2.776 0.627 Inf   4.429  <.0001
# recovering - unrestored    3.344 0.576 Inf   5.811  <.0001



emmeans(mod.lmer.rest, list(pairwise ~ Distance_to_shore|Exposure|reststat), type = "response", adjust = "fdr")
#$`pairwise differences of Distance_to_shore | reststat, Exposure`
#reststat = reference, Exposure = Exposed:
# 3                                         estimate    SE df t.ratio p.value
# Distance_to_shore10 - Distance_to_shore20   1.2086 0.426 53   2.836  0.0101
# Distance_to_shore10 - Distance_to_shore30   1.8886 0.426 53   4.431  0.0001
# Distance_to_shore10 - Distance_to_shore40   2.6881 0.552 53   4.870  0.0001
# Distance_to_shore20 - Distance_to_shore30   0.6800 0.405 53   1.679  0.1189
 #Distance_to_shore20 - Distance_to_shore40   1.4795 0.525 53   2.819  0.0101
# Distance_to_shore30 - Distance_to_shore40   0.7995 0.525 53   1.524  0.1336

#reststat = recovering, Exposure = Exposed:
# 3                                         estimate    SE df t.ratio p.value
# Distance_to_shore10 - Distance_to_shore20   1.4483 0.405 53   3.576  0.0015
# Distance_to_shore10 - Distance_to_shore30   2.0450 0.405 53   5.049  <.0001
# Distance_to_shore10 - Distance_to_shore40   2.6067 0.405 53   6.436  <.0001
# Distance_to_shore20 - Distance_to_shore30   0.5967 0.405 53   1.473  0.1713
 #Distance_to_shore20 - Distance_to_shore40   1.1583 0.405 53   2.860  0.0091
# Distance_to_shore30 - Distance_to_shore40   0.5617 0.405 53   1.387  0.1713

#reststat = unrestored, Exposure = Exposed:
# 3                                         estimate    SE df t.ratio p.value
# Distance_to_shore10 - Distance_to_shore20   0.2883 0.405 53   0.712  0.7938
# Distance_to_shore10 - Distance_to_shore30   0.4667 0.405 53   1.152  0.7633
# Distance_to_shore10 - Distance_to_shore40   0.5183 0.405 53   1.280  0.7633
# Distance_to_shore20 - Distance_to_shore30   0.1783 0.405 53   0.440  0.7938
# Distance_to_shore20 - Distance_to_shore40   0.2300 0.405 53   0.568  0.7938
# Distance_to_shore30 - Distance_to_shore40   0.0517 0.405 53   0.128  0.8990

#reststat = reference, Exposure = Protected:
# 3                                         estimate    SE df t.ratio p.value
# Distance_to_shore10 - Distance_to_shore20   1.2086 0.426 53   2.836  0.0101
# Distance_to_shore10 - Distance_to_shore30   1.8886 0.426 53   4.431  0.0001
# Distance_to_shore10 - Distance_to_shore40   2.6881 0.552 53   4.870  0.0001
# Distance_to_shore20 - Distance_to_shore30   0.6800 0.405 53   1.679  0.1189
# Distance_to_shore20 - Distance_to_shore40   1.4795 0.525 53   2.819  0.0101
 #Distance_to_shore30 - Distance_to_shore40   0.7995 0.525 53   1.524  0.1336

#reststat = recovering, Exposure = Protected:
# 3                                         estimate    SE df t.ratio p.value
# Distance_to_shore10 - Distance_to_shore20   1.4483 0.405 53   3.576  0.0015
# Distance_to_shore10 - Distance_to_shore30   2.0450 0.405 53   5.049  <.0001
# Distance_to_shore10 - Distance_to_shore40   2.6067 0.405 53   6.436  <.0001
# Distance_to_shore20 - Distance_to_shore30   0.5967 0.405 53   1.473  0.1713
# Distance_to_shore20 - Distance_to_shore40   1.1583 0.405 53   2.860  0.0091
# Distance_to_shore30 - Distance_to_shore40   0.5617 0.405 53   1.387  0.1713

#reststat = unrestored, Exposure = Protected:
# 3                                         estimate    SE df t.ratio p.value
# Distance_to_shore10 - Distance_to_shore20   0.2883 0.405 53   0.712  0.7938
# Distance_to_shore10 - Distance_to_shore30   0.4667 0.405 53   1.152  0.7633
# Distance_to_shore10 - Distance_to_shore40   0.5183 0.405 53   1.280  0.7633
# Distance_to_shore20 - Distance_to_shore30   0.1783 0.405 53   0.440  0.7938
# Distance_to_shore20 - Distance_to_shore40   0.2300 0.405 53   0.568  0.7938
# Distance_to_shore30 - Distance_to_shore40   0.0517 0.405 53   0.128  0.8990

#Degrees-of-freedom method: kenward-roger 
#P value adjustment: fdr method for 6 tests 


###Offshore gradient in n15 around BOTH exposed and protected sides for recovering and reference, but no offshore gradient on either side for unrestored (BUT NO INTERACTION BETWEEN SIDE*DISTANCE)*****

#repeat with asymptotic df:
emmeans(mod.lmer.rest, list(pairwise ~ Distance_to_shore|reststat|Exposure), type = "response", adjust = "fdr",
        lmer.df = "asymptotic")
#no change to results***
#$`pairwise differences of Distance_to_shore | reststat, Exposure`
#reststat = reference, Exposure = Exposed:
# 3                                         estimate    SE  df z.ratio p.value
# Distance_to_shore10 - Distance_to_shore20   1.2086 0.426 Inf   2.836  0.0072
# Distance_to_shore10 - Distance_to_shore30   1.8886 0.426 Inf   4.431  <.0001
# Distance_to_shore10 - Distance_to_shore40   2.6881 0.552 Inf   4.870  <.0001
# Distance_to_shore20 - Distance_to_shore30   0.6800 0.405 Inf   1.679  0.1118
# Distance_to_shore20 - Distance_to_shore40   1.4795 0.525 Inf   2.819  0.0072
# Distance_to_shore30 - Distance_to_shore40   0.7995 0.525 Inf   1.524  0.1276

#reststat = recovering, Exposure = Exposed:
# 3                                         estimate    SE  df z.ratio p.value
# Distance_to_shore10 - Distance_to_shore20   1.4483 0.405 Inf   3.576  0.0007
# Distance_to_shore10 - Distance_to_shore30   2.0450 0.405 Inf   5.049  <.0001
# Distance_to_shore10 - Distance_to_shore40   2.6067 0.405 Inf   6.436  <.0001
# Distance_to_shore20 - Distance_to_shore30   0.5967 0.405 Inf   1.473  0.1655
# Distance_to_shore20 - Distance_to_shore40   1.1583 0.405 Inf   2.860  0.0064
# Distance_to_shore30 - Distance_to_shore40   0.5617 0.405 Inf   1.387  0.1655

#reststat = unrestored, Exposure = Exposed:
# 3                                         estimate    SE  df z.ratio p.value
# Distance_to_shore10 - Distance_to_shore20   0.2883 0.405 Inf   0.712  0.7917
# Distance_to_shore10 - Distance_to_shore30   0.4667 0.405 Inf   1.152  0.7478
# Distance_to_shore10 - Distance_to_shore40   0.5183 0.405 Inf   1.280  0.7478
# Distance_to_shore20 - Distance_to_shore30   0.1783 0.405 Inf   0.440  0.7917
# Distance_to_shore20 - Distance_to_shore40   0.2300 0.405 Inf   0.568  0.7917
# Distance_to_shore30 - Distance_to_shore40   0.0517 0.405 Inf   0.128  0.8985


##
emmeans(mod.lmer.rest, list(pairwise ~ Exposure|reststat|Distance_to_shore), type = "response", adjust = "fdr",
        lmer.df = "asymptotic")
#reststat = reference, Distance_to_shore = 10:
# 3                   estimate    SE  df z.ratio p.value
# Exposed - Protected   -0.879 0.493 Inf  -1.782  0.0748

#reststat = recovering, Distance_to_shore = 10:
# 3                   estimate    SE  df z.ratio p.value
# Exposed - Protected   -1.907 0.456 Inf  -4.179  <.0001

#reststat = unrestored, Distance_to_shore = 10:
# 3                   estimate    SE  df z.ratio p.value
# Exposed - Protected    2.948 0.456 Inf   6.462  <.0001


##and same for every distance to shore.....so equivalent to this:
emmeans(mod.lmer.rest, list(pairwise ~ Exposure|reststat), type = "response", adjust = "fdr",
        lmer.df = "asymptotic")
#SO: reference and recovering have higher n15 values at each distance on protected side (marginal for reference)
#whereas unrestored has higher n15 values on exposed side. 

```



#Run models with seabird breeding biomass as predictor----
```{r}

#log-transform:
n15.all.seabirds2<-
  n15.all.seabirds%>%
  mutate(log_breeding_biomass_kgha_side = log(breeding_biomass_kgha_side))

#compared log versus non-log, log is better:
mod.lmer.breeding.log <- lmer(N15 ~ log_breeding_biomass_kgha_side*Distance_to_shore + log_breeding_biomass_kgha_side*Exposure + (1|site.name), n15.all.seabirds2)
plot(mod.lmer.breeding.log)
qqnorm(resid(mod.lmer.breeding.log))
hist(resid(mod.lmer.breeding.log))



#test statistics----
summary(mod.lmer.breeding.log)
Anova(mod.lmer.breeding.log)
#log_breeding_biomass_kgha_side                     20.6547  1  5.500e-06 ***
#Distance_to_shore                                  68.2012  3  1.036e-14 ***
#Exposure                                           0.5241  1  0.4691040    
#log_breeding_biomass_kgha_side:Distance_to_shore   23.9758  3  2.527e-05 ***
#log_breeding_biomass_kgha_side:Exposure            11.2675  1  0.0007888 ***



#look at emmeans:---
emtrends(mod.lmer.breeding.log,  ~ Distance_to_shore|Exposure, var = "log_breeding_biomass_kgha_side", adjust = "fdr", lmer.df = "asymptotic")
#looks like positive trends on protected side, negative on exposed side. larger effects at closer distances

test(emtrends(mod.lmer.breeding.log, ~ Distance_to_shore|Exposure, var = "log_breeding_biomass_kgha_side",  adjust = "fdr", type = "response"))
test(emtrends(mod.lmer.breeding.log, ~ Distance_to_shore|Exposure, var = "log_breeding_biomass_kgha_side",  adjust = "fdr", type = "response", lmer.df = "asymptotic"))
#all protected side p-values significant, nothing significant on exposed side.
#same results/conclusions regardless of df used, just smaller p-values with asymptotic:

#Exposure = Exposed:
# Distance_to_shore log_breeding_biomass_kgha_side.trend    SE  df z.ratio p.value
# 10                                               0.271 0.288 Inf   0.939  0.5459
# 20                                              -0.057 0.287 Inf  -0.198  0.8429
# 30                                              -0.237 0.287 Inf  -0.825  0.5459
# 40                                              -0.395 0.290 Inf  -1.361  0.5459

#Exposure = Protected:
# Distance_to_shore log_breeding_biomass_kgha_side.trend    SE  df z.ratio p.value
# 10                                               1.366 0.197 Inf   6.932  <.0001
# 20                                               1.038 0.195 Inf   5.334  <.0001
# 30                                               0.858 0.195 Inf   4.409  <.0001
# 40                                               0.701 0.195 Inf   3.588  0.0003
#Degrees-of-freedom method: asymptotic 
#P value adjustment: fdr method for 4 tests 

#back transform estimates: because x log-transformed, need to raise trend log(2^(coef)) so each doubling of seabird biomass is associated with a change in mean algal n15 of log(2^coef) units
log(2^1.366) #0.946839
log(2^1.038) #0.7194868
log(2^0.858) #0.5947203
log(2^0.701) #0.4858962


range(n15.all.seabirds2$log_breeding_biomass_kgha_side)
 mean(n15.all.seabirds2$log_breeding_biomass_kgha_side)
emmeans(mod.lmer.breeding.log, list(pairwise ~ log_breeding_biomass_kgha_side|Distance_to_shore|Exposure), type = "response", adjust = "fdr", lmer.df = "asymptotic",
         at = list(log_breeding_biomass_kgha_side = c(1.68, 4.09, 5.94)))
#yup, all different on protected side but not exposed side. 

emmeans(mod.lmer.breeding.log, list(pairwise ~ Distance_to_shore|log_breeding_biomass_kgha_side), type = "response", adjust = "fdr", lmer.df = "asymptotic",
         at = list(log_breeding_biomass_kgha_side = c(1.68, 4.09, 5.94)))
#at the lowest seabird biomass, there was no effect of distance to shore. At mid and high biomass, there is decline with distance to shore.

```


##Check if seabird biomass on Iti explains exposed side of Rimatuu patterns-----
```{r}
#Bring in seabird data, with Iti----
seabirds2 <- read.csv("../../seabird_data/outputs/seabird_dens_bio_by_side_iti_rimatuu_exposed_combined.csv")

seabirds2$site.name <- paste(seabirds2$Motu, seabirds2$Exposure, sep = "_")


##combine with algae data:----
n15.all.seabirds.iti <- merge(algae, seabirds2[,-1], by = c("site.name", 
                                                             "Motu", "Exposure"), all = TRUE, no.dups = TRUE)

#make sure distance to shore is a factor
n15.all.seabirds.iti$Distance_to_shore_f <- as.factor(n15.all.seabirds$Distance_to_shore)

n15.all.seabirds.iti$breeding_biomass_kgha_side
n15.all.seabirds$breeding_biomass_kgha_side
#yup, changes Rimatuu exposed from ~9 kg/ha to ~500 kg/ha

```

##re-run models with iti included, biomass/side:
```{r}
#again, checked log versus non-log, log looks best (and then is consistent across models):
n15.all.seabirds.iti2<-
  n15.all.seabirds.iti%>%
    mutate(log_breeding_biomass_kgha_side = log(breeding_biomass_kgha_side))


mod.lmer.breeding.log.iti <- lmer(N15 ~ log_breeding_biomass_kgha_side*Distance_to_shore + log_breeding_biomass_kgha_side*Exposure + (1|site.name), n15.all.seabirds.iti2)
plot(mod.lmer.breeding.log.iti)
qqnorm(resid(mod.lmer.breeding.log.iti))
hist(resid(mod.lmer.breeding.log.iti))


#test statistics----
summary(mod.lmer.breeding.log.iti)
Anova(mod.lmer.breeding.log.iti)
#log_breeding_biomass_kgha_side                   26.2179  1   3.05e-07 ***
#Distance_to_shore                                51.1976  3   4.44e-11 ***
#Exposure                                          1.9617  1     0.1613    
#log_breeding_biomass_kgha_side:Distance_to_shore  3.6329  3     0.3039    
#log_breeding_biomass_kgha_side:Exposure           1.9543  1     0.1621    


#look at emmeans, but ignore interactions because ns----
emtrends(mod.lmer.breeding.log.iti,  list(pairwise~ Exposure), var = "log_breeding_biomass_kgha_side", adjust = "fdr") #
emtrends(mod.lmer.breeding.log.iti,  list(pairwise~ Exposure), var = "log_breeding_biomass_kgha_side", adjust = "fdr", lmer.df = "asymptotic") #no difference in biomass effect on 2 sides of island (averaged over distance from shore)

emtrends(mod.lmer.breeding.log,  list(pairwise~ Exposure), var = "log_breeding_biomass_kgha_side", adjust = "fdr", lmer.df = "asymptotic") #compared to model without Iti - BIG DIFF (averaged over distance from shore)


emtrends(mod.lmer.breeding.log.iti,  list(pairwise~ Distance_to_shore), var = "log_breeding_biomass_kgha_side", adjust = "fdr", lmer.df = "asymptotic") #no differences with distance to shore (averaged over exposure)
emtrends(mod.lmer.breeding.log,  list(pairwise~ Distance_to_shore), var = "log_breeding_biomass_kgha_side", adjust = "fdr", lmer.df = "asymptotic") #compared to model without Iti - BIG DIFF (averaged over distance from shore)



test(emtrends(mod.lmer.breeding.log.iti,  ~1, var = "log_breeding_biomass_kgha_side", adjust = "fdr", lmer.df = "asymptotic"))
#1       log_breeding_biomass_kgha_side.trend    SE  df z.ratio p.value
# overall                                0.594 0.279 Inf   2.135  0.0328

#back transform estimates: because x log-transformed, need to raise trend log(2^(coef)) so each doubling of seabird biomass is associated with a change in mean algal n15 of log(2^coef) units
log(2^0.594) #0.4117294

test(emtrends(mod.lmer.breeding.log.iti,  ~Distance_to_shore, var = "log_breeding_biomass_kgha_side", adjust = "fdr", lmer.df = "asymptotic"))


#re-run with additive model because no interactions sig:
mod.lmer.breeding.log.iti.add <- lmer(N15 ~ log_breeding_biomass_kgha_side+Distance_to_shore + Exposure + (1|site.name), n15.all.seabirds.iti2)
plot(mod.lmer.breeding.log.iti.add)
qqnorm(resid(mod.lmer.breeding.log.iti.add))
hist(resid(mod.lmer.breeding.log.iti.add))
summary(mod.lmer.breeding.log.iti.add)
Anova(mod.lmer.breeding.log.iti.add)

```



##COMBINE FIGURES FOR RESTORATION STATUS, ALL SEABIRD BIOMASS RESULTS------
```{r}
###NO ITI----
plot_dat2.log<-emmip(mod.lmer.breeding.log, Distance_to_shore ~ log_breeding_biomass_kgha_side|Exposure, 
                     at = list(log_breeding_biomass_kgha_side = seq(1.68, 5.94, by = .01)), CIs = TRUE, plotit=FALSE)

plot_dat2.log

#rename and relvel exposure:
plot_dat2.log<-
  plot_dat2.log%>%
   mutate(Exposure = fct_recode(Exposure, leeward = "Protected", windward = "Exposed"))%>%
 mutate(Exposure = fct_relevel(Exposure, "leeward", "windward"))

#limit to correct range per group:
range(n15.all.seabirds2[n15.all.seabirds2$Exposure == "Protected",]$log_breeding_biomass_kgha_side)
range(n15.all.seabirds2[n15.all.seabirds2$Exposure == "Exposed",]$log_breeding_biomass_kgha_side)

plot_dat2.log.protected<-
  plot_dat2.log%>%
  filter(Exposure == "leeward")%>%
  filter(log_breeding_biomass_kgha_side>=1.6&log_breeding_biomass_kgha_side<=6)

plot_dat2.log.exposed<-
  plot_dat2.log%>%
  filter(Exposure == "windward")%>%
  filter(log_breeding_biomass_kgha_side>=2.2&log_breeding_biomass_kgha_side<=4.9)

sb_algae_n15_plot<-
n15.all.seabirds2 %>%
   mutate(Exposure = fct_recode(Exposure, leeward = "Protected", windward = "Exposed"))%>%
 mutate(Exposure = fct_relevel(Exposure, "leeward", "windward"))%>%
   ggplot(aes(x = exp(log_breeding_biomass_kgha_side), y = N15, color = Distance_to_shore, fill = Distance_to_shore, group = Distance_to_shore))+
  geom_point(alpha = .9, size = 3, aes(shape = Exposure))+
   geom_ribbon(data = plot_dat2.log.protected, aes(x = exp(log_breeding_biomass_kgha_side), y = yvar, ymin = LCL, ymax=UCL, fill = Distance_to_shore), alpha = .2, linetype=0)+
     geom_ribbon(data = plot_dat2.log.exposed, aes(x = exp(log_breeding_biomass_kgha_side), y = yvar, ymin = LCL, ymax=UCL, fill = Distance_to_shore), alpha = .2, linetype=0)+
 geom_line(data = plot_dat2.log.protected, aes(x = exp(log_breeding_biomass_kgha_side), y = yvar, color = Distance_to_shore, group = Distance_to_shore))+
   geom_line(data = plot_dat2.log.exposed, aes(x = exp(log_breeding_biomass_kgha_side), y = yvar, color = Distance_to_shore, group = Distance_to_shore))+
  theme_bw() +
  facet_wrap(~Exposure)+
   xlab("Seabird breeding biomass (kg/ha)")+
  ylab(expression(Algal~delta^15~N))+
#  scale_fill_viridis_d()+
#  scale_color_viridis_d()+
    scale_fill_viridis_d(option = "mako")+
  scale_color_viridis_d(option = "mako")+
  labs(color = "Distance to shore (m)", fill = "Distance to shore (m)")+
  guides(shape = "none")+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.85,.8),
        legend.background = element_blank(),
        strip.text = element_text(hjust = 0, size = 12))+
  facet_wrap(~Exposure, strip.position = "top",  
             labeller = labeller (Exposure = c("leeward" = "a. Leeward", "windward" = "b. Windward")))

sb_algae_n15_plot


### ITI----
plot_dat2.log.iti.add2<-emmip(mod.lmer.breeding.log.iti.add, Distance_to_shore ~ log_breeding_biomass_kgha_side, 
                     at = list(log_breeding_biomass_kgha_side = seq(1.68, 6.22, by = .01)), CIs = TRUE, plotit=FALSE)

sb_algae_n15_plot_iti<-
n15.all.seabirds.iti2 %>%
   mutate(Exposure = fct_recode(Exposure, leeward = "Protected", windward = "Exposed"))%>%
 mutate(Exposure = fct_relevel(Exposure, "leeward", "windward"))%>%
   ggplot(aes(x = exp(log_breeding_biomass_kgha_side), y = N15, color = Distance_to_shore, fill = Distance_to_shore, group = Distance_to_shore))+
  geom_point(alpha = .9, size = 3, aes(shape = Exposure))+
   geom_ribbon(data = plot_dat2.log.iti.add2, aes(x = exp(log_breeding_biomass_kgha_side), y = yvar, ymin = LCL, ymax=UCL, fill = Distance_to_shore), alpha = .2, linetype=0)+
 geom_line(data = plot_dat2.log.iti.add2, aes(x = exp(log_breeding_biomass_kgha_side), y = yvar, color = Distance_to_shore, group = Distance_to_shore))+
  theme_bw() +
   xlab("Seabird breeding biomass (kg/ha)")+
  ylab(expression(Algal~delta^15~N))+
#  scale_fill_viridis_d()+
#  scale_color_viridis_d()+
    scale_fill_viridis_d(option = "mako")+
  scale_color_viridis_d(option = "mako")+
  labs(color = "Distance to shore (m)", fill = "Distance to shore (m)", shape = "Exposure")+
  ggtitle("e. Including nearby seabirds")+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.8,.25),
        legend.background = element_blank(),
        legend.box = "horizontal",
        plot.title = element_text(size=12))
sb_algae_n15_plot_iti



##REST STATUS
N15.lineplot.exposure <- 
  n15.line.sum.exp%>%
  mutate(Exposure = fct_recode(Exposure, leeward = "Protected", windward = "Exposed"))%>%
 mutate(Exposure = fct_relevel(Exposure, "leeward", "windward"))%>%
  ggplot(aes(x = Distance_to_shore, y = mean_n15, fill = reststat, color = reststat, group = reststat) )+
  #geom_boxplot(alpha = 0.6) +
  geom_point(alpha = 0.9, size = 5, aes(color = reststat, shape = Exposure)) +
  geom_errorbar(aes(ymin = (mean_n15-se_n15), ymax = (mean_n15+se_n15)), alpha = .5, width = 0.1)+
  geom_line(alpha = .6, lwd = 1.2)+
  ylab(expression(Algal~italic(delta)^15*N)) +
  #scale_fill_manual(values = c( "unrestored" = "#CD1913", "recovering" = "#F2BB05", "reference" ="#2F9D3E")) + # red-yellow-green
  scale_colour_manual(values = c( "unrestored" = "#CD1913", "recovering" = "#F2BB05", "reference" ="#2F9D3E")) +
  xlab("Distance to Shore (m)")+
  guides(shape = "none")+
  #labs(color='Distance \nFrom Shore (m)', fill = 'Distance \nFrom Shore (m)') +
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.title = element_blank(),
        legend.position = c(.88, .85),
        strip.text = element_text(hjust = 0, size = 12))+
  facet_wrap(~Exposure, strip.position = "top",  
             labeller = labeller (Exposure = c("leeward" = "c. Leeward", "windward" = "d. Windward")))

N15.lineplot.exposure


sb_algae_n15_plot_iti<-
  sb_algae_n15_plot_iti+
  theme(plot.margin = unit(c(0,3.5,0,3.5), "cm"),
        legend.position = c(.6,.25))

##combine all:
sb_algae_plots<-cowplot::plot_grid(sb_algae_n15_plot, N15.lineplot.exposure, sb_algae_n15_plot_iti, 
                                   ncol = 1, scale = c(1,1,1)) #, rel_heights = c(1,1,.8),
sb_algae_plots


#ggsave(sb_algae_plots, file = "../output/seabird-algaen15/sb_algae_plots_combined.jpg",
#    width = 8, height = 12)
#ggsave(sb_algae_plots, file = "../output/seabird-algaen15/sb_algae_plots_combined.pdf",
#    width = 8, height = 12)

```
