---
title: "seabirds_vs_fish_condition"
author: "CEB"
date: '2024-01-23'
output: html_document
---


#load packages
```{r}
library(tidyverse)

library(lme4)
library(car)
library(jtools)

library(emmeans)

library(corrplot)

```


#load data
```{r}
seabirds <- read.csv("../output/n15_seabirds_combined_no_iti.csv", strip.white = T, header = T)
fish_n15_cond <- read.csv("../../fish_isotopes/output/fish_n15_condition.csv", stringsAsFactors = TRUE)
algae_n15<-read.csv("../output/n15_seabirds_combined_no_iti.csv")

```



#merge data
```{r}
#make combined site name column in fish_n15

fishn15.seabirds.cond<-right_join(dplyr::select(seabirds, c("site.name", "breeding_biomass_kgha_side")), 
                                  dplyr::select(fish_n15_cond, c("site.name", "motu", "fish.id", "species", 
                                                   "month.caught", "year.caught", "protection", "TL.cm", "FL.cm", "SL.cm", "whole.weight.g", 
                                                   "liver.weight.g", "n15", "c13", "n.percent", "c.percent")),
                            
                                   by = "site.name")%>%
  mutate(site.name = as.factor(site.name))
fishn15.seabirds.cond

```

#calculate condition indices, add seabird levels
```{r}

#add k and hsi----

fishn15.seabirds.cond<-
  fishn15.seabirds.cond%>%
  mutate(K = 100*(whole.weight.g/(TL.cm^3)),
         HSI = liver.weight.g/whole.weight.g*100)
fishn15.seabirds.cond


#3 sites, add seabird levels because non-linear possible and only 3 sites so needs to be categorical:----
#Aie protected = 378.720000	
#Reiono exposed = 115.353333
#Rimatuu protected = 5.390526

fishn15.seabirds.cond<-
  fishn15.seabirds.cond%>%
  mutate(seabird_level = case_when(breeding_biomass_kgha_side<10 ~"low",
                                   breeding_biomass_kgha_side>10&breeding_biomass_kgha_side <200 ~"mid",
                                   breeding_biomass_kgha_side>200 ~"high"))%>%
  mutate(seabird_level = as.factor(seabird_level))%>%
  mutate(seabird_level = fct_relevel(seabird_level, "low", "mid", "high"))%>%
  relocate(seabird_level, .before = breeding_biomass_kgha_side)

fishn15.seabirds.cond



##remove C. argus because n = 1 for 'high' (Aie)----
fishn15.seabirds.cond.r<-
  fishn15.seabirds.cond%>%
  filter(species != "Cephalopholis argus")%>%
  droplevels()


##check sample sizes, lengths per site:----
fishn15.seabirds.cond.r%>%
  group_by(species, site.name)%>%
  summarize(n = length(n15))


```


#run regular lm's USING SEABIRD LEVELS, because now only one site per motu (so random effects don't make much sense):
```{r}

#n15----
fish_n15_lm<-lm(n15~ seabird_level*species, 
                          data = fishn15.seabirds.cond)
summary(fish_n15_lm)
anova(fish_n15_lm)#everything significant
plot(fish_n15_lm) #qq not great, and one point (10) with extremely high leverage = Aie C. argus because n = 1 for this***


#re-run without argus, n15---
fish_n15_r_lm<-lm(n15~ seabird_level*species, 
                          data = fishn15.seabirds.cond.r)
summary(fish_n15_r_lm)
anova(fish_n15_r_lm) #everything significant
plot(fish_n15_r_lm) #qq not great


fish_n15_r_log_lm<-lm(log(n15)~ seabird_level*species, 
                          data = fishn15.seabirds.cond.r)
summary(fish_n15_r_log_lm)
anova(fish_n15_r_log_lm) #everything significant
plot(fish_n15_r_log_lm) #qq still not great. proceed with non-log for now....

emmeans(fish_n15_r_log_lm, list(revpairwise ~ seabird_level|species), adjust = "fdr", type = "response")
emmeans(fish_n15_r_log_lm, list(pairwise ~ seabird_level|species), adjust = "fdr", type = "response")


#look at emmeans:
fish_n15_r_lm %>% 
  emmeans(~ seabird_level|species,
          type = "response") 


EMM_fish_n15 <- emmeans(fish_n15_r_lm, ~ species * seabird_level)
pairs(EMM_fish_n15, simple = "seabird_level", type = "response")
#Ab sept - mid and high are both higher than low, but not different from each other***
#A tri - low is lower than mid, and mid is marginally higher than high. low and high not different
#Lutjanus - nothing significant
#Stegastes nigricans - low is marginally lower than mid, all else not difference.


test(pairs(EMM_fish_n15, by = "species"), by = NULL, adjust = "mvt")
test(pairs(EMM_fish_n15, by = "species"), by = NULL, adjust = "none")
#similar to pairs results above

emmeans(EMM_fish_n15, list(pairwise ~ seabird_level|species), adjust = "fdr")
emmeans(fish_n15_r_lm, list(pairwise ~ seabird_level|species), adjust = "fdr")
#same results


```

##some plots using emmeans----
```{r}
#response plot n15----
plot_data_n15<-emmip(fish_n15_r_lm, ~ seabird_level*species,
          type = "response", CIs = TRUE, plotit=FALSE)%>%
    mutate(species = fct_relevel(species, c("Acanthurus triostegus", "Stegastes nigricans", "Abudefduf septemfasciatus", "Lutjanus fulvus")))

plot_data_n15

#my_colors <- RColorBrewer::brewer.pal(9, "Blues")[c(2, 4, 6, 8)]

fish_n15_response_int_plot<-
  ggplot(data = plot_data_n15, aes(x = seabird_level, y = yvar, color = species, fill = species, group = species))+
#  geom_point(pch = 4,  position = position_dodge(.3))+
  geom_pointrange(aes(ymin = LCL, ymax = UCL), alpha = .3, linewidth = 2, size = 0,  position = position_dodge(.1)) + #,  position = position_dodge(.3)
 # geom_point(data = fishn15.seabirds.cond.r, 
           #  aes(y = n15, x = seabird_level), size = 2.5, alpha = .5,  position = position_dodge(.3))+ 
    geom_line(alpha = .5 ,  position = position_dodge(.1))+
  #scale_fill_manual(values = my_colors)+
 # scale_color_manual(values = my_colors) +
  ylab(expression(delta^15~N))+
  xlab("")+
   theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.15,.85) )

fish_n15_response_int_plot



fish_n15_response_int_plot_flipped<-
  ggplot(data = plot_data_n15, aes(x = species, y = yvar, color = seabird_level, fill = seabird_level))+
  geom_point(pch = 21,  position = position_dodge(.3))+
  geom_pointrange(aes(ymin = LCL, ymax = UCL), alpha = .3, linewidth = 5, size = 0,  position = position_dodge(.3)) + 
 # geom_point(data = fishn15.seabirds.cond.r, 
    #         aes(y = n15, x = species), size = 2.5, alpha = .5,  position = position_dodge(.3))+
scale_fill_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+ #low-mid-high = red-yellow-green
    scale_colour_manual(values = c( "low" = "#CD1913", "mid" = "#F2BB05", "high" ="#2F9D3E"))+#low-mid-high = red-yellow-green
  ylab(expression(delta^15~N))+
  xlab("")+
  labs(color = "seabird level", fill = "seabird level")+
   theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.23,.92),
        legend.direction = "horizontal",
        legend.box.background = element_rect(colour = "black"))
#,
       # axis.text = element_text(size = 14),
       # axis.title.y = element_text(size = 14)


fish_n15_response_int_plot_flipped

#ggsave("../output/seabird-fishn15/fish_n15_sb_level_estplot.pdf", plot = fish_n15_response_int_plot_flipped)
#ggsave("../output/seabird-fishn15/fish_n15_sb_level_estplot.jpg", plot = fish_n15_response_int_plot_flipped)
#ggsave("../output/seabird-fishn15/fish_n15_sb_level_estplot_diff_axes.jpg", plot = fish_n15_response_int_plot)


```


#run regular lm's USING ALGAE N15 AT 40, because now only one site per motu (so random effects don't make much sense): - still need to clean up figures, likely for supplement*
```{r}

#combine data with algae n15----
fishn15.seabirds.cond.algae<-
  left_join(fishn15.seabirds.cond.r, 
            select(algae_n15, c("site.name", "N.15_at_10m", "N.15_at_20m","N.15_at_30m","N.15_at_40m")), 
            by = "site.name")
fishn15.seabirds.cond.algae


#n15----
fish_n15_algae_lm<-lm(n15~ N.15_at_40m*species, 
                          data = fishn15.seabirds.cond.algae)
summary(fish_n15_algae_lm)
anova(fish_n15_algae_lm)#everything significant
plot(fish_n15_algae_lm) #okay


#look at emmeans:
emtrends(fish_n15_algae_lm,  ~ species, var = "N.15_at_40m")
#looks like Ab sept and Ac tri both are positive. Other two trending towards positive but overlaps 0

test(emtrends(fish_n15_algae_lm, ~ species, var = "N.15_at_40m", adjust = "fdr"))
test(emtrends(fish_n15_algae_lm, ~ species, var = "N.15_at_40m", adjust = "none"))


#try with lmer:
fish_n15_algae_lmer<-lmer(n15~ N.15_at_40m*species + (1|site.name), 
                          data = fishn15.seabirds.cond.algae)
summary(fish_n15_algae_lmer)
Anova(fish_n15_algae_lmer)

test(emtrends(fish_n15_algae_lmer, ~ species, var = "N.15_at_40m", adjust = "fdr"))
emtrends(fish_n15_algae_lmer, ~ species, var = "N.15_at_40m")


fish_n15_algae_lmer.add<-lmer(n15~ N.15_at_40m+species + (1|site.name), 
                          data = fishn15.seabirds.cond.algae)
summary(fish_n15_algae_lmer.add)
Anova(fish_n15_algae_lmer.add)


# plot - maybe just for supplement---------
range(fishn15.seabirds.cond.algae$N.15_at_40m) #3.043333 6.003333
levels(fishn15.seabirds.cond.algae$species)
(mylist <- list(
    N.15_at_40m = seq(3, 6, by = 1),
    species = c("Abudefduf septemfasciatus", "Acanthurus triostegus" ,   "Lutjanus fulvus"     ,     
 "Stegastes nigricans")
))

emmip(fish_n15_algae_lm, species ~ N.15_at_40m, at = mylist, CIs = TRUE)



#plot raw data + lines: 
plot_dat<-emmip(fish_n15_algae_lm, species ~ N.15_at_40m, at = mylist, CIs = TRUE, plotit=FALSE)
plot_dat

fishn15.seabirds.cond.algae %>%
   ggplot(aes(x = N.15_at_40m, y = n15, color = species, fill = species, group = species))+
  geom_point(alpha = .5)+
geom_line(data = plot_dat, aes(x = N.15_at_40m, y = yvar, color = species, group = species))+
  theme_bw() 


(mylist2 <- list(
    N.15_at_40m = c(3.043333, 5.233333, 6.003333),
    species = c("Abudefduf septemfasciatus", "Acanthurus triostegus" ,   "Lutjanus fulvus"     ,     
 "Stegastes nigricans")
))
plot_dat2<-emmip(fish_n15_algae_lm, species ~ N.15_at_40m, at = mylist2, CIs = TRUE, plotit=FALSE)
plot_dat2

fishn15.seabirds.cond.algae %>%
      mutate(species = fct_relevel(species, c("Acanthurus triostegus", "Stegastes nigricans", "Abudefduf septemfasciatus", "Lutjanus fulvus")))%>%
   ggplot(aes(x = N.15_at_40m, y = n15, color = species, fill = species, group = species))+
  geom_point(alpha = .5)+
   geom_ribbon(data = plot_dat2, aes(x = N.15_at_40m, y = yvar, ymin = LCL, ymax=UCL, fill = species), alpha = .2, lwd=0)+
 geom_line(data = plot_dat2, aes(x = N.15_at_40m, y = yvar, color = species, group = species))+
  theme_bw() 

fishn15.algan15.plot<-
fishn15.seabirds.cond.algae %>%
      mutate(species = fct_relevel(species, c("Acanthurus triostegus", "Stegastes nigricans", "Abudefduf septemfasciatus", "Lutjanus fulvus")))%>%
   ggplot(aes(x = N.15_at_40m, y = n15, color = species, fill = species, group = species))+
  geom_point(alpha = .8)+
   geom_ribbon(data = plot_dat2, aes(x = N.15_at_40m, y = yvar, ymin = LCL, ymax=UCL, fill = species), alpha = .2, lwd=0)+
 geom_line(data = plot_dat2, aes(x = N.15_at_40m, y = yvar, color = species, group = species))+
  ylab(expression(Fish~delta^15~N))+
  xlab(expression(Algae~delta^15~N))+
  labs(color = "", fill = "")+
  theme_bw() +
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.2,.85),
        legend.background = element_blank())
        #legent.key = element_rect) #,
        #legend.direction = "horizontal",
      #  legend.box.background = element_rect(colour = "black"))
fishn15.algan15.plot


#ggsave("../output/seabird-fishn15/fish_n15_algae_n15_estplot_lines_points.jpg", plot = fishn15.algan15.plot, width = 7, height = 5)

#just raw data:
fishn15.seabirds.cond.algae %>%
   ggplot(aes(x = N.15_at_40m, y = n15, color = species, fill = species, group = species))+
  geom_point(alpha = .5)+
  stat_smooth(method = "lm")+
  theme_bw() 

fishn15.seabirds.cond.algae%>%
  group_by(species, N.15_at_40m)%>%
  summarize(mean_n15 = mean(n15),
            n_n15 = length(n15),
            se_n15 = sd(n15)/sqrt(n_n15))%>%
  ggplot(aes(x = N.15_at_40m, y = mean_n15, color = species, fill = species, group = species))+
  geom_point(alpha = .5)+
  geom_errorbar(aes(ymin = (mean_n15-se_n15), ymax = (mean_n15+se_n15)), alpha = .5, width = 0)+
  geom_line(alpha = .5)+
  theme_bw() 


```



#correlation test
```{r}
##also include n15 at various distances just to see if matches up:

fishn15.seabirds.cond.algae<-
  left_join(fishn15.seabirds.cond.r, 
            select(algae_n15, c("site.name", "N.15_at_10m", "N.15_at_20m","N.15_at_30m","N.15_at_40m")), 
            by = "site.name")
fishn15.seabirds.cond.algae


##separate fish species----
#a little complicated bc different sample sizes for different species/site combos:
fishn15.seabirds.long<- 
  fishn15.seabirds.cond.algae %>%
    select(c(site.name, species, n15, breeding_biomass_kgha_side, N.15_at_10m, N.15_at_20m, N.15_at_30m, N.15_at_40m))%>%
  group_by(site.name, species) %>%
  mutate(Index=row_number())%>%
  relocate(Index, .before = site.name)
fishn15.seabirds.long

fishn15.seabirds.wide <- 
  pivot_wider(fishn15.seabirds.long,names_from = c("species"),values_from = c("n15"))
fishn15.seabirds.wide

corr_mat_fish_n15_sb_sp<-as.data.frame(fishn15.seabirds.wide[c(3,7:11)]) #only need to start with seabird biomass and offshore algae

cor(corr_mat_fish_n15_sb_sp, method = "spearman", use = "pairwise.complete.obs")
cor(corr_mat_fish_n15_sb_sp, method = "pearson", use = "pairwise.complete.obs")

##spearman:
cor.mat_sb_fishn15_byspp<- cor(fishn15.seabirds.wide[c(3,7,8,10,11,9)], method = "spearman", use = "pairwise.complete.obs")
cor.mat_sb_fishn15_byspp
corrplot(cor.mat_sb_fishn15_byspp, type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5)

##pearson:
cor.mat_sb_fishn15_byspp_pearson<- cor(fishn15.seabirds.wide[c(3,7,8,10,11,9)], method = "pearson", use = "pairwise.complete.obs")
cor.mat_sb_fishn15_byspp_pearson
corrplot(cor.mat_sb_fishn15_byspp_pearson, type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5)


##spearman, no algae:
cor.mat_sb_fishn15_byspp_no_algae<- cor(fishn15.seabirds.wide[c(3,8,10,11,9)], method = "spearman", use = "pairwise.complete.obs")
cor.mat_sb_fishn15_byspp_no_algae
corrplot(cor.mat_sb_fishn15_byspp_no_algae, type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5)

##save outputs----
#chunk 1
pdf(file = "../output/seabird-fishn15/seabirds_fishn15_corr_plot_by_sp_SPEARMAN.pdf")
corrplot(cor.mat_sb_fishn15_byspp, type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5)
dev.off()


#chunk 2
pdf(file = "../output/seabird-fishn15/seabirds_fishn15_corr_plot_by_sp_PEARSON.pdf")
corrplot(cor.mat_sb_fishn15_byspp_pearson, type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5)
dev.off()


##Oh wait, all a bit weird because of NAs, and correlations among fish species depend on order-----
cor(fishn15.seabirds.wide[c(3,8,10,11,9)], method = "spearman", use = "pairwise.complete.obs")
cor(fishn15.seabirds.wide[c(3,10)], method = "spearman", use = "pairwise.complete.obs")
cor(fishn15.seabirds.wide[c(3,11)], method = "spearman", use = "pairwise.complete.obs")
cor(fishn15.seabirds.wide[c(3,9)], method = "spearman", use = "pairwise.complete.obs")
cor(fishn15.seabirds.wide[c(3,8)], method = "spearman", use = "pairwise.complete.obs")
#okay, each species corr with seabird biomass matches*

#what if we arrange within each species/biomass level, n15 from high to low:
fishn15.seabirds.long2<- 
  fishn15.seabirds.cond.algae %>%
    select(c(site.name, species, n15, breeding_biomass_kgha_side, N.15_at_10m, N.15_at_20m, N.15_at_30m, N.15_at_40m))%>%
    arrange(desc(n15))%>%
  group_by(site.name, species) %>%
  mutate(Index=row_number())%>%
  relocate(Index, .before = site.name)
fishn15.seabirds.long

fishn15.seabirds.wide2 <- 
  pivot_wider(fishn15.seabirds.long2,names_from = c("species"),values_from = c("n15"))
fishn15.seabirds.wide2

corrplot(cor(fishn15.seabirds.wide2[c(3,8,11,9, 10)], method = "spearman", use = "pairwise.complete.obs"), type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5)

cor(fishn15.seabirds.wide2[c(3,8,11,9, 10)], method = "spearman", use = "pairwise.complete.obs")
cor(fishn15.seabirds.wide[c(3,8,10,11,9)], method = "spearman", use = "pairwise.complete.obs")
#YUP, now really different cors***
#SO: can't show correlations across different fish species, unless we were to take a mean per site or something, but then we'd only have 3 points....


###save:----
cor.mat_sb_fishn15_byspp_no_algae<- cor(fishn15.seabirds.wide[c(3,8,10,11,9)], method = "spearman", use = "pairwise.complete.obs")

cor.mat_sb_fishn15_fish_by_sb_only<- cor(x = fishn15.seabirds.wide[c(3)], y =fishn15.seabirds.wide[c(8,10,11,9)], method = "spearman", use = "pairwise.complete.obs")



pdf(file = "../output/seabird-fishn15/seabirds_fishn15_corr_plot_by_sp_sb_onlySPEARMAN.pdf")
corrplot(cor.mat_sb_fishn15_fish_by_sb_only, type = "full",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5)
dev.off()


pdf(file = "../output/seabird-fishn15/seabirds_fishn15_corr_plot_by_sp_sb_onlySPEARMAN_LEGEND.pdf")
corrplot(cor.mat_sb_fishn15_byspp_no_algae, type = "full",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5, cl.pos = "b")
dev.off()


#try with seabirds and algae:
cor.mat_sb_fishn15_fish_by_sb_algae_only<- cor(x = fishn15.seabirds.wide[c(3,4,5,6,7)], y =fishn15.seabirds.wide[c(8,10,11,9)], method = "spearman", use = "pairwise.complete.obs")


```



#any way to combine algae and fish corr plots?? - NOPE

