---
title: "seabird_analysis"
author: "CEB"
date: '2023-08-28'
output: html_document
---

Analysis of seabird data from Tetiaroa. Original correlations analysis done in seabird_data_prep.Rmd file

#load packages
```{r}
library(tidyverse)

library(lme4)
library(car)
library(jtools)

library(vegan)

library(emmeans)


library(RColorBrewer)
library(cowplot)


library(corrplot)

```


#load data
```{r}
#load seabird data----
load("outputs/seabird_dens_bio_data.RData")

#by species:
#sb_dat_focal_nests_motu_sp
#sb_dat_focal_nests_100m_sp
#sb_dat_focal_nests_200m_sp
#sb_dat_focal_nests_side_sp

#sb_dat_focal_adults_motu_sp
#sb_dat_focal_adults_100m_sp
#sb_dat_focal_adults_200m_sp
#sb_dat_focal_adults_side_sp

#plus iti by species:
#sb_dat_iti_adults_sp
#sb_dat_iti_nests_sp

#aggregated:
#seabird_focal_all
#seabird_side_w_iti


#load metadata----
site_metdata<-read.csv("../metadata/TARP_Nov2021_site_metadata_version2.csv")
str(site_metdata)   

```


#combine seabird data + metadata
```{r}
str(seabird_focal_all)
str(site_metdata)   

#in seabird data - change to lowercase, change name of exposure -> "protection"
seabird_focal_all2<-
  seabird_focal_all%>%
  rename_with(tolower)%>%
  mutate(motu = str_to_lower(motu),
         exposure = str_to_lower(exposure))%>%
  rename(protection = exposure)
  
seabird_focal_all2

seabird_focal_all_meta<-right_join(select(site_metdata, 
                                                             c("motu", "site.name", "protection", "island.side", "rat.eradication.status")), seabird_focal_all2, by = join_by(motu, protection))

seabird_focal_all_meta

```

#check which seabird species dominates density/biomsas
```{r}
sb_dat_focal_nests_motu_sp %>%
  group_by(SpeciesName)%>%
  summarize(sum_abundance = sum(Abundance),
            sum_density = sum(Density_ha),
            sum_biomass = sum(biomass_kg_ha))

#density:
4.210526/(4.210526+268.823529	+13.034056	+382.807018) #0.006294936
268.823529/(4.210526+268.823529	+13.034056	+382.807018) #0.4019039
13.034056/(4.210526+268.823529	+13.034056	+382.807018) #0.01948653
382.807018/(4.210526+268.823529	+13.034056	+382.807018) #0.5723146


#biomass:
0.4736842/(0.4736842+50.8076471	+1.5249845	+373.2368421) #0.001111822
50.8076471/(0.4736842+50.8076471	+1.5249845	+373.2368421) #0.1192547
1.5249845/(0.4736842+50.8076471	+1.5249845	+373.2368421) #0.003579413
373.2368421/(0.4736842+50.8076471	+1.5249845	+373.2368421) #0.8760541

```


#run analysis with spatial scale as a predictor
```{r}
seabird_focal_all_meta

#start with breeding biomass:
seabird_focal_all_meta_br_bio<-
  seabird_focal_all_meta[,(1:9)]
seabird_focal_all_meta_br_bio


seabird_focal_all_meta_long<-pivot_longer(seabird_focal_all_meta_br_bio,
                                          cols = starts_with("breeding_biomass_kgha"),
                                          names_to = "spatial_scale",
                                          values_to = "breeding_biomass")%>%
  mutate(spatial_scale = str_remove(spatial_scale, 'breeding_biomass_kgha_'))
seabird_focal_all_meta_long

#run regular lm----
#lmms don't work because random effect of motu equivalent to eradication status
sb_br_bio_space_mod_lm<-lm(breeding_biomass~ rat.eradication.status + protection + spatial_scale, 
                          data = seabird_focal_all_meta_long)
summary(sb_br_bio_space_mod_lm)
plot_summs(sb_br_bio_space_mod_lm)
Anova(sb_br_bio_space_mod_lm)
##THIS LOOKS PROMISING - hierarchy in seabird biomass by rat status, protected sides also tend to have higher biomass...
#no trends by spatial scale...
plot(sb_br_bio_space_mod_lm)

#do post-hoc test for rat eradication? - Tukey HSD didn't work, use emmeans for estiamtes:
sb_br_bio_space_mod_lm %>% 
  emmeans(~ rat.eradication.status,
          type = "response") 


sb_br_bio_space_mod_lm %>% 
  emmeans(~ rat.eradication.status|protection,
          type = "response") 


#looks good, except some estimates below 0 so that doesn't make sense....may need to use a different distribution***
#OR do log***

#run log model to avoid negative values for seabird estimates----
#(need log + 1 because one 0 value)
sb_br_bio_space_mod_log_lm<-lm(log(breeding_biomass+1)~ rat.eradication.status + protection + spatial_scale, 
                          data = seabird_focal_all_meta_long)
summary(sb_br_bio_space_mod_log_lm)
plot_summs(sb_br_bio_space_mod_log_lm)
Anova(sb_br_bio_space_mod_log_lm)
plot(sb_br_bio_space_mod_log_lm)

sb_br_bio_space_mod_log_lm %>% 
  emmeans(~ rat.eradication.status,
          type = "response") 
#now makes sense***

sb_br_bio_space_mod_log_lm %>% 
  emmeans(~ rat.eradication.status|protection,
          type = "response") 


sb_br_bio_space_mod_log_lm %>% 
  emmeans(~ rat.eradication.status|spatial_scale,
          type = "response") 


sb_br_bio_space_mod_log_lm %>% 
  emmeans(~ rat.eradication.status|spatial_scale + protection,
          type = "response") 

#do lrt
sb_br_bio_space_mod_log_lm_r<-lm(log(breeding_biomass+1)~ protection + spatial_scale, 
                          data = seabird_focal_all_meta_long)
anova(sb_br_bio_space_mod_log_lm, sb_br_bio_space_mod_log_lm_r)


#run interaction model
sb_br_bio_space_mod_log_lm_int<-lm(log(breeding_biomass+1)~ rat.eradication.status * protection * spatial_scale, 
                          data = seabird_focal_all_meta_long)
summary(sb_br_bio_space_mod_log_lm_int)
#Anova(sb_br_bio_space_mod_log_lm_int)
#doens't work - not enough power...


sb_br_bio_space_mod_log_lm_int<-lm(log(breeding_biomass+1)~ rat.eradication.status * protection + spatial_scale, 
                          data = seabird_focal_all_meta_long)
summary(sb_br_bio_space_mod_log_lm_int)
Anova(sb_br_bio_space_mod_log_lm_int)
#marginal interaction


sb_br_bio_space_mod_log_lm_int<-lm(log(breeding_biomass+1)~ rat.eradication.status * protection + spatial_scale*rat.eradication.status + protection*spatial_scale, 
                          data = seabird_focal_all_meta_long)
summary(sb_br_bio_space_mod_log_lm_int)
Anova(sb_br_bio_space_mod_log_lm_int)
#marginal interaction between protectoin*eradication status.  eradication status also significant

sb_br_bio_space_mod_log_lm_int %>% 
  emmeans(~ protection|rat.eradication.status,
          type = "response") 
#where rats present, similar low densities across both sides
#but where no rats, trend towards higher biomass on protected sides within each motu. Strongest pattern on Aie....Really this is because RFB's nest on north side but not south side of motu. 

```

#re-run and extract interaction estimates
```{r}

sb_br_bio_space_mod_log_lm_3int<-lm(log(breeding_biomass+1)~ rat.eradication.status * protection * spatial_scale, 
                          data = seabird_focal_all_meta_long)
summary(sb_br_bio_space_mod_log_lm_3int)
#can't do 3-way interaction - not enough power.  So proceed with 2-way interactions:


sb_br_bio_space_mod_log_lm_2int<-lm(log(breeding_biomass+1)~ rat.eradication.status * protection + spatial_scale*rat.eradication.status + protection*spatial_scale, 
                          data = seabird_focal_all_meta_long)
summary(sb_br_bio_space_mod_log_lm_2int)
plot(sb_br_bio_space_mod_log_lm_2int) #plots/assumptions look okay


anova(sb_br_bio_space_mod_log_lm_2int)
Anova(sb_br_bio_space_mod_log_lm_2int)#same as anova
#marginal interaction between protection*eradication status.  eradication status also significant

#get estimates using emmeans:
sb_br_bio_space_mod_log_lm_2int %>% 
  emmeans(~ protection|rat.eradication.status,
          type = "response") 
#where rats present, similar low densities across both sides
#but where no rats, trend towards higher biomass on protected sides within each motu. Strongest pattern on Aie....Really this is because RFB's nest on north side but not south side of motu. 

sb_br_bio_space_mod_log_lm_2int %>% 
  emmeans(~ rat.eradication.status,
          type = "response") 

#re-run non-logged model just to check: 
sb_br_bio_space_mod_lm_2int<-lm(breeding_biomass~ rat.eradication.status * protection + spatial_scale*rat.eradication.status + protection*spatial_scale, 
                          data = seabird_focal_all_meta_long)
summary(sb_br_bio_space_mod_lm_2int)
anova(sb_br_bio_space_mod_lm_2int)
#now interaction between rats*protection p = .05325, protection = .04, rat status = .001
plot(sb_br_bio_space_mod_lm_2int) #plots/assumptions actually look okay

sb_br_bio_space_mod_lm_2int %>% 
  emmeans(~ protection|rat.eradication.status,
          type = "response") 
#doesn't make much sense because CIs falling below 0, not biologically realistic.  So go with log model:


sb_br_bio_space_mod_log_lm_2int %>% 
  emmeans(~ rat.eradication.status|protection,
          type = "response") 


sb_br_bio_space_mod_log_lm_2int %>% 
  emmeans(~ protection|rat.eradication.status,
          type = "response") 


EMM_rat <- emmeans(sb_br_bio_space_mod_log_lm_2int, ~ protection * rat.eradication.status)
pairs(EMM_rat, simple = "rat.eradication.status", type = "response")
#so when split by side, actually eradicated 2018 and rat-free are the same (p = 0.16).  But on protected side all 3 levels different.

pairs(EMM_rat, simple = "protection", type = "response")
#and when split by rat status, only rat-free has sig different exposed versus protected....


test(pairs(EMM_rat, by = "rat.eradication.status"), by = NULL, adjust = "mvt")
test(pairs(EMM_rat, by = "rat.eradication.status"), by = NULL, adjust = "none")



test(pairs(EMM_rat, by = "protection"), by = NULL, adjust = "mvt")
test(pairs(EMM_rat, by = "protection"), by = NULL, adjust = "none")
test(pairs(EMM_rat, by = "protection"), by = NULL, adjust = "fdr")

test(pairs(EMM_rat, by = "protection"), by = NULL, adjust = "fdr",
     )


test(pairs(emmeans(sb_br_bio_space_mod_log_lm_2int, ~ protection | rat.eradication.status, adjust = "fdr", type = "response")))
test(pairs(emmeans(sb_br_bio_space_mod_log_lm_2int, ~ rat.eradication.status | protection, adjust = "fdr", type = "response")))
test(emmeans(sb_br_bio_space_mod_log_lm_2int, ~ rat.eradication.status, adjust = "fdr", type = "response"))


emmeans(sb_br_bio_space_mod_log_lm_2int, list(revpairwise ~ protection | rat.eradication.status), type = "response", adjust = "fdr")


emmeans(sb_br_bio_space_mod_log_lm_2int, list(revpairwise ~ rat.eradication.status), type = "response", adjust = "fdr")
emmeans(sb_br_bio_space_mod_log_lm_2int, list(pairwise ~ rat.eradication.status), type = "response", adjust = "fdr")

#need to decide best method for extracting p-values**** Currently using ANOVA table for overall p-values, and emmeans for estimates and pairwise comparisons****

```


#maybe show plots of raw values and model estimates - WITH INTERACTIONS
```{r}

#emmeans plot----
plot(emmeans(sb_br_bio_space_mod_log_lm_2int, ~ rat.eradication.status*protection,
          type = "response"))


#response plot----
plot_data<-emmip(sb_br_bio_space_mod_log_lm_2int, ~ rat.eradication.status*protection,
          type = "response", CIs = TRUE, plotit=FALSE)%>%
  mutate(rat.eradication.status = fct_relevel(rat.eradication.status, c("None", "eradicated_2018", "eradicated_2022")))
plot_data

#my_colors <- RColorBrewer::brewer.pal(9, "Blues")[c(2, 4, 6, 8)]

seabird_rat_response_int_plot<-
  ggplot(data = plot_data, aes(x = rat.eradication.status, y = yvar, color = protection))+
  geom_point(pch = 4)+
  geom_pointrange(aes(ymin = LCL, ymax = UCL), alpha = .3, linewidth = 5, size = 0) + 
  geom_point(data = seabird_focal_all_meta_long, 
             aes(y = breeding_biomass, x = rat.eradication.status, shape = spatial_scale,                  
                 color = protection, fill = protection), size = 2.5, alpha = .5)+
  #scale_fill_manual(values = my_colors)+
 # scale_color_manual(values = my_colors) +
  ylab("Seabird breeding biomass (kg/ha)")+
  xlab("")+
    scale_x_discrete(labels = c('no rats','rats eradicated 2018','rats'))+
   theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.9,.7) )

seabird_rat_response_int_plot


#log plot----
plot_data_log<-emmip(sb_br_bio_space_mod_log_lm_2int, ~ rat.eradication.status*protection,
           CIs = TRUE, plotit=FALSE)%>%
  mutate(rat.eradication.status = fct_relevel(rat.eradication.status, c("None", "eradicated_2018", "eradicated_2022")))
plot_data_log


seabird_focal_all_meta_long2<-
  seabird_focal_all_meta_long%>%
  mutate(spatial_scale = fct_relevel(spatial_scale, c("100m", "200m", "side", "motu")))

my_colors <- RColorBrewer::brewer.pal(3, "Dark2")[c(1,2)]

seabird_rat_log_int_plot<-
  ggplot(data = plot_data_log, aes(x = rat.eradication.status, y = yvar, color = protection, fill = protection, group = protection))+
  geom_point(pch = 4, position = position_dodge(.3))+
  geom_pointrange(aes(ymin = LCL, ymax = UCL), alpha = .3, linewidth = 5, size = 0, fatten = 0, position = position_dodge(.3)) + 
  geom_point(data = seabird_focal_all_meta_long2,  position = position_dodge(.3),
             aes(y = log(breeding_biomass+1), x = rat.eradication.status, shape = spatial_scale), size = 2.5, alpha = .5)+
  scale_fill_manual(values = my_colors, labels = c('windward', 'leeward'))+
  scale_color_manual(values = my_colors, labels = c('windward', 'leeward')) +
  scale_shape_manual(values = c(22, 24, 23, 21))+
    ylab(bquote(Seabird~breeding~biomass~(log~kg~ha^-1)))+
  #ylab("Seabird breeding biomass (log kg/ha)")+
  xlab("")+
    scale_x_discrete(labels = c('target','recovering','unrestored'))+
   theme_bw()+
  labs(shape = "spatial scale", fill = 'exposure', color = 'exposure')+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.8,.8),
        axis.text = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        legend.box = "horizontal",
        legend.box.background = element_rect(colour = "black"))
seabird_rat_log_int_plot
  

#ggsave("outputs/seabird_rat_log_int_plot.pdf", plot = seabird_rat_log_int_plot)
#ggsave("outputs/seabird_rat_log_int_plot.jpg", plot = seabird_rat_log_int_plot)


```



#maybe show plots of raw values and model estimates - NO INTERACTIONS
```{r}

#emmeans plot----
plot(emmeans(sb_br_bio_space_mod_log_lm, ~ rat.eradication.status,
          type = "response"))

emmip(sb_br_bio_space_mod_log_lm, ~ rat.eradication.status,
          type = "response", CIs = TRUE)+
   geom_point(data = seabird_focal_all_meta_long, 
             aes(y = breeding_biomass, x = rat.eradication.status, shape = protection, color = spatial_scale, fill = spatial_scale))+
  theme_bw()

#response plot----
plot_data<-emmip(sb_br_bio_space_mod_log_lm, ~ rat.eradication.status,
          type = "response", CIs = TRUE, plotit=FALSE)%>%
  mutate(rat.eradication.status = fct_relevel(rat.eradication.status, c("None", "eradicated_2018", "eradicated_2022")))
plot_data

my_colors <- RColorBrewer::brewer.pal(9, "Blues")[c(2, 4, 6, 8)]

seabird_rat_response_plot<-
  ggplot(data = plot_data, aes(x = rat.eradication.status, y = yvar))+
  geom_point(pch = 4)+
  geom_pointrange(aes(ymin = LCL, ymax = UCL), alpha = .3, linewidth = 5, size = 0) + 
  geom_point(data = seabird_focal_all_meta_long, 
             aes(y = breeding_biomass, x = rat.eradication.status, shape = protection,                  
                 color = spatial_scale, fill = spatial_scale), size = 2.5, alpha = .5)+
  scale_fill_manual(values = my_colors)+
  scale_color_manual(values = my_colors) +
  ylab("Seabird breeding biomass (kg/ha)")+
  xlab("")+
    scale_x_discrete(labels = c('no rats','rats eradicated 2018','rats'))+
   theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.9,.7) )

seabird_rat_response_plot


#log plot----
plot_data_log<-emmip(sb_br_bio_space_mod_log_lm, ~ rat.eradication.status,
           CIs = TRUE, plotit=FALSE)%>%
  mutate(rat.eradication.status = fct_relevel(rat.eradication.status, c("None", "eradicated_2018", "eradicated_2022")))
plot_data_log



seabird_rat_log_plot<-
  ggplot(data = plot_data_log, aes(x = rat.eradication.status, y = yvar))+
  geom_point(pch = 4)+
  geom_pointrange(aes(ymin = LCL, ymax = UCL), alpha = .3, linewidth = 5, size = 0) + 
  geom_point(data = seabird_focal_all_meta_long, 
             aes(y = log(breeding_biomass+1), x = rat.eradication.status, shape = protection, 
                 color = spatial_scale, fill = spatial_scale), size = 2.5, alpha = .5)+
  scale_fill_manual(values = my_colors)+
  scale_color_manual(values = my_colors) +
  ylab("Seabird breeding biomass (log kg/ha)")+
  xlab("")+
    scale_x_discrete(labels = c('no rats','rats eradicated 2018','rats'))+
   theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
        legend.position = c(.9,.7) )
seabird_rat_log_plot
  
```

##save/print plots - OLD
```{r}
seabird_rat_log_plot
seabird_rat_response_plot

#go with log-plot to see everything - save plot

#ggsave("outputs/seabird_vs_rat_log_plot.pdf", plot = seabird_rat_log_plot)

```


##make plot of seabird proportions by motu
```{r}
sb_dat_focal_nests_motu_sp%>%
  ggplot(aes(fill = SpeciesName, y = Density_ha, x = Motu))+
  geom_bar(position = "stack", stat =  "identity")

sb_dat_focal_nests_motu_sp%>%
  ggplot(aes(fill = SpeciesName, y = biomass_kg_ha, x = Motu))+
  geom_bar(position = "stack", stat =  "identity")


#clean up plots and save:
sb_dens_stack_plot<-
sb_dat_focal_nests_motu_sp%>%
  ggplot(aes(fill = SpeciesName, y = Density_ha, x = Motu))+
  geom_bar(position = "stack", stat =  "identity")+
  ylab("Seabird breeding density/ha")+
  xlab("")+
  scale_fill_manual(values = c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3"),  #rcolorbrewer - set2, colorblind friendly
                    name = "Species",
                                            breaks=c("Aminutus",  "Astolidus", "Galba",  "Ssula"),
                       labels=c("Anous minutus (black noddy)", "Anous stolidus (brown noddy)", "Gygis alba (fairy tern)", "Sula sula (red-footed booby)")
                    )+ 
  theme_bw()+
 theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
       legend.position = c(.75,.8)
       )
sb_dens_stack_plot



sb_bio_stack_plot<-
sb_dat_focal_nests_motu_sp%>%
  ggplot(aes(fill = SpeciesName, y = biomass_kg_ha, x = Motu))+
  geom_bar(position = "stack", stat =  "identity")+
  ylab("Seabird breeding biomass kg/ha")+
  xlab("")+
  scale_fill_manual(values = c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3"), #rcolorbrewer - set2, colorblind friendly
                    name = "Species",
                                            breaks=c("Aminutus",  "Astolidus", "Galba",  "Ssula"),
                       labels=c("Anous minutus (black noddy)", "Anous stolidus (brown noddy)", "Gygis alba (fairy tern)", "Sula sula (red-footed booby)")
                    )+ 
  theme_bw()+
 theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
      # legend.position = c(.75,.8)
        legend.position = "none"
        )

sb_bio_stack_plot


seabird_stack_plots<-plot_grid(sb_bio_stack_plot, sb_dens_stack_plot, labels = "auto")
seabird_stack_plots



#ggsave(filename = "outputs/seabird_stack_plots.pdf", 
#       plot = seabird_stack_plots,
#       width = 10,
#      height = 5,
 #      units = "in",
#      dpi = 500)



```



#make and save corrplots - repeat to match crossdata files

```{r}


seabird_focal_all_meta_for_corr<-as.data.frame(seabird_focal_all_meta[,6:21])


cor.mtest(seabird_focal_all_meta_for_corr)
cor.mtest(seabird_focal_all_meta_for_corr, method = "spearman")
cor(seabird_focal_all_meta_for_corr, method = "spearman")
cor(seabird_focal_all_meta_for_corr, method = "pearson")


##PEARSON----
correlation.matrix <- cor(seabird_focal_all_meta_for_corr, use = "pairwise.complete.obs")
write.csv(correlation.matrix, "outputs/seabird_metrics_corrmatrix.csv")


corrplot(cor(seabird_focal_all_meta_for_corr, use = "pairwise.complete.obs"), type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5, title = "Seabirds")

pdf(file = "outputs/seabirds_corrplot.pdf")

corrplot(cor(seabird_focal_all_meta_for_corr, use = "pairwise.complete.obs"), type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5, title = "Seabirds")

dev.off()


##SPEARMAN----
correlation.matrix <- cor(seabird_focal_all_meta_for_corr, use = "pairwise.complete.obs", method = "spearman")
write.csv(correlation.matrix, "outputs/seabird_metrics_corrmatrix_SPEARMAN.csv")


corrplot(cor(seabird_focal_all_meta_for_corr, use = "pairwise.complete.obs", method = "spearman"), type = "upper",addCoef.col = "black", addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5, title = "Seabirds")

pdf(file = "outputs/seabirds_corrplot_SPEARMAN.pdf")

corrplot(cor(seabird_focal_all_meta_for_corr, use = "pairwise.complete.obs", method = "spearman"), type = "upper",
         addCoef.col = NULL, addCoefasPercent = FALSE, tl.col = "black", tl.cex = 0.5)

dev.off()

#all strong corrs....


```



